---
title: "2024 GLM Effects for All Experiments"
author: "Cassandra Buzby"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    code_folding: hide
  html_notebook:
    code_folding: hide
---

```{r, warning=FALSE, message=FALSE, comment=FALSE, fig.width=18, fig.height=5}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Load packages
require(ggplot2)

require(tidyr)
require(dplyr)
require(reshape2)
require(cowplot)
require(data.table)

require(doParallel)
require(RColorBrewer)
require(scales)
require(circlize) 
require(stringr)

require(cybrBSA)
require(lme4)

#TESTING
#glm_formula <- "Allele ~ Bulk * Parent + Rep"

ggplot2::theme_set(theme_light() + theme(text = element_text(size = 10)))

ChromosomeScale <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(Summary = NA, Label = NA) %>% select(-delete)

ChromosomeScale$Start <- 30000
ChromosomeScale$End <- ChromosomeScale$POS - 30000

ChromosomeScale2 <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(summary = 0, label = "Bulk") %>% select(-delete)

# Loci to look at specifically

myloci <- data.frame(CHROM = c("V","V","IX", "III", "IV", "I", "III"),
                     POS = c(375215, 116167,389572, 198671, 46271, 203403, 260311),
                     name = c("FLO8", "URA3", "FLO11", "MAT", "HO", "FLO1", "TUP1"),
                     cat = c("Floc", "X", "Floc", "X", "X", "Floc", "Floc"))

```

# Functions

```{r}
glm_cb2_short <- function(..., W, formula, numgroups = FALSE, outputlength = 4, return = c("Z")) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  #MAYBEWORKS
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  #Return specific ones like z-score only
  if(return %in% "Z"){
    output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients)*0.5)+1):((length(summary(glm_fit)$coefficients)*0.75))]
  }
  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
}

glm_cb2_effect <- function(..., W, formula, numgroups = FALSE, outputlength = 4) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  #MAYBEWORKS
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  #Return effects only

  output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients)*0)+1):((length(summary(glm_fit)$coefficients)*0.25))]

  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
}

glm_cb2_effectSE <- function(..., W, formula, numgroups = FALSE, outputlength = 4) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  #MAYBEWORKS
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  #Return effects only

  output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients)*0)+1):((length(summary(glm_fit)$coefficients)*0.5))]

  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
}

```


## Load In GLM Prep Data

```{r}
#CuSO4 CSS1
HNGLVDRXY_CSS1_glm_prep <- readRDS("StandardGLM/HNGLVDRXY_CSS1_glm_prep.rds") %>% 
  mutate(Bulk = gsub("aUnselected", "aD", Bulk))

HKTFTDRX2_CSS1_glm_prep <- readRDS("StandardGLM/HKTFTDRX2_CSS1_glm_prep.rds")

#CuSO4 CSS8
HVYTYDRX2_CuSO4_CSS8_glm_prep <- readRDS("StandardGLM/HVYTYDRX2_CuSO4_CSS8_glm_prep.rds")

HTG3TDMXY_CSS8_glm_prep <- readRDS("StandardGLM/HTG3TDMXY_CSS8_glm_prep.rds") %>% 
  mutate(DoseCol = Bulk) %>%
  select(-Bulk) %>% 
  select(DoseCol = DoseCol, Bulk = B, Allele = Allele, POS = POS, Parent = Parent, SmoothCount = SmoothCount, CHROM = CHROM, Rep = Rep) %>% na.omit() %>% 
  filter(CHROM != "VIII", CHROM != "M")

HTG3TDMXY_CSS8_glm_prep %>% 
  mutate(DoseCol = gsub("5", "5_", DoseCol)) %>% 
  mutate(DoseCol = gsub("D", "D_", DoseCol)) %>%
  separate(DoseCol, into = c("Dose", "DoseRep"), sep = "_") %>% 
  mutate(Dose = paste(Parent,Dose, sep = "_")) %>%
  mutate(Dose = gsub("O8_35", "1", Dose)) %>%
  mutate(Dose = gsub("O8_45", "2", Dose)) %>%
  mutate(Dose = gsub("W8_35", "2", Dose)) %>%
  mutate(Dose = gsub("W8_25", "1", Dose)) %>%
  mutate(Dose = gsub(".*D", "0", Dose)) -> HTG3TDMXY_CSS8_glm_prep_selection
  

################################################################################

#Fluc CSS8
HVYTYDRX2_Fluc_CSS8_glm_prep <- readRDS("StandardGLM/HVYTYDRX2_Fluc_CSS8_glm_prep.rds")

```


## Separate each into different bulks

CuSO4 1A

```{r}
HNGLVDRXY_CSS1_glm_prep %>% group_by(Bulk, CHROM, POS) %>% #filter(CHROM == "I") %>%
  na.omit() %>%
  summarize(Effect = glm_cb2_effectSE(Allele = Allele,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Parent", "Intercept", "Parent"),
            stat = c("Effect", "Effect", "SE", "SE")) -> HNGLVDRXY_CSS1_SEglm

saveRDS(HNGLVDRXY_CSS1_SEglm, file = "HNGLVDRXY_CSS1_SEglm.rds")
```
CuSO4 1B

```{r}
HKTFTDRX2_CSS1_glm_prep %>% group_by(Bulk, CHROM, POS) %>% #filter(CHROM == "I") %>%
  na.omit() %>%
  summarize(Effect = glm_cb2_effectSE(Allele = Allele,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Parent", "Intercept", "Parent"),
            stat = c("Effect", "Effect", "SE", "SE")) -> HKTFTDRX2_CSS1_SEglm

saveRDS(HKTFTDRX2_CSS1_SEglm, file = "HKTFTDRX2_CSS1_SEglm.rds")
```

CuSO4 8A

```{r}
HVYTYDRX2_CuSO4_CSS8_glm_prep %>% group_by(Bulk, CHROM, POS) %>% #filter(CHROM == "I") %>%
  select(-Dose) %>% na.omit() %>%
  summarize(Effect = glm_cb2_effectSE(Allele = Allele,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Parent", "Intercept", "Parent"),
            stat = c("Effect", "Effect", "SE", "SE")) -> HVYTYDRX2_CuSO4_CSS8_SEglm

saveRDS(HVYTYDRX2_CuSO4_CSS8_SEglm, file= "HVYTYDRX2_CuSO4_CSS8_SEglm.rds")
```

CuSO4 8B

```{r}
HTG3TDMXY_CSS8_glm_prep %>% group_by(Bulk, CHROM, POS) %>% #filter(CHROM == "I") %>%
  na.omit() %>%
  summarize(Effect = glm_cb2_effectSE(Allele = Allele,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Parent", "Intercept", "Parent"),
            stat = c("Effect", "Effect", "SE", "SE")) -> HTG3TDMXY_CSS8_SEglm

saveRDS(HTG3TDMXY_CSS8_SEglm, file = "HTG3TDMXY_CSS8_SEglm.rds")
```
## TESTING NO INTERCEPT

```{r}
HTG3TDMXY_CSS8_glm_prep %>% group_by(CHROM, POS) %>% #filter(CHROM == "I") %>%
  na.omit() %>%
  summarize(Effect = glm_cb2_effect(Allele = Allele,
                                    Bulk = Bulk,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ 0 + Bulk*Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Bulk", "Parent", "Interaction")) -> HTG3TDMXY_CSS8_glm_NOINTERCEPT

HTG3TDMXY_CSS8_glm_prep %>% group_by(CHROM, POS) %>% #filter(CHROM == "I") %>%
  na.omit() %>%
  summarize(Effect = glm_cb2_effect(Allele = Allele,
                                    Bulk = Bulk,
                                      Parent = Parent,
                                      W = SmoothCount,
                                      formula = "Allele ~ Bulk*Parent",
                                      outputlength = 4),
            labels = c("Intercept", "Bulk", "Parent", "Interaction")) -> HTG3TDMXY_CSS8_glm_WITHINTERCEPT

```


## Pivot each so that they all have the stats to compare

```{r}
HNGLVDRXY_CSS1_SEglm %>% 
  mutate(Bulk = gsub("Selected", "C", Bulk),
         Bulk = gsub("Unselected", "aD", Bulk)) %>%
  pivot_wider(names_from = c(Bulk, stat), values_from = Effect) %>% mutate(Z = ((C_Effect - aD_Effect)/sqrt(C_SE^2+aD_SE^2))) -> HNGLVDRXY_CSS1_SEglm_pivot

HKTFTDRX2_CSS1_SEglm %>% 
  pivot_wider(names_from = c(Bulk, stat), values_from = Effect) %>% mutate(Z = ((C_Effect - aD_Effect)/sqrt(C_SE^2+aD_SE^2))) -> HKTFTDRX2_CSS1_SEglm_pivot

HVYTYDRX2_CuSO4_CSS8_SEglm %>% 
  pivot_wider(names_from = c(Bulk, stat), values_from = Effect) %>% mutate(Z = ((C_Effect - aD_Effect)/sqrt(C_SE^2+aD_SE^2))) -> HVYTYDRX2_CuSO4_CSS8_SEglm_pivot

HTG3TDMXY_CSS8_SEglm %>% 
  pivot_wider(names_from = c(Bulk, stat), values_from = Effect) %>% mutate(Z = ((C_Effect - aD_Effect)/sqrt(C_SE^2+aD_SE^2))) -> HTG3TDMXY_CSS8_SEglm_pivot

```

```{r, fig.width=12, fig.height=5}
HNGLVDRXY_CSS1_SEglm_pivot %>% ggplot(aes(x = POS, y = Z, color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")
HKTFTDRX2_CSS1_SEglm_pivot %>% ggplot(aes(x = POS, y = Z, color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")
HVYTYDRX2_CuSO4_CSS8_SEglm_pivot %>% ggplot(aes(x = POS, y = Z, color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")
HTG3TDMXY_CSS8_SEglm_pivot %>% ggplot(aes(x = POS, y = Z, color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")

```
```{r, fig.width=12, fig.height=5}

rbind(data.frame(HNGLVDRXY_CSS1_SEglm_pivot, ds = "HNGLVDRXY_CSS1"),
      data.frame(HKTFTDRX2_CSS1_SEglm_pivot, ds = "HKTFTDRX2_CSS1"),
      data.frame(HVYTYDRX2_CuSO4_CSS8_SEglm_pivot,  ds = "HVYTYDRX2_CuSO4_CSS8"),
      data.frame(HTG3TDMXY_CSS8_SEglm_pivot, ds = "HTG3TDMXY_CSS8")) %>% 
  filter(labels == "Parent") %>% 
  ggplot(aes(x = POS, y = abs(Z), color = ds)) + geom_line() + facet_grid(ds~CHROM, scales = "free", space = "free") + ggtitle("Z scores between Bulks of Parent Effects") + theme(legend.position = "none")

 
```
Load in the comparison of CuSO4 Effects

```{r, fig.width=12, fig.height=5}
#CuSO4Comp_Effects <- readRDS("StandardGLM/CuSO4Comp_Effects.rds")

CuSO4Comp_Effects %>% filter(Factor == "Interaction", glm != "Additive") %>%
  ggplot(aes(x = POS, y = abs(Summary), color = ds)) + geom_line() + facet_grid(ds~CHROM, scales = "free", space = "free") + 
  ggtitle("Interaction Effects") + theme(legend.position = "none")
```
```{r, fig.width=12, fig.height=4}


HTG3TDMXY_CSS8_glm_NOINTERCEPT %>% ggplot(aes(x = POS, y = abs(Effect), color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free") + 
  ggtitle("No Intercept") + theme(legend.position = "bottom")


HTG3TDMXY_CSS8_glm_WITHINTERCEPT %>%  ggplot(aes(x = POS, y = abs(Effect), color = labels)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free") + 
  ggtitle("With Intercept (and replicate)") + theme(legend.position = "bottom")

```


Merge together and see the difference for each effect

```{r, fig.width=12, fig.height=4}
rbind(data.frame(HTG3TDMXY_CSS8_glm_NOINTERCEPT, ds = "NO_INTERCEPT"),
      data.frame(HTG3TDMXY_CSS8_glm_WITHINTERCEPT, ds = "INTERCEPT")) %>%
  ggplot(aes(x = POS, y = abs(Effect), color = paste(ds, labels))) + geom_line(alpha = 0.6) + facet_grid(labels~CHROM, scales = "free", space = "free") + 
  ggtitle("Comparison of Intercept") + #theme(legend.position = "none") +
  scale_color_manual(values = c("black", "black", "black", "black",
                                "turquoise3", "salmon", "violet", "gray"))
```
## Ignoring bulk altogether

```{r, fig.width=12, fig.height=5}
rbind(data.frame(HNGLVDRXY_CSS1_SEglm_pivot, ds = "HNGLVDRXY_CSS1"),
      data.frame(HKTFTDRX2_CSS1_SEglm_pivot, ds = "HKTFTDRX2_CSS1"),
      data.frame(HVYTYDRX2_CuSO4_CSS8_SEglm_pivot,  ds = "HVYTYDRX2_CuSO4_CSS8"),
      data.frame(HTG3TDMXY_CSS8_SEglm_pivot, ds = "HTG3TDMXY_CSS8")) %>% 
  filter(CHROM != "I", CHROM != "VIII") %>%
  ggplot(aes(x = POS, y = abs(C_Effect), color = labels)) + geom_line() + facet_grid(ds~CHROM, scales = "free", space = "free") + 
  ggtitle("Comparison of Copper Parent Effects") + scale_color_manual(values = c("gray", "turquoise4"))
```

Just looking at HTG3TDMXY_CSS8_SEglm_pivot

```{r, fig.width=10, fig.height=5}
HTG3TDMXY_CSS8_SEglm_pivot %>% ggplot(aes(x = POS, y = abs(C_Effect), color = labels)) + geom_line() + facet_grid(labels~CHROM, scales = "free", space = "free") + 
  ggtitle("Copper Parent Effects") + theme(legend.position = "bottom") + scale_color_manual(values = c("turquoise4", "violet"))

rbind(data.frame(HTG3TDMXY_CSS8_glm_NOINTERCEPT, ds = "NO_INTERCEPT"),
      data.frame(HTG3TDMXY_CSS8_glm_WITHINTERCEPT, ds = "INTERCEPT")) %>%
  filter(labels %in% c("Bulk", "Parent", "Interaction")) %>%
  ggplot(aes(x = POS, y = abs(Effect), color = paste(ds, labels))) + geom_line(alpha = 0.6) + facet_grid(labels~CHROM, scales = "free", space = "free") + 
  ggtitle("Comparison of Intercept") + theme(legend.position = "bottom") +
  scale_color_manual(values = c("black", "black", "black",
                                "turquoise4", "salmon", "violet" ))
```

## Okay so what if we had equal ratios of Unselected and then more Oak alleles in one background, and then the other background has a range?

```{r}
simepistasis <- data.frame(Index = 1:100,
                           S_1 = 1:100,
           S_2 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata
 
testdata %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm

testglm %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 1")

################################################################################
simepistasis <- data.frame(Index = 1:100,
                           S_2 = 1:100,
           S_1 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata
 
testdata %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm

testglm %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 2")
```
## Same as above, except let's make the Intecept 0

```{r}
simepistasis <- data.frame(Index = 1:100,
                           S_1 = 1:100,
           S_2 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata
 
testdata %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ 0+Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm

testglm %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 1")

################################################################################
simepistasis <- data.frame(Index = 1:100,
                           S_2 = 1:100,
           S_1 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata
 
testdata %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ 0+ Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm

testglm %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 2")
```

## Now let's try contrasts

## Same as above, except let's make the Intecept 0

```{r}
simepistasis <- data.frame(Index = 1:100,
                           S_1 = 1:100,
           S_2 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata_c1

contrasts(testdata_c1$Bulk) <- matrix(c(1/2, -1/2), ncol = 1)
contrasts(testdata_c1$Allele) <- matrix(c(1/2, -1/2), ncol = 1)
contrasts(testdata_c1$Parent) <- matrix(c(1/2, -1/2), ncol = 1)

testdata_c1 %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ 0+Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm_c1

testglm_c1 %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 1")

################################################################################
simepistasis <- data.frame(Index = 1:100,
                           S_2 = 1:100,
           S_1 = 100, 
           D_1 = 50, 
           D_2 = 50)

simepistasis %>% pivot_longer(-Index, names_to = "Bulk", values_to = "A") %>%
  mutate(B = 101-A) %>%
  pivot_longer(c(A, B), names_to = "Allele", values_to = "count") %>%
  separate(Bulk, into = c("Bulk", "Parent"), sep = "_") %>%
  mutate_if(is.character, as.factor) -> testdata_c2
 
contrasts(testdata_c2$Bulk) <- matrix(c(1/2, -1/2), ncol = 1)
contrasts(testdata_c2$Allele) <- matrix(c(1/2, -1/2), ncol = 1)
contrasts(testdata_c2$Parent) <- matrix(c(1/2, -1/2), ncol = 1)

testdata_c2 %>% group_by(Index) %>%
  summarize(effect = glm_cb2_effect(Allele = Allele, 
                           Bulk = Bulk,
                           Parent = Parent,
                           W = count,
                           formula = "Allele ~ 0+ Bulk*Parent"),
            label = c("Intercept", "Bulk", "Parent", "Interaction")) -> testglm_c2

testglm_c2 %>% ggplot(aes(x = Index, y = effect, color = label)) + geom_point() + ggtitle("Index 1 = sign epistasis, Epistatic is parent 2")
```