---
title: "Fluconazole Experiments"
author: "Cassandra Buzby"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Load packages
require(ggplot2)
require(tidyr)
require(dplyr)
require(reshape2)
require(cowplot)
require(data.table)

require(doParallel)
require(RColorBrewer)
require(scales)
require(circlize) 
require(stringr)
require(ggrepel)

require(cybrBSA)
library(fuzzyjoin)

require(BiocManager)
require(IRanges)

# if (!require("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")

# BiocManager::install("IRanges")

ggplot2::theme_set(theme_light() + theme(text = element_text(size = 10)) +
                     theme(#axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()))

ChromosomeScale <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(Summary = NA, Label = NA) %>% select(-delete)

ChromosomeScale$Start <- 30000
ChromosomeScale$End <- ChromosomeScale$POS - 30000

ChromosomeScale2 <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(summary = 0, label = "Bulk") %>% select(-delete)

# Loci to look at specifically

myloci <- data.frame(CHROM = c("V","V","IX", "III", "IV", "I", "III"),
                     POS = c(375215, 116167,389572, 198671, 46271, 203403, 260311),
                     name = c("FLO8", "URA3", "FLO11", "MAT", "HO", "FLO1", "TUP1"),
                     cat = c("Floc", "X", "Floc", "X", "X", "Floc", "Floc"))



## Functions for GLM all and Permutation all

glm_cb2_all <- function(..., W, formula, numgroups = FALSE, outputlength = 8) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  output <- summary(glm_fit)$coefficients[c(((length(summary(glm_fit)$coefficients)*0)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.25)),
                                            ((length(summary(glm_fit)$coefficients)*0.5)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.75)))]

  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
} 


################################################################################
# No replicates, fix Parent
cybrPermute_cb2_all <- function(dataset, 
                                R = 0, perp = 1, outlength = 4, 
                                glmform = "Allele ~ Bulk * Parent", 
                                inputlabels = c("Intercept", "Bulk", "Parent", "Interaction")){
  start.time <- Sys.time()
    
  print("Make sure that dilute bulk is labeled aD")
  print(paste("Your labels are:", inputlabels))

    if(R > 0){ #INCLUDE REPLICATES
        dataset %>% 
        distinct() %>% ungroup() %>%
        group_by(CHROM, POS, Allele, Bulk, Rep, Parent) %>% 
        summarize(culprits = length((SmoothCount))) %>% 
        merge(dataset) %>% 
        filter(culprits == 1) %>% 
        ungroup() %>%
        distinct() %>% #THIS IS IMPORTANT
        pivot_wider(names_from = Allele, values_from = SmoothCount) -> newnewtest    
    }else{ #DO NOT INCLUDE REPLICATES
        dataset %>% 
        distinct() %>% ungroup() %>%
        group_by(CHROM, POS, Allele, Bulk, Parent) %>% 
        summarize(culprits = length((SmoothCount))) %>% 
        merge(dataset) %>% 
        filter(culprits == perp) %>% 
        ungroup() %>%
        distinct() %>% #THIS IS IMPORTANT
        pivot_wider(names_from = Allele, values_from = SmoothCount) -> newnewtest
    }
  
    #PERMUTE TWICE
  if(R > 0){
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Rep, 
             Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Rep = Rep, 
                Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "A") -> shuffled_DiluteA2
    
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, 
             Rep, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Rep = Rep,
                Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "B") -> shuffled_DiluteB2
    
  }else{
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "A") -> shuffled_DiluteA2
    
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "B") -> shuffled_DiluteB2
    
  }
    
    rbind(shuffled_DiluteA2, shuffled_DiluteB2) %>% pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "SmoothCount") -> shuffletoglm2
    
    #RUN THE GLM
    if(R > 0) {
      shuffletoglm2 %>% na.omit() %>%
      group_by(Loc) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(Allele = Allele,
                                 Bulk = Bulk,
                                 Parent = Parent,
                                 Rep = Rep,
                                 W = SmoothCount,
                                 formula = glmform,
                                outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> glmresult
    }else{
      shuffletoglm2 %>% na.omit() %>%
      #Original Script
      group_by(Loc) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(Allele = Allele,
                                 Bulk = Bulk,
                                 Parent = Parent,
                                 W = SmoothCount,
                                 formula = glmform,
                                outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> glmresult
    }
    
    
    end.time = Sys.time()
    print(end.time - start.time)
    return(glmresult)
}

newnewtest %>% na.omit()
shuffled_DiluteA2 %>% na.omit()
shuffled_DiluteB2 %>% na.omit()
```

# Load in pre-glm data

## Do the GLMs and Permutations for EACH EXPERIMENT

```{r}
#USE THIS ONE
HVYTYDRX2_prep <- readRDS("StandardGLM/HVYTYDRX2_Fluc_CSS8_glm_prep.rds") 
HVYTYDRX2_prep$Bulk <- factor(HVYTYDRX2_prep$Bulk)
contrasts(HVYTYDRX2_prep$Bulk) <- matrix(c(0, 1), ncol = 1)
contrasts(HVYTYDRX2_prep$Parent) <- matrix(c(1/2, -1/2), ncol = 1)


# HVYTYDRX2_prep %>% unite(c(Parent), col = "PD") %>% filter(PD != "O8_5") %>% separate(PD, into = c("Parent", "Dose"), sep = "_") %>%
#   mutate(DoseCol = 0) %>%
#   select(DoseCol = DoseCol, Bulk = Bulk, Allele = Allele, POS = POS, Parent = Parent, 
#          SmoothCount = SmoothCount, CHROM = CHROM, Rep = Rep, Pool = Pool) %>% 
#   filter(CHROM != "VIII", CHROM != "M") %>% mutate_if(is.character,as.factor) -> test

#test -> HVYTYDRX2_prep

table(HVYTYDRX2_prep$Bulk, HVYTYDRX2_prep$Parent)

inputlabels <- c("cept", "Bulk", "Parent", "Interaction")
HVYTYDRX2_prep %>% select(-Dose) %>% na.omit() %>% 
      group_by(Pool, CHROM, POS) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(
                                    Allele = Allele, Bulk = Bulk, Parent = Parent, 
                                    W = SmoothCount,
                                    formula = "Allele ~ Bulk * Parent",
                                    outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> HVYTYDRX2_glm

saveRDS(HVYTYDRX2_glm, file = "HVYTYDRX2_glm_APRIL24f.rds")

HVYTYDRX2_glm %>% na.omit()

################################################################################
HVYTYDRX2_permutation <- cybrPermute_cb2_all(HVYTYDRX2_prep, perp = 2)


HVYTYDRX2_permutation %>% group_by(Factor) %>%
  summarize(quant095 = quantile(abs(Summary), 0.95, na.rm = TRUE),
             quant099 = quantile(abs(Summary), 0.99, na.rm = TRUE),
             quant0995 = quantile(abs(Summary), 0.995, na.rm = TRUE)) -> HVYTYDRX2_permutation_Qs


saveRDS(HVYTYDRX2_permutation_Qs, file = "HVYTYDRX2_permutation_Qs_APRIL24f.rds")
```

```{r}
#CHANGED
HGVMVDRX2_prep <- readRDS("StandardGLM/HGVMVDRX2_CSS1_glm_prep.rds") %>% 
  # mutate(DoseCol = 0) %>%
  # select(DoseCol = DoseCol, Bulk = Bulk, Allele = Allele, POS = POS, Parent = Parent, 
  #        SmoothCount = SmoothCount, CHROM = CHROM, Rep = Rep, Pool = Pool) %>% na.omit() %>% 
  filter(CHROM != "I", CHROM != "M") %>% mutate(Bulk = gsub("aDilute", "aD", Bulk)) %>% mutate_if(is.character,as.factor)

contrasts(HGVMVDRX2_prep$Bulk) <- matrix(c(0, 1), ncol = 1)
contrasts(HGVMVDRX2_prep$Parent) <- matrix(c(1/2, -1/2), ncol = 1)

inputlabels <- c("cept", "Bulk", "Parent", "Interaction")
HGVMVDRX2_prep %>% na.omit() %>% 
      group_by(Pool, CHROM, POS) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(
                                    Allele = Allele, Bulk = Bulk, Parent = Parent, 
                                    W = SmoothCount,
                                    formula = "Allele ~ Bulk * Parent",
                                    outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> HGVMVDRX2_glm

saveRDS(HGVMVDRX2_glm, file = "HGVMVDRX2_glm_APRIL24f.rds")

################################################################################

HGVMVDRX2_permutation <- cybrPermute_cb2_all(HGVMVDRX2_prep)
#unique(HGVMVDRX2_prep$Bulk)
#table(HGVMVDRX2_prep$Rep, HGVMVDRX2_prep$Bulk, HGVMVDRX2_prep$Parent)

HGVMVDRX2_permutation %>% group_by(Factor) %>%
  summarize(quant095 = quantile(abs(Summary), 0.95, na.rm = TRUE),
             quant099 = quantile(abs(Summary), 0.99, na.rm = TRUE),
             quant0995 = quantile(abs(Summary), 0.995, na.rm = TRUE)) -> HGVMVDRX2_permutation_Qs


saveRDS(HGVMVDRX2_permutation_Qs, file = "HGVMVDRX2_permutation_Qs_APRIL24f.rds")
```


# Load in pre-run data
```{r}
HGVMVDRX2_permutation_Qs <- readRDS("HGVMVDRX2_permutation_Qs_APRIL24f.rds")
HVYTYDRX2_permutation_Qs <- readRDS("HVYTYDRX2_permutation_Qs_APRIL24f.rds")

```

```{r}

HGVMVDRX2_glm <- readRDS("HGVMVDRX2_glm_APRIL24f.rds") 
HVYTYDRX2_glm <- readRDS("HVYTYDRX2_glm_APRIL24f.rds")

HGVMVDRX2_glm %>% filter(d == "Z", Factor != "cept") %>% mutate(Pool = "HGVMVDRX2") %>% merge(HGVMVDRX2_permutation_Qs) -> HGVMVDRX2
HVYTYDRX2_glm %>% filter(d == "Z", Factor != "cept") %>% mutate(Pool = "HVYTYDRX2") %>% merge(HVYTYDRX2_permutation_Qs) -> HVYTYDRX2

rbind(HVYTYDRX2, HGVMVDRX2) %>%
  ungroup() %>% 
  group_by(Pool, CHROM, Factor, d) %>%
  #na.omit() %>%
  arrange(POS) %>%
summarize(POS = POS, Summary = frollapply(x = Summary, n = 100, FUN = mean, align = "left"),
          quant095 = quant095,
          quant099 = quant099,
          quant0995 = quant0995) %>% #na.omit() %>%
   mutate(Dose = 0) %>%
  select(Factor,CHROM,Dose,d,POS,Summary,Pool,quant095,quant099,quant0995) -> Fluc_All

unique(Fluc_All$Pool)
  
```

# Calling Peaks


```{r, eval = FALSE}
Fluc_All %>% group_by(Pool, Factor, CHROM) %>% arrange(POS) %>%
  na.omit() %>%
  mutate(is_above_threshold = abs(Summary) > quant095) %>%
  
  mutate(segment_change = is_above_threshold != lag(is_above_threshold, default = FALSE)) %>%
  mutate(segment_id = cumsum(segment_change)) %>%
  # Group by chromosome and segment_id to count the points in each segment
  group_by(Pool, Factor, CHROM, segment_id) %>%
  mutate(points_in_segment = n()) %>%
  # Now filter to keep only those segments that are above the threshold and have 5 or more points
  filter(is_above_threshold, points_in_segment >= 100) %>%
 # mutate(change = is_above_threshold != lag(is_above_threshold, default = first(is_above_threshold))) %>%
  #mutate(group_id = cumsum(change)) %>%
  #group_by(Pool, Factor, CHROM, d, group_id) %>%
 # filter(is_above_threshold) %>%
  summarize(max_value = max(abs(Summary), na.rm = TRUE),
            ppeakPOS = POS[which.max(abs(Summary))]) %>%
  ungroup() -> maybepeaks

maybepeaks %>% filter(CHROM == "VIII") %>% mutate(Dist = 212535 - ppeakPOS) %>% ungroup() %>% summarize(max = max(Dist),
                                                                                                        mean = mean(Dist),
                                                                                                        sd = sd(Dist)) -> CUP1distance
#19kb distance from nearest CUP1 start
#5kb sd in this distance
```


## Bulk Peaks

This plot shows the peaks that are between 50000bp from each other within both high and low doses, and can be called overlapping peaks that way. These are also based on peaks called by the entire region above the cutoff, which in particular affects Chr XII since there are two areas where peaks seem to occur. The peaks on Chr XIII don't seem to be called at all, probably because they're too far from one another.


```{r, fig.height=4, fig.width=10}
maybepeaks %>% filter(Factor == "Bulk") %>% select(-segment_id) %>% pivot_wider(names_from = c(Pool), values_from = max_value) -> bulkpeaks

for(i in unique(bulkpeaks$CHROM)){
  bulkpeaks %>% filter(CHROM == i) -> tempdata
  tempdist <- as.matrix(dist(tempdata$ppeakPOS, upper = FALSE, diag = FALSE))
  successes <- as.data.frame(which(tempdist < 19317, arr.ind = TRUE)) %>% filter(row != col)
  
  for(k in 1:(nrow(successes)/2)){
    if(k == 1){
      all <- c(tempdata$ppeakPOS[successes$row[k]], tempdata$ppeakPOS[successes$col[k]])
    }else{
      pairs <- c(tempdata$ppeakPOS[successes$row[k]], tempdata$ppeakPOS[successes$col[k]])
      all <- rbind(all, pairs)
    }
    
  }
}
#find the common rounding, or maybe just find if there are any within 19kb?
rm(groupbulks)
for(i in unique(bulkpeaks$CHROM)){
  bulkpeaks %>% filter(CHROM == i) -> tempdata
  if(nrow(tempdata) > 1){
    tempdist <- (dist(tempdata$ppeakPOS, upper = FALSE, diag = FALSE))
      hc <- hclust(tempdist)
      groups <- cutree(hc, h = 19317)
      tempdata$groups <- groups
      
  }else{
      tempdata$groups <- 0
  }
  if(exists("groupbulks") == FALSE){
        groupbulks <- tempdata
      }else{
        groupbulks <- rbind(groupbulks, tempdata)
      }
  }
  

groupbulks %>% ungroup() %>% group_by(CHROM, groups) %>% summarize(num = length(ppeakPOS),
                                                                   avgPOS = mean(ppeakPOS)) %>% merge(groupbulks) -> groupbulks

groupbulks %>% 
  pivot_longer(-c(CHROM, groups, num, avgPOS, Factor, ppeakPOS), names_to = c("Pool", "Dose"), names_sep = "_") %>% 
   ungroup() %>% group_by(CHROM) -> gb

Fluc_All %>% filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gb, aes(xintercept = avgPOS, color = paste(num, groups)), alpha = 0.4, size = 1) +
  geom_point(data = gb, aes(x = avgPOS, color = paste(num, groups), shape = as.factor(num), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Bulk Comparison of Doses") +
  theme(legend.position = "none")

Fluc_All %>% filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gb[gb$num > 1,], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gb[gb$num > 1,], aes(x = avgPOS, color = as.factor(groups), shape = as.factor(num), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Bulk Comparison of Doses; Overlapping Peaks") +
  theme(legend.position = "none")

Fluc_All %>% filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gb[gb$num == 1,], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gb[gb$num == 1,], aes(x = avgPOS, color = as.factor(groups), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Bulk Comparison of Doses; Non-Overlapping Peaks") +
  theme(legend.position = "none")

```

Checking to make sure it all looks normal

```{r, fig.height=4, fig.width=10}
Fluc_All %>% #filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary), color = Pool)) + 
  geom_hline(aes(yintercept = quant095, color = Pool)) + 
  #geom_vline(data = gb, aes(xintercept = avgPOS, color = paste(num, groups)), alpha = 0.4, size = 1) +
  #geom_point(data = gb, aes(x = avgPOS, color = paste(num, groups), shape = as.factor(num), y = value)) +
  geom_line(aes(linetype = Dose == "High"), alpha = 0.8, show.legend = FALSE) +
  facet_grid(Factor~CHROM, space = "free", scales = "free") + ggtitle("Comparison of Runs") +
  theme(legend.position = "bottom")

Fluc_All %>% #filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary), color = Factor)) + 
  geom_hline(aes(yintercept = quant095, color = Factor)) + 
  #geom_vline(data = gb, aes(xintercept = avgPOS, color = paste(num, groups)), alpha = 0.4, size = 1) +
  #geom_point(data = gb, aes(x = avgPOS, color = paste(num, groups), shape = as.factor(num), y = value)) +
  geom_line(aes(linetype = Dose == "High"), alpha = 0.8, show.legend = FALSE) +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Comparison of Runs by Factor") +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("black", "purple", "gray"))

```

## Interaction Peaks

This plot shows the peaks that are between 50000bp from each other within both high and low doses, and can be called overlapping peaks that way. These are also based on peaks called by the entire region above the cutoff, which in particular affects Chr XII since there are two areas where peaks seem to occur. The peaks on Chr XIII don't seem to be called at all, probably because they're too far from one another.


```{r, fig.height=4, fig.width=10}
maybepeaks %>% filter(Factor == "Interaction") %>% select(-segment_id) %>% pivot_wider(names_from = c(Pool), values_from = max_value) -> Interactionpeaks

#find the common rounding, or maybe just find if there are any within 19kb?
rm(groupInteractions)

for(i in unique(Interactionpeaks$CHROM[Interactionpeaks$CHROM %in% c("VIII", "I") == FALSE])){
  Interactionpeaks %>% filter(CHROM == i) -> tempdata
  if(nrow(tempdata) >1){
    tempdist <- (dist(tempdata$ppeakPOS, upper = FALSE, diag = FALSE))
    hc <- hclust(tempdist)
    groups <- cutree(hc, h = 19317)
    tempdata$groups <- groups

  }else{
    tempdata$groups <- 0
  }
  
  if(i == unique(Interactionpeaks$CHROM[Interactionpeaks$CHROM %in% c("VIII", "I") == FALSE])[1]){
    groupInteractions <- tempdata
  }else{
    groupInteractions <- rbind(groupInteractions, tempdata)
  }
}

groupInteractions %>% ungroup() %>% group_by(CHROM, groups) %>% summarize(num = length(ppeakPOS),
                                                                   avgPOS = mean(ppeakPOS)) %>% merge(groupInteractions) -> groupInteractions

groupInteractions %>% 
  pivot_longer(-c(CHROM, groups, num, avgPOS, Factor, ppeakPOS), names_to = c("Pool", "Dose"), names_sep = "_") %>% 
   ungroup() %>% group_by(CHROM) -> gI

Fluc_All %>% filter(Factor == "Interaction") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gI, aes(xintercept = avgPOS, color = paste(num, groups)), alpha = 0.4, size = 1) +
  geom_point(data = gI, aes(x = avgPOS, color = paste(num, groups), shape = as.factor(num), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Interaction Comparison of Doses") +
  theme(legend.position = "none")

Fluc_All %>% filter(Factor == "Interaction") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gI[gI$num > 1,], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gI[gI$num > 1,], aes(x = avgPOS, color = as.factor(groups), shape = as.factor(num), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Interaction Comparison of Doses; Overlapping Peaks") +
  theme(legend.position = "none")

Fluc_All %>% filter(Factor == "Interaction") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095)) + 
  geom_vline(data = gI[gI$num == 1,], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gI[gI$num == 1,], aes(x = avgPOS, color = as.factor(groups), y = value)) +
  geom_line(alpha = 0.8, color = "black") +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Interaction Comparison of Doses; Non-Overlapping Peaks") +
  theme(legend.position = "none")

```

# Combining peaks to call at once

```{r}
maybepeaks %>% select(-segment_id) %>% pivot_wider(names_from = c(Pool), values_from = max_value) -> allpeaks

#find the common rounding, or maybe just find if there are any within 19kb?

for(i in unique(allpeaks$CHROM)){
  allpeaks %>% filter(CHROM == i) -> tempdata
  if(nrow(tempdata) > 1){
      tempdist <- (dist(tempdata$ppeakPOS, upper = FALSE, diag = FALSE))
      hc <- hclust(tempdist)
      groups <- cutree(hc, h = 24818)
      tempdata$groups <- groups
  }else{
    tempdata$groups <- 0
  }

  if(i == unique(allpeaks$CHROM)[1]){
    groupInteractions <- tempdata
  }else{
    groupInteractions <- rbind(groupInteractions, tempdata)
  }
}

groupInteractions %>% ungroup() %>% group_by(CHROM, groups) %>% summarize(num = length(ppeakPOS),
                                                                   avgPOS = mean(ppeakPOS)) %>% merge(groupInteractions) -> groupPeaks

groupPeaks %>% 
  pivot_longer(-c(CHROM, groups, num, avgPOS, Factor, ppeakPOS), names_to = c("Pool", "Dose"), names_sep = "_") %>% 
   ungroup() %>% group_by(CHROM) -> gP
```

```{r, fig.width = 12, fig.height = 5}
ggplot2::theme_set(theme_light() + theme(axis.text.x = element_blank(), legend.position = "bottom") + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "gray70"),
        panel.border = element_rect(colour = "gray70", fill=NA, linewidth=0.4))+
    theme(#axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    theme(text = element_text(size = 10)))

# length(unique(gP$groups))

Fluc_All %>% 
  ggplot(aes(x = POS, y = abs(Summary))) + 
  #geom_hline(aes(yintercept = quant095, linetype = paste(Pool))) + 
  #single peaks
  geom_vline(data = gP[gP$num == 1,], aes(xintercept = avgPOS), color = "gray", alpha = 0.2, size = 1, show.legend=FALSE) +
  geom_point(data = gP[gP$num == 1,], aes(x = ppeakPOS, y = value), alpha = 0.4, color = "gray", shape = 17, show.legend=FALSE) +
  #shared peaks
  geom_vline(data = gP[gP$num > 1,], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1, show.legend=FALSE) +
  geom_point(data = gP[gP$num > 1,], aes(x = ppeakPOS, color = as.factor(groups), y = value), size = 2, alpha = 0.8, show.legend=FALSE) +
  
  #geom_line(aes(linetype = paste(Pool)), alpha = 0.8, color = "black", show.legend=FALSE) +
  geom_line(aes(linetype = paste(Pool)), color = "black") +
  facet_grid(Factor~CHROM, space = "free", scales = "free") + ggtitle("Peaks within 24kb")
```

```{r, fig.width = 12, fig.height = 5}

Fluc_All %>% filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095, linetype = paste(Pool))) + 
  #single peaks
  geom_vline(data = gP[gP$num == 1 & gP$Factor == "Bulk",], aes(xintercept = avgPOS), color = "gray", alpha = 0.2, size = 1) +
  geom_point(data = gP[gP$num == 1 & gP$Factor == "Bulk",], aes(x = ppeakPOS, y = value), alpha = 0.4, color = "gray", shape = 17) +
  #shared peaks
  geom_vline(data = gP[gP$num > 1  & gP$Factor == "Bulk",], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gP[gP$num > 1 & gP$Factor == "Bulk",], aes(x = ppeakPOS, color = as.factor(groups), y = value), size = 2, alpha = 0.8) +
  
  geom_line(aes(linetype = paste(Pool)), alpha = 0.8, color = "black", show.legend=FALSE) +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Bulk Peaks within 24kb")+ 
  theme(legend.position = "none")

Fluc_All %>% filter(Factor == "Interaction") %>%
  ggplot(aes(x = POS, y = abs(Summary))) + 
  geom_hline(aes(yintercept = quant095, linetype = paste(Pool))) + 
  #single peaks
  geom_vline(data = gP[gP$num == 1 & gP$Factor == "Interaction",], aes(xintercept = avgPOS), color = "gray", alpha = 0.2, size = 1) +
  geom_point(data = gP[gP$num == 1 & gP$Factor == "Interaction",], aes(x = ppeakPOS, y = value), alpha = 0.4, color = "gray", shape = 17) +
  #shared peaks
  geom_vline(data = gP[gP$num > 1  & gP$Factor == "Interaction",], aes(xintercept = avgPOS, color = as.factor(groups)), alpha = 0.4, size = 1) +
  geom_point(data = gP[gP$num > 1 & gP$Factor == "Interaction",], aes(x = ppeakPOS, color = as.factor(groups), y = value), size = 2, alpha = 0.8) +
  
  geom_line(aes(linetype = paste(Pool)), alpha = 0.8, color = "black", show.legend=FALSE) +
  facet_grid(Pool~CHROM, space = "free", scales = "free") + ggtitle("Interaction Peaks within 24kb")+ 
  theme(legend.position = "none")
```

# Comparing which peaks actually overlap

### Rescaling to the highest peak or cutoff

```{r, fig.width=12, fig.height=4}
Fluc_All %>% group_by(Pool, Factor) %>% summarize(CHROM = CHROM, POS = POS, 
                                                               maxpeak = max(abs(Summary)),
                                                              prop = abs(Summary)/maxpeak) -> Fluc_All_proportions

Fluc_All_proportions %>% filter(Factor == "Bulk") %>%
  ggplot(aes(x = POS, y = prop, linetype = paste(Pool))) + geom_line() + 
  geom_vline(data = addtoplot2[addtoplot2$num > 1  & addtoplot2$Factor == "Bulk",], 
             aes(xintercept = avgPOS, color = as.factor(groups)), 
             alpha = 0.4, size = 1) +
  facet_grid(~CHROM, space = "free", scales = "free") +
  theme(legend.position = "none") 
```

