---
title: "Running cybrBSA Easily | Lab Meeting Tutorial"
author: "Cassandra Buzby"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---


Link to the cybrBSA github: https://github.com/cbuzby/cybrBSA  

### Install cybrBSA if you haven't already

One day Cassandra will get this on CRAN, but until then, github is going to have to work:

```{r, eval = FALSE}
#Do you have devtools installed?
#install.packages("devtools")

#Do you have devtools loaded?
library(devtools)

#Do you have cybrBSA installed?
install_github("cbuzby/cybrBSA")

#Do you have cybrBSA loaded?
library(cybrBSA)

```

### Load in your functions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Load packages
library(tidyverse)
library(dplyr)
library(cybrBSA) #Adding this here as well since you'll need to run this section each

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r, echo = FALSE}
ez_getrawdata <- function(tablefilename){
  ChromKey <- data.frame(chromosomes = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII", 
                                       "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"), 
                       CHROM = c("NC_001133.9", "NC_001134.8", "NC_001135.5", "NC_001136.10", 
                                 "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6", 
                                 "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5", 
                                 "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1"))
  
  cybrInputGATKTable(tablefilename) %>% mutate(Coverage = as.numeric(AD.REF) + as.numeric(AD.ALT)) %>%
  select(POS, CHROM, Dataset, GQ, AD.REF, AD.ALT, Coverage) -> rawdata
  
  return(rawdata)
}

ez_callSNPs <- function(mydata = rawdata, parentSNPs){
  
  if(missing(parentSNPs)){
    parentSNPs <- cybrConvertParentalAlleles(Truncate = TRUE)
  }

  mydata %>% 
    merge(parentSNPs) %>% 
    mutate(REFW = as.numeric(Type == "Wine"), REFO = as.numeric(Type == "Oak")) %>%
    group_by(Dataset, CHROM, POS) %>%
    mutate(Wine = max(REFW * as.numeric(AD.REF), REFO * as.numeric(AD.ALT)),
           Oak = max(REFW * as.numeric(AD.ALT), REFO * as.numeric(AD.REF))) %>%
    select(Dataset, POS, CHROM, Coverage, Wine, Oak) %>%
    pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "Reads") -> called.output
  
  return(called.output)
}

ez_smooth <- function(mydata = rawdata_called, window = 200, myfunction = cybr_weightedgauss, myalignment = "center"){
  
  require(data.table)

  mydata %>% group_by(Dataset, CHROM, Allele) %>% arrange(POS) %>%
  reframe(POS = POS, 
          SmoothCount = ceiling(frollapply(Reads, n = window, FUN = myfunction, align = myalignment))
          ) -> smoothed.output
  
  return(smoothed.output)

}

ez_colselect <- function(mydata = rawdata_smoothed,
                       datasetcol = "Dataset",
                       separator = "[_.]",
                       mode = "SELECTCOLS",
                       library, droplist = "B", keeplist = "C"){
  
  n_cols <- max(lengths(strsplit(mydata[[datasetcol]], separator)))
  
  mydata %>%
    #head(10) %>%
    separate(datasetcol, into = LETTERS[1:n_cols], sep = separator) -> temp
  
  if(mode == "SELECTCOLS"){
    
    cat("You are using ez_glmprep in SELECTCOLS mode. To switch, please set mode to 'FILTERCOLS'","\n" )
    for(k in unique(temp$A)){
      temp.a <- temp %>% filter(A == k)
      
      cat(paste("\n","### In library", k,"###", "\n"))
      
      for(i in LETTERS[2:n_cols]){
      #cat(i,"\n")
      cat("Col", i, ":", unique(temp.a[[i]]),"\n")
      }
    }
  }else if(mode == "FILTERCOLS"){
      mycols <- LETTERS[1:n_cols]
      losers <- mycols[mycols %in% droplist | (mycols %in% keeplist)== FALSE]
      
    if(missing(library)){
      temp %>% select(colnames(temp)[colnames(temp) %in% losers == FALSE]) %>%
      na.omit() -> filtered.output
    
    return(filtered.output)
    }else{
       temp %>% filter(A == library) %>%
        select(colnames(temp)[colnames(temp) %in% losers == FALSE]) %>%
      na.omit() -> filtered.output
    
    return(filtered.output)
    }
  }
}

ez_glmprep.setcontrasts <- function(mydata, colname, ctrl, exp){
  mysubset <- mydata[mydata[[colname]] %in% c(ctrl, exp),]
  mysubset[[colname]] <- factor(mysubset[[colname]], levels = c(ctrl, exp))
  
  contrasts(mysubset[[colname]]) <- c(0,1)
  
  return(mysubset)
}

ez_glm.single <- function(mydatainput, 
                          dropchroms = c("M"),
                       AlleleCol = "Allele",
                       ExpCol = "E",
                       ReadsCol = "SmoothCount"){
  
  myformula = "Allele ~ E"
  
  mydatainput$Allele <- mydatainput[[AlleleCol]]
  mydatainput$E <- mydatainput[[ExpCol]]
  mydatainput$weights <- mydatainput[[ReadsCol]]
  
  mydatainput %>% na.omit() %>% 
  filter(CHROM %in% dropchroms == FALSE) %>%
  group_by(CHROM, POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(summary = glm_cb2_short(Allele = Allele,
                             E = E,
                             W = weights, #use the weights variable from test
                             formula = myformula,
                             outputlength = 2),
            #MAKE SURE THIS IS THE SAME LENGTH AS OUTPUT LENGTH
            Factor = (c("Intercept", "E"))) -> processed_glm_all
  
  return(processed_glm_all)
}

ez_plotting <- function(glmoutput, absolutevalue = TRUE,
                        dropintercept = TRUE,
                        chroms = c("All"),
                        cutoff){
  
  require(ggplot2)
  
  if(dropintercept == TRUE){
    glmoutput %>% filter(Factor != "Intercept") -> glmoutput
  }
  
  if(chroms != "All"){
    glmoutput %>% filter(CHROM %in% chroms) -> glmoutput
  }
  
  if(absolutevalue == TRUE){
    glmoutput$summary <- abs(glmoutput$summary)
  }
  
  glmoutput %>% 
      ggplot(aes(x = POS, y = summary, color = Factor)) + geom_line() +
      ylab("z-score") +
      facet_grid(~CHROM, scales = "free", space = "free") +
      theme_bw() +
      theme(legend.position = "bottom") -> plotoutput
  
  if(missing(cutoff) == FALSE){
    plotoutput + geom_hline(aes(yintercept = cutoff), linetype = "dashed") -> plotoutput
  }
  
  return(plotoutput)
    
}

```


# Theory

We're going to load in a partially processed segment here that we can use for principles, before getting to an actual pipeline.  

```{r, eval = FALSE}
#This is how I'm getting the data that you can load in as an RDS; it takes a while since it's all

rawdata.cb <- ez_getrawdata(tablefilename = "C://Users//cassa//Documents//SiegalLab//Data//Jan25_CSS15.SortedCat.vcf.output.table")

rawdata.cb_called <- ez_callSNPs(mydata = rawdata.cb)

rawdata.cb_called %>% filter(grepl("undetermined", Dataset) == FALSE) -> rawdata.cb_called.filtered

ez_colselect(mydata = rawdata.cb_called.filtered[rawdata.cb_called.filtered$CHROM == "II",], 
             mode = "SELECTCOLS")

sampledata <- ez_colselect(mydata = rawdata.cb_called.filtered, 
                           keeplist = c("C", "D", "E"), 
                           mode = "FILTERCOLS")

saveRDS(sampledata, file = "sampledata.rds")
```

```{r}
example.cb <- readRDS("sampledata.rds")

head(example.cb)

```


```{r}
#What do our log odds look like? Filter from Chr IV to test
example.cb %>% 
  filter(CHROM == "IV") %>%
  pivot_wider(names_from = Allele, values_from = Reads) %>%
  unnest() %>% 
  mutate(logOdds = log(Oak/Wine)) -> example.cb.logodds

#Plot these unsmoothed values
example.cb.logodds %>% ggplot(aes(x = POS, y = logOdds, color = C, group = E)) +
  geom_line() +
  geom_vline(aes(xintercept = 1000343), linetype = "dotted") +
      scale_color_manual(values = c("orange", "maroon")) +
  facet_grid(D ~ CHROM)

example.cb.logodds %>% ungroup() %>% 
  filter(CHROM == "IV", POS < (1000343 + 2000), POS > (1000343 - 1000)) %>%
  ggplot(aes(x = POS, y = logOdds, color = C, group = E)) +
  geom_point() +
  geom_vline(aes(xintercept = 1000343), linetype = "dotted") +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
      scale_color_manual(values = c("orange", "maroon")) +
  facet_grid(D ~ CHROM) + ggtitle("Pos 1000343 +/- 1kb")

example.cb.logodds %>% filter(POS == 1000343, CHROM == "IV") %>%
 ggplot(aes(x = C, y = logOdds, color = C)) +
  geom_boxplot() + 
  geom_point(size = 4, alpha = 0.6) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  xlab("Background Strain") +
    scale_color_manual(values = c("orange", "maroon")) +
  guides(color = "none") +
   facet_grid(~ D) +
  theme_bw()+ ggtitle("Pos 1000343 by Condition")

example.cb.logodds %>% filter(POS == 1000343, CHROM == "IV") %>%
 ggplot(aes(x = C, y = logOdds, color = C)) +
  geom_point(size = 4, alpha = 0.6) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") +
    scale_color_manual(values = c("orange", "maroon")) +
  guides(color = "none") +
  xlab("Background Strain") +
   facet_grid(E ~ D) +
  theme_bw()  + ggtitle("Pos 1000343, Condition x Replicate")
```

Comparing ratio counts using bar plots (geom_col)  

```{r}
#What do our ratios look like at this random position?
example.cb %>% filter(POS == 1000343, CHROM == "IV") %>%
  ggplot(aes(x = C, y = Reads, fill = Allele)) + geom_col(position = "fill") +
  geom_hline(aes(yintercept = 0.5), linetype = "dashed") +
  xlab("Parent (O = Oak XV)") +
    scale_fill_manual(values = c("orange", "maroon")) +
  facet_grid(E~D, scales = "free") +
  theme_bw() + ggtitle("Chromosome IV, Position 1000343")

#What do our ratios look like on the fixed chromosome?
example.cb %>% filter(CHROM == "XV", POS == 100003) %>%
  ggplot(aes(x = C, y = Reads, fill = Allele)) + geom_col(position = "fill") +
  geom_hline(aes(yintercept = 0.5), linetype = "dashed") +
  xlab("Parent (O = Wine XV)") +
  facet_grid(E~D, scales = "free") +
  scale_fill_manual(values = c("orange", "maroon")) +
  theme_bw() + ggtitle("Chromosome XV (fixed), Position 100003")
```

## Running a logistic regression on dilute vs copper without parent

```{r}
#Let's look at just one position and Dilute (D) versus Copper (C)
example.cb %>% filter(POS == 1000343, CHROM == "IV", D %in% c("D", "C")) -> sample_glm_input
```

Using glm() to calculate slope and z-score of generalized linear model for a single position.

```{r}
#need to make your category a factor
sample_glm_input %>% mutate_if(is.character, as.factor) %>% mutate(Bulk = D) -> input.fct

head(input.fct)

#Make sure D (dilute) is at 0
contrasts(input.fct$Bulk)
contrasts(input.fct$Bulk) <- c(1,0)

#Use glm() to calculate z-score and effect size
testglm <- glm(formula = "Allele ~ Bulk", 
               data = as.data.frame(input.fct), 
               weights = Reads, 
               family = binomial)

#Print your results
testglm

#Use summary() to get the useful results
summary(testglm)
```
Plotting what we just did here

```{r}

input.fct %>% 
  mutate(Bulk = as.numeric(Bulk == "C")) %>%
  pivot_wider(names_from = Allele, values_from = Reads) %>%
  group_by(D,E,POS, CHROM) %>%
  mutate(logOdds = log(Wine/Oak),
         totalReads = sum(Wine, Oak)) %>%
  ggplot(aes(x = as.numeric(Bulk), 
                         y = logOdds)) + 
  geom_jitter(aes(color = factor(Bulk), size = totalReads), width = 0, height = 0, size = 3, alpha = 0.5) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_abline(aes(slope = -0.02580, intercept = -0.07709), color = "red", linetype = "dashed") +
  geom_smooth(method = "lm",
              mapping = aes(weight = totalReads)) +
  xlim(-0.5, 1.5) + ylim(-1, 1) +
  scale_color_manual(values = c("black", "darkturquoise")) +
  ggtitle("Allele ~ Bulk") +
  theme(legend.position = "none") -> plot.bulk

plot.bulk
```


Using the EZ tools

```{r}
#Set contrasts to make your groups factors
sample_glm_input.fct <- ez_glmprep.setcontrasts(sample_glm_input, colname = "D", ctrl = "D", exp = "C")

#Compare these by running both at once:
head(sample_glm_input)
head(sample_glm_input.fct)

#Run this to get your z-score
ez_glm.single(sample_glm_input.fct, ReadsCol = "Reads", AlleleCol = "Allele", ExpCol = "D")

glm_cb2_short
```

Running a logistic regression on selection (dilute vs copper) x parent (oak vs wine XV)

```{r}
#need to make your category a factor
sample_glm_input %>% mutate_if(is.character, as.factor) %>% mutate(Bulk = D, Parent = C) -> input.fct.epistasis

head(input.fct.epistasis)

#Make sure D (dilute) is at 0
contrasts(input.fct.epistasis$Bulk)
contrasts(input.fct.epistasis$Bulk) <- c(1,0)

contrasts(input.fct.epistasis$Parent)
contrasts(input.fct.epistasis$Parent) <- c(-0.5,0.5)

#Use glm() to calculate z-score and effect size
testglm.epistasis <- glm(formula = "Allele ~ Bulk*Parent", 
               data = as.data.frame(input.fct.epistasis), 
               weights = Reads, 
               family = binomial)

#Print your results
testglm.epistasis

#Use summary() to get the useful results
summary(testglm.epistasis)

```

And to quickly plot what this looks like:  

```{r}

input.fct.epistasis %>% 
  mutate(Bulk = as.numeric(Bulk == "C")) %>%
  pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(Wine/Oak)) %>%
  ggplot(aes(x = as.numeric(Bulk), 
                         y = logOdds,
             color = factor(Parent))) + 
  geom_jitter(aes(), width = 0, height = 0, size = 3, alpha = 0.5) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_smooth(method = "lm") +
  xlim(-0.5, 1.5) + ylim(-1, 1) +
  scale_color_manual(values = c("orange", "maroon")) +
  theme(legend.position = "none") +
  ggtitle("Allele ~ B*P") -> plot.epistasis

library(cowplot)
plot_grid(plot.bulk, plot.epistasis)
```


# Practice 

## Example usage of all EZ functions

```{r}
#Where are you on your computer?
getwd()

#Do you have the files that you need in this directory?
dir()

#Do you have an output.table file in your directory? (This is gross code, who can make it better?)
dir()[which(grepl("output.table", dir()))]
```

```{r}
#Input is vcf output table, which should be in your CURRENT working directory
rawdata <- ez_getrawdata(tablefilename = "HGV.SortedCat.vcf.output.table")

head(rawdata)
unique(rawdata$CHROM)
```

```{r}
#add SNPs to the data frame
rawdata_called <- ez_callSNPs(mydata = rawdata)

head(rawdata_called)

```


```{r}
#smooth the reads column; MUST be named "Reads"
rawdata_smoothed <- ez_smooth(rawdata_called)

#print out which columns are which
ez_colselect(mydata = rawdata_smoothed, 
             mode = "SELECTCOLS")
```

```{r}
#use the above to select columns
dtest <- ez_colselect(mydata = rawdata_smoothed, mode = "FILTERCOLS", 
                      library = "HNGLVDRXY", keeplist = c("E"))
head(dtest)
```

```{r}
#set up what the control and experiment groups are for your bulk (experiment) column
#CHANGE THESE ARGUMENTS
torun <- ez_glmprep.setcontrasts(mydata = dtest, colname = "E", ctrl = "UnselectedA", exp = "UnselectedC")
head(torun)
```

```{r}
#run a single variable logistic regression
outputglm <- ez_glm.single(torun)
head(outputglm)
```

```{r}
#plot the output of the logistic regression
ez_plotting(outputglm, cutoff = 0.5)
```

## Practice for using EZ functions

Starting with these options, choose another library to analyze:

```{r}
ez_colselect(mydata = rawdata_smoothed, 
             mode = "SELECTCOLS")
```

Use ez_colselect() under FILTERCOLS mode to create a new test dataset

```{r}

```

Use ez_glmprep.setcontrasts() to decide which experiment groups you are comparing

```{r}

```

Use ez_glm.single() to produce your output

```{r}

```

Use ez_plotting() to make a plot of your glm output

```{r}

```

# Try this with your own data

```{r, eval = FALSE}
rawdata <- ez_getrawdata(tablefilename = "YOUR_FILE_HERE.output.table")

head(rawdata)
unique(rawdata$CHROM)
```

```{r}

```

