---
title: "All Traits Figures Dec 2024"
author: "Cass"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load packages
require(ggplot2)
require(tidyr)
require(dplyr)
require(reshape2)
require(cowplot)
require(data.table)

require(doParallel)
require(RColorBrewer)
require(scales)
require(circlize) 
require(stringr)
require(ggrepel)

require(cybrBSA)
require(lme4)

ggplot2::theme_set(theme_minimal() + theme(text = element_text(size = 10)) +
                     theme(#axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()))
```

# Figures

```{r}
Copper_CSS1_glm <- readRDS("covfilt/Copper_CSS1_glm_J25.rds")  
Copper_CSS8_glm <- readRDS("covfilt/Copper_CSS8_glm_J25.rds")  

Fluconazole_CSS1_glm <- readRDS("covfilt/Fluconazole_CSS1_glm_J25.rds") 
Fluconazole_CSS8_glm <- readRDS("covfilt/Fluconazole_CSS8_glm_J25.rds") 

Cyc_CSS1_glm <- readRDS("covfilt/Cyc_CSS1_glm_J25.rds") 
Cyc_CSS8_glm <- readRDS("covfilt/Cyc_CSS8_glm_J25.rds") 

H2O2_CSS1_glm <- readRDS("covfilt/H2O2_CSS1_glm_covfilt_c.rds") #remove trials 9 and 10, concat vcfs
H2O2_CSS8_glm <- readRDS("covfilt/H2O2_CSS8_glm_covfilt_c.rds") 

Ethanol_CSS1_glm <- readRDS("covfilt/Ethanol_CSS1_glm_J25.rds") 
Ethanol_CSS8_glm <- readRDS("covfilt/Ethanol_CSS8_glm_covfilt_H2LK2only.rds") 

Zeocin_CSS1_glm <- readRDS("covfilt/Zeocin_CSS1_glm_covfilt_c.rds") 
Zeocin_CSS8_glm <- readRDS("covfilt/Zeocin_CSS8_glm_covfilt_c.rds") 

PQ_CSS1_glm <- readRDS("covfilt/PQ_CSS1_glm_covfilt_xNAs.rds") 
PQ_CSS8_glm <- readRDS("covfilt/PQ_CSS8_glm_covfilt_xNAs.rds")

rbind(Copper_CSS1_glm,Copper_CSS8_glm,Fluconazole_CSS1_glm,Fluconazole_CSS8_glm,
      Cyc_CSS1_glm,Cyc_CSS8_glm,H2O2_CSS1_glm,H2O2_CSS8_glm,Ethanol_CSS1_glm, Ethanol_CSS8_glm,
      Zeocin_CSS1_glm,PQ_CSS1_glm,
      Zeocin_CSS8_glm,PQ_CSS8_glm) -> glms

########################

Copper_CSS1_q5 <- readRDS("covfilt/Copper_CSS1_q5_J25.rds") %>% mutate(Selection = "Copper", CSS = "Fixed I")
Copper_CSS8_q5 <- readRDS("covfilt/Copper_CSS8_q5_J25.rds") %>% mutate(Selection = "Copper", CSS = "Fixed VIII")

Fluconazole_CSS1_q5 <- readRDS("covfilt/Fluconazole_CSS1_q5_J25.rds") %>% mutate(Selection = "Fluconazole", CSS = "Fixed I")
Fluconazole_CSS8_q5 <- readRDS("covfilt/Fluconazole_CSS8_q5_J25.rds") %>% mutate(Selection = "Fluconazole", CSS = "Fixed VIII")

Cyc_CSS1_q5 <- readRDS("covfilt/Cyc_CSS1_q5_J25.rds") %>% mutate(Selection = "Cycloheximide", CSS = "Fixed I")
Cyc_CSS8_q5 <- readRDS("covfilt/Cyc_CSS8_q5_J25.rds") %>% mutate(Selection = "Cycloheximide", CSS = "Fixed VIII")

#Forgot to change these to c in name but should be the new ones
H2O2_CSS1_q5 <- readRDS("covfilt/H2O2_CSS1_q5_J25.rds") %>% mutate(Selection = "H2O2", CSS = "Fixed I")
H2O2_CSS8_q5 <- readRDS("covfilt/H2O2_CSS8_q5_J25.rds") %>% mutate(Selection = "H2O2", CSS = "Fixed VIII")

Ethanol_CSS1_q5 <- readRDS("covfilt/Ethanol_CSS1_q5_J25.rds") %>% mutate(Selection = "Ethanol", CSS = "Fixed I")
Ethanol_CSS8_q5 <- readRDS("covfilt/Ethanol_CSS8_q5_J25.rds") %>% mutate(Selection = "Ethanol", CSS = "Fixed VIII")

Zeocin_CSS8_q5 <- readRDS("covfilt/Zeocin_CSS8_q5_J25.rds") %>% mutate(Selection = "Zeocin", CSS = "Fixed VIII")
Paraquat_CSS8_q5 <- readRDS("covfilt/Paraquat_CSS8_q5_J25.rds") %>% mutate(Selection = "Paraquat", CSS = "Fixed VIII")

Zeocin_CSS1_q5 <- readRDS("covfilt/Zeocin_CSS1_q5_J25.rds") %>% mutate(Selection = "Zeocin", CSS = "Fixed I")
Paraquat_CSS1_q5 <- readRDS("covfilt/Paraquat_CSS1_q5_J25.rds") %>% mutate(Selection = "Paraquat", CSS = "Fixed I")

################################################################################

Copper_CSS1_q5_s15 <- readRDS("covfilt/Copper_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Copper", CSS = "Fixed I")
Copper_CSS8_q5_s15 <- readRDS("covfilt/Copper_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Copper", CSS = "Fixed VIII")

Fluconazole_CSS1_q5_s15 <- readRDS("covfilt/Fluconazole_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Fluconazole", CSS = "Fixed I")
Fluconazole_CSS8_q5_s15 <- readRDS("covfilt/Fluconazole_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Fluconazole", CSS = "Fixed VIII")

Cyc_CSS1_q5_s15 <- readRDS("covfilt/Cyc_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Cycloheximide", CSS = "Fixed I")
Cyc_CSS8_q5_s15 <- readRDS("covfilt/Cyc_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Cycloheximide", CSS = "Fixed VIII")

#Forgot to change these to c in name but should be the new ones
H2O2_CSS1_q5_s15 <- readRDS("covfilt/H2O2_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "H2O2", CSS = "Fixed I")
H2O2_CSS8_q5_s15 <- readRDS("covfilt/H2O2_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "H2O2", CSS = "Fixed VIII")

Ethanol_CSS1_q5_s15 <- readRDS("covfilt/Ethanol_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Ethanol", CSS = "Fixed I")
Ethanol_CSS8_q5_s15 <- readRDS("covfilt/Ethanol_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Ethanol", CSS = "Fixed VIII")

Zeocin_CSS8_q5_s15 <- readRDS("covfilt/Zeocin_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Zeocin", CSS = "Fixed VIII")
Paraquat_CSS8_q5_s15 <- readRDS("covfilt/Paraquat_CSS8_q5_covfilt_s15.rds") %>% mutate(Selection = "Paraquat", CSS = "Fixed VIII")

Zeocin_CSS1_q5_s15 <- readRDS("covfilt/Zeocin_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Zeocin", CSS = "Fixed I")
Paraquat_CSS1_q5_s15 <- readRDS("covfilt/Paraquat_CSS1_q5_covfilt_s15.rds") %>% mutate(Selection = "Paraquat", CSS = "Fixed I")

################################################################################

rbind(Copper_CSS1_q5,Copper_CSS8_q5,Fluconazole_CSS1_q5,Fluconazole_CSS8_q5,
      Zeocin_CSS1_q5, Paraquat_CSS1_q5, Zeocin_CSS8_q5, Paraquat_CSS8_q5,
      Cyc_CSS1_q5,Cyc_CSS8_q5,H2O2_CSS1_q5,H2O2_CSS8_q5,Ethanol_CSS1_q5, Ethanol_CSS8_q5) -> q5s

rbind(Copper_CSS1_q5_s15,Copper_CSS8_q5_s15,Fluconazole_CSS1_q5_s15,Fluconazole_CSS8_q5_s15,
      Zeocin_CSS1_q5_s15, Paraquat_CSS1_q5_s15, Zeocin_CSS8_q5_s15, Paraquat_CSS8_q5_s15,
      Cyc_CSS1_q5_s15,Cyc_CSS8_q5_s15,H2O2_CSS1_q5_s15,H2O2_CSS8_q5_s15,Ethanol_CSS1_q5_s15, Ethanol_CSS8_q5_s15) -> q5_s15s

q5_s15s %>% mutate(q15 = quant) %>% select(-quant) %>% merge(q5s) -> allQs

saveRDS(allQs, file = "allQs_coveragefiltered.rds") 

glms %>% merge(allQs) -> AllTrait_glms

saveRDS(AllTrait_glms, file = "CoverageFiltered_AllTrait_glms.rds")
```

```{r, fig.width=12, fig.height=5, eval = FALSE}

Cyc_CSS1_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  geom_hline(data = Cyc_CSS1_q5[Cyc_CSS1_q5$label != "cept",], aes(yintercept = quant, color = label)) +
  geom_hline(data = Cyc_CSS1_q5[Cyc_CSS1_q5$label != "cept",], aes(yintercept = -quant, color = label)) +
  facet_grid(~CHROM, scales = "free", space = "free") + ggtitle("Cyc_CSS1_glm")

Cyc_CSS8_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Cyc_CSS8_glm")

H2O2_CSS1_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("H2O2_CSS1_glm")

H2O2_CSS8_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("H2O2_CSS8_glm")

Fluconazole_CSS1_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Fluconazole_CSS1_glm")

Fluconazole_CSS8_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Fluconazole_CSS8_glm")

Copper_CSS1_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Copper_CSS1_glm") 

Copper_CSS8_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Copper_CSS8_glm")

Ethanol_CSS1_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Ethanol_CSS1_glm") 

Ethanol_CSS8_glm %>% filter(label != "cept") %>% ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() +
  facet_grid(~CHROM, scales = "free", space = "free")+ ggtitle("Ethanol_CSS8_glm")


```

```{r, fig.width=10, fig.height=6}
glms %>% filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label, linetype = CSS)) + geom_line() +
  facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("Bulk and Interactions") +
  scale_color_manual(values = c("navyblue", "darkorange")) + 
  theme(legend.position = "bottom") 
```

```{r, eval = FALSE}
H2O2_G200<- readRDS("covfilt/H2O2_G200_covfilt.rds")
H2O2_G200 %>% na.omit() %>% 
  filter(grepl(8, Parent)) %>%
  mutate_if(is.character, as.factor) -> H2O2_CSS8_factor

H2O2_CSS8_factor %>% filter(CHROM == "XV", POS < 4.6e5, POS > 4.58e5, grepl("8", Parent)) -> tempdf

table(tempdf$POS)

H2O2_CSS8_factor %>% filter(CHROM == "XV", POS < 4.6e5, POS > 4.58e5, grepl("8", Parent)) %>%
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>%
  mutate(logOdds = log(Wine/Oak)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Parent)) + geom_point(alpha = 0.4) +
  facet_grid("Bulk") +
  theme(legend.position = "bottom")

H2O2_CSS8_factor %>% group_by(CHROM, POS) %>% count(POS) -> doesthiswork

doesthiswork %>% filter(n == 80)

table(doesthiswork$n)

H2LK2DMX2 %>% filter(POS == 169833, CHROM == "IV",  Dataset == "Wine8_D_17") %>% distinct()
H2O2_Unsmoothed %>% filter(POS == 169833, CHROM == "IV", Dataset == "Wine8_D_17") 
H2O2_G200 %>% filter(POS == 169833, CHROM == "IV", Dataset == "Wine8_D_17") 
H2O2_G200_edit %>% filter(POS == 169833, CHROM == "IV", Dataset == "Wine8_D_17") 
H2O2_CSS1_factor %>% filter(POS == 169833, CHROM == "IV", Dataset == "Wine8_D_17") 
H2O2_CSS8_factor %>% filter(POS == 169833, CHROM == "IV", Dataset == "Wine8_D_17") 

```

```{r, eval = FALSE}
#Without cutoffs

glms %>% filter(label %in% c("Bulk"), Selection == "H2O2", CHROM == "XV", POS < 4.6e5, POS > 4.58e5, CSS == "Fixed VIII") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = as.factor(POS))) + geom_point(alpha = 0.4) +
  facet_grid(CSS~CHROM, scales = "free", space = "free") + ggtitle("H2O2 Bulk only") +
  theme(legend.position = "bottom") 

glms %>% filter(label %in% c("Bulk"), Selection == "Zeocin", CHROM == "XV") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = CSS, linetype = CSS)) + geom_point(size = 0.2, alpha = 0.4) +
  facet_grid(CSS~CHROM, scales = "free", space = "free") + ggtitle("Zeocin Bulk only") +
  scale_color_manual(values = c("navyblue", "darkorange")) + 
  theme(legend.position = "bottom") 
```


```{r, fig.width=12, fig.height=5}
glms %>% filter(label == "Bulk") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = Selection, linetype = CSS)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("Bulk by Selection") +
  theme(legend.position = "bottom")

glms %>% filter(label %in%  c("cept", "Background")) %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = Selection, linetype = CSS)) + geom_line() +
  facet_grid(label~CHROM, scales = "free", space = "free")+ ggtitle("Background and Intercept") +
  theme(legend.position = "bottom")

################################################################################

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "Ethanol") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3)) +
  ggtitle("Ethanol")

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "Copper") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))+
  ggtitle("Copper")

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "Fluconazole") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))+
  ggtitle("Fluconazole")

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "Cycloheximide") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))+
  ggtitle("Cycloheximide")

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "H2O2") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))+
  ggtitle("H2O2")

AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction"), Selection == "Zeocin") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line() +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = quant, color = label)) +
  scale_color_manual(values = c("black", "firebrick2")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))+
  ggtitle("Zeocin")
```

```{r, fig.width=8, fig.height=6}
AllTrait_glms %>% filter(label == "Bulk") %>% ggplot(aes(x = POS, y = abs(zscore), color = CSS)) + geom_line() +
  facet_grid(Selection~CHROM, scales = "free", space = "free")+ 
  geom_hline(aes(yintercept = quant, color = CSS, linetype = CSS)) +
  scale_color_manual(values = c("navyblue", "darkorange")) +
  ggtitle("Bulk Effects")+
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))

AllTrait_glms %>% filter(label == "Interaction") %>% ggplot(aes(x = POS, y = abs(zscore), color = CSS)) + geom_line() +
  facet_grid(Selection~CHROM, scales = "free", space = "free")+ 
  geom_hline(aes(yintercept = quant, color = CSS, linetype = CSS)) +
  scale_color_manual(values = c("navyblue", "darkorange")) +
  ggtitle("Interaction Effects") +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))

```

Using the cutoff of highest Chr III value

```{r, fig.width=8, fig.height=6}
AllTrait_glms %>% filter(CHROM == "III") %>%
  group_by(label, CSS) %>%
  summarize(Max3 = max(abs(zscore))) %>% merge(AllTrait_glms) -> AllTrait_glms_3

AllTrait_glms_3 %>% filter(label == "Interaction") %>% ggplot(aes(x = POS, y = abs(zscore ), color = CSS)) + geom_line() +
  facet_grid(Selection~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = Max3, color = CSS, linetype = CSS)) +
  scale_color_manual(values = c("navyblue", "darkorange")) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))

AllTrait_glms_3 %>% filter(label == "Interaction") %>% ggplot(aes(x = POS, y = abs(zscore), color = Selection)) + geom_line() +
    geom_hline(aes(yintercept = quant, color = Selection), linetype = "dashed") +
  facet_grid(CSS~CHROM, scales = "free", space = "free")+ ggtitle("") +
  geom_hline(aes(yintercept = Max3)) +
  theme(legend.position = "bottom") + scale_linetype_manual(values = c(2,3))
```

## Find bulk peaks

Remaking the logpeak function

```{r}
cybr_lmpeaks2 <- function(Data, cutoff, width = 700, labelgroup = "Bulk"){
  CrossoverPoints <- Data %>% mutate(abs_zscore = abs(zscore)) %>% 
        mutate_at(vars(abs_zscore), funs(replace(., . < cutoff, 
            -2))) %>% arrange(POS) %>% group_by(CSS, CHROM) %>% 
        summarize(POS = POS, abs_zscore = abs_zscore, smooth_abs_z = frollapply(abs_zscore, 
            mean, n = 1, align = "center")) %>% na.omit() %>% 
        group_by(CHROM, CSS) %>% arrange(POS) %>% summarize(POS = POS, 
        abs_zscore = abs_zscore, smooth_abs_z = smooth_abs_z, 
        slope = frollapply(smooth_abs_z, FUN = slope_change, 
            n = width, align = "center")) %>% mutate(negative = slope < 
        0) %>% na.omit() %>% summarize(POSc = POS, crossover = frollapply(negative, 
        FUN = subtract2, n = 2)) %>% filter(crossover == 1)
    
    tempStartEnd <- data.frame(CHROM = as.factor(as.character(as.roman(1:16)))) %>% 
        merge(data.frame(CSS = unique(Data$CSS))) %>% mutate(POSc = 1, 
        crossover = 0) %>% rbind(CrossoverPoints) %>% group_by(CHROM, 
        CSS) %>% arrange(POSc) %>% mutate(order = paste("A", 
        row_number(POSc), sep = "_")) %>% select(-crossover) %>% 
        pivot_wider(names_from = order, values_from = POSc) %>% 
        pivot_longer(cols = starts_with("A"), names_to = "segment", 
            values_to = "value") %>% filter(!is.na(value)) %>% 
        arrange(CHROM, CSS, value) %>% group_by(CHROM, CSS) %>% 
        mutate(End = lead(value, default = Inf)) %>% ungroup() %>% 
        rename(Start = value) %>% select(CHROM, CSS, Start, End)
    peakdata <- data.frame(CHROM = NA, CSS = NA, zscore = NA)
    for (i in unique(tempStartEnd$CHROM)) {
        for (c in unique(tempStartEnd$CSS)) {
            newtemp <- tempStartEnd %>% filter(CHROM == i, CSS == 
                c)
            for (k in 1:length(newtemp$Start)) {
                something <- Data %>% filter(CHROM == i, CSS == 
                  c, label == labelgroup) %>% filter(POS > newtemp$Start[k], 
                  POS < newtemp$End[k]) %>% ungroup() %>% group_by(CHROM, 
                  CSS) %>% summarize(zscore = max(abs(zscore)))
                peakdata <- rbind(peakdata, something)
            }
            rm(newtemp)
        }
    }
    peaks <- Data %>% mutate(zscore = abs(zscore)) %>% merge(peakdata) %>% 
        filter(zscore > cutoff)
    return(peaks)
}

```

Make a loop to do the cutoffs?

```{r}
AllTrait_glms <- readRDS("CoverageFiltered_AllTrait_glms.rds")

AllTrait_glms %>% merge(SNPEff_table) -> AllTraits_snpeff_glms

AllTraits_snpeff_glms %>% filter(label %in% c("Bulk", "Interaction")) %>%
  filter(CHROM %in% c("XV")) %>%
  ggplot(aes(x= POS, y = abs(zscore), color = label, linetype = CSS)) +
  geom_hline(aes(yintercept = quant, linetype = CSS)) +
  geom_line() +
  geom_point(aes(size = Annotation_Impact == "HIGH"), alpha = 0.4) +
  scale_size_manual(values = c(0,3)) +
  # geom_point(data = BulkPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  # geom_point(data = IntPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  facet_grid(Selection ~ CHROM, scales = "free", space = "free") +
  theme(legend.position = "bottom") +
  #ylim(0, 15) +
  scale_color_manual(values = c("black", "red"))


AllTraits_snpeff_glms %>% filter(label %in% c("Bulk", "Interaction")) %>%
  filter(CHROM %in% c("VIII", "VII")) %>%
  ggplot(aes(x= POS, y = abs(zscore), color = label, linetype = CSS)) +
  geom_hline(aes(yintercept = quant, linetype = CSS)) +
  geom_line() +
  geom_point(aes(size = Annotation_Impact == "HIGH"), alpha = 0.4) +
  scale_size_manual(values = c(0,3)) +
  # geom_point(data = BulkPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  # geom_point(data = IntPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  facet_grid(Selection ~ CHROM, scales = "free", space = "free") +
  theme(legend.position = "bottom") +
  geom_vline(xintercept = 492468) +
  #ylim(0, 15) +
  scale_color_manual(values = c("black", "red"))

AllTraits_snpeff_glms %>% filter(label == "Bulk", CHROM == "VII") %>%
  arrange(desc(abs(zscore)))

SNPEff_table %>% filter(CHROM == "VII", POS <= 492468, POS > 400000) %>%
  filter(Annotation_Impact == "HIGH")

SNPEff_table %>% filter(CHROM == "VII", POS > 492468 - 10000, POS < 492468 + 10000) %>%
  count(Gene_Name, Annotation_Impact) %>%
  pivot_wider(names_from = Annotation_Impact, values_from = n)

#This will fail without loading in pSNPs:
SNPEff_table %>% filter(Gene_Name == "PMA1") %>% filter(Annotation_Impact == "MODERATE") %>% merge(pSNPs) %>%
  pivot_wider(names_from = Type, values_from = Annotation_Impact)

SNPEff_table %>% filter(CHROM == "VIII", POS < 212720+6000, POS > 212720 - 6000) 

```


```{r, eval = FALSE}
#Bulk Cutoffs
BulkCutoffs <- AllTrait_glms[1,] %>% mutate(label = "BLANK")
for(s in unique(AllTrait_glms$Selection)){
  for(c in unique(AllTrait_glms$CSS)){
    AllTrait_glms %>% filter(CSS == c, Selection == s, label == "Bulk") -> subsetGLMs

    tempcutoffs <- cybr_lmpeaks2(subsetGLMs, cutoff = unique(subsetGLMs$q15))
    
    BulkCutoffs <- rbind(BulkCutoffs, tempcutoffs)
    rm(tempcutoffs)
  }
}

#Interaction Cutoffs
IntCutoffs <- AllTrait_glms[1,] %>% mutate(label = "BLANK")
for(s in unique(AllTrait_glms$Selection)){
  for(c in unique(AllTrait_glms$CSS)){
    AllTrait_glms %>% filter(CSS == c, Selection == s, label == "Interaction")  -> subsetGLMs

    tempcutoffs <- cybr_lmpeaks2(subsetGLMs, cutoff = unique(subsetGLMs$q15), labelgroup = "Interaction")

    IntCutoffs <- rbind(IntCutoffs, tempcutoffs)
    rm(tempcutoffs)
  }
}

saveRDS(BulkCutoffs, file = "covfilt/BulkCutoffs_cf.rds")
saveRDS(IntCutoffs, file = "covfilt/IntCutoffs_cf.rds")
```

# Plotting Together

```{r}
BulkPeaks <- readRDS("covfilt/BulkCutoffs_cf.rds") %>% filter(label != "BLANK")
IntPeaks <- readRDS("covfilt/IntCutoffs_cf.rds") %>% filter(label != "BLANK")

# BulkPeaks <- readRDS("BulkCutoffs.rds") %>% filter(label != "BLANK")
# IntPeaks <- readRDS("IntCutoffs.rds") %>% filter(label != "BLANK")

#AllTrait_glms <- readRDS("CoverageFiltered_AllTrait_glms.rds")

```

```{r, fig.height=7, fig.width=7}
AllTrait_glms %>% filter(label %in% c("Bulk", "Interaction")) %>%
  ggplot(aes(x= POS, y = abs(zscore), color = label, linetype = CSS)) +
  geom_hline(aes(yintercept = quant, linetype = CSS)) +
  geom_line() +
  geom_point(data = BulkPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  geom_point(data = IntPeaks, aes(x = POS, y = zscore), alpha = 0.2) +
  facet_grid(Selection ~ CHROM, scales = "free", space = "free") +
  theme(legend.position = "bottom") +
  ylim(0, 15) +
  scale_color_manual(values = c("black", "red"))
  
```


## Correlations

```{r}
BulkPeaks %>%
  rbind(IntPeaks) -> Peaks

Peaks %>%
  group_by(label, Selection, CSS) %>% count() %>% 
  
  pivot_wider(names_from = label, values_from = n) -> tempNAs

tempNAs[is.na(tempNAs)] <- 0  
        
tempNAs %>% mutate(Selection = gsub("Cycloheximide", "Cyc", Selection),
         Selection = gsub("Copper", "Cu", Selection),
         Selection = gsub("Fluconazole", "Fluc", Selection),
         Selection = gsub("Ethanol", "EtOH", Selection),
         Selection = gsub("Zeocin", "Zeo", Selection),
         Selection = gsub("Paraquat", "PQ", Selection)) %>%
   ggplot(aes(x = Interaction, y = Bulk, color = CSS, fill = CSS)) + geom_point(aes(shape = CSS), size = 4, alpha = 0.6) +
  scale_color_manual(values = c("navy", "darkorange")) +
  scale_fill_manual(values = c("navy", "darkorange")) +
  theme_bw() + ggtitle("Counts") +
  theme(legend.position = "bottom") +
  ylim(0, 65) +
  geom_smooth(method = "lm", alpha = 0.2) -> mylmplot

Peaks %>% mutate(Selection = gsub("Cycloheximide", "Cyc", Selection),
         Selection = gsub("Copper", "Cu", Selection),
         Selection = gsub("Fluconazole", "Fluc", Selection),
         Selection = gsub("Ethanol", "EtOH", Selection),
         Selection = gsub("Zeocin", "Zeo", Selection),
         Selection = gsub("Paraquat", "PQ", Selection)) %>%
  group_by(label, Selection, CSS) %>% 
  ggplot(aes(x = Selection, fill = label)) + 
  geom_bar(position = position_stack(reverse = TRUE), ) +
  scale_fill_manual(values = c("black", "red3")) +
  facet_grid(rows = "CSS") +
  theme_bw() + theme(legend.position = "bottom") +
  ggtitle("QTL per Resistance Trait") -> mybarplot

cowplot::plot_grid(mylmplot, mybarplot, rel_widths = c(1,2))

```

```{r}

Peaks %>% group_by(label, Selection, CSS) %>% 
  mutate(CSS = as.factor(CSS)) %>%
  distinct() %>%
  mutate(Selection = gsub("Cycloheximide", "Cyc", Selection),
         Selection = gsub("Copper", "Cu", Selection),
         Selection = gsub("Fluconazole", "Fluc", Selection),
         Selection = gsub("Ethanol", "EtOH", Selection),
         Selection = gsub("Zeocin", "Zeo", Selection),
         Selection = gsub("Paraquat", "PQ", Selection)) %>%
  #mutate(Selection = substr(Selection, 1, 6)) %>%
  #filter(label == "Bulk") %>%
  ggplot(aes(x = zscore, y = CSS, color = CSS)) + 
  geom_boxplot(outliers = FALSE, size = 0.8) +
  
  geom_jitter(alpha = 0.4, height = 0.1, width = 0) +
  geom_vline(aes(xintercept =quant), color = "firebrick", size = 1, alpha = 0.4) +
  geom_vline(aes(xintercept =q15), color = "red", size = 1, alpha = 0.4) +
  #geom_point(aes(x =quant, y = CSS), color = "red", size = 2, alpha = 0.4, shape = 5) +
  scale_color_manual(values = c("navy", "darkorange")) +
  #facet_grid(rows = "Selection") +
  theme_bw() + theme(legend.position = "bottom") +
  theme(axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        axis.title.y = element_blank()) +
  xlab("| zscore |") +
  ggtitle("QTL magnitudes per resistance trait") +
  facet_grid(Selection~label, space = 'free', scales = "free_x") +
  scale_x_continuous(breaks = c(1,5,10, 15, 20)) 
```

```{r}
AllTrait_glms %>% select(-quant, -q15) %>% pivot_wider(names_from = label, values_from = zscore) -> AllTrait_wide

# AllTrait_wide %>% ggplot(aes(x = (Bulk), y = (Interaction), color = Selection)) + geom_point(alpha = 0.2, size = 0.2) +
#   #scale_color_manual(values = c("blue", "darkorange")) + 
#   geom_smooth(method = "lm")

# AllTrait_wide %>% filter(Selection == "Cycloheximide") %>% ggplot(aes(x = (Bulk), y = (Interaction), color = CSS)) + geom_point(alpha = 0.2, size = 0.2) +
#   scale_color_manual(values = c("blue", "darkorange")) + geom_smooth(method = "lm")

summary(lm(data = AllTrait_wide, formula = abs(Interaction) ~ abs(Bulk) + CSS))
summary(lm(data = AllTrait_wide, formula = abs(Interaction) ~ abs(Bulk) + Selection))

# for(i in unique(AllTrait_wide$Selection)){
#   print(i)
#   print(summary(lm(data = AllTrait_wide[AllTrait_wide$Selection == i,], formula = abs(Interaction) ~ abs(Bulk))))
# 
# }
# 
# for(i in unique(AllTrait_wide$Selection)){
#   print(i)
#   print(summary(lm(data = AllTrait_wide[AllTrait_wide$Selection == i,], formula = (Interaction) ~ (Bulk))))
# }

cor(x = AllTrait_wide$Bulk, y = AllTrait_wide$Interaction)

cor(abs(AllTrait_wide$Bulk[1:300000]), abs(AllTrait_wide$Interaction[1:300000]), method = "spearman")

```

Bootstrapping for correlation between bulk and interactions

```{r, message=FALSE, warning=FALSE, eval = FALSE}
AllTrait_glms %>% select(-quant, -q15) %>% pivot_wider(names_from = label, values_from = zscore) -> AllTrait_wide

AllTrait_wide %>% mutate(ID = row_number()) -> BootstrappingDF

alloutput <- data.frame(Rsquared = NA, Intercept = NA, Bulk = NA)
BootstrappingDF %>% filter(Selection == "Copper") -> Copper_boot

for(i in 1:1000){
  Copper_boot %>% group_by(Selection, CSS, CHROM) %>%
  summarize(IDs = sample(ID, size = 1)) -> mysample
  
  BootstrappingDF_sample <- BootstrappingDF[BootstrappingDF$ID %in% mysample$IDs,]
  
  slm <- summary(lm(BootstrappingDF_sample$Interaction ~ BootstrappingDF_sample$Bulk))
  output <- c(slm$r.squared, slm$coefficients[5:6])
  
  alloutput <- rbind(alloutput, output)
}

saveRDS(alloutput, file = "Copper_nonpeak_covfilt_BxI_bootstrap.rds")

alloutput %>% ggplot(aes(x = Rsquared)) + geom_density() + theme_classic()
alloutput %>% ggplot(aes(x = Bulk)) + geom_density() + theme_classic()

```

```{r}
alloutput <- readRDS("Copper_nonpeak_covfilt_BxI_bootstrap.rds")
BulkPeaks <- readRDS("covfilt/BulkCutoffs_cf.rds") %>% filter(label != "BLANK")
IntPeaks <- readRDS("covfilt/IntCutoffs_cf.rds") %>% filter(label != "BLANK")

AllTrait_glms <- readRDS("CoverageFiltered_AllTrait_glms.rds")

```

```{r}
AllTrait_glms %>% filter(Selection == "Copper", label %in% c("Interaction")) %>%
  select(Selection, CSS, CHROM, POS, Intz = zscore) -> c_ints

BulkPeaks %>% merge(c_ints) -> BxI_R2

AllTrait_glms %>% filter(Selection == "Copper", label %in% c("Bulk")) %>%
  select(Selection, CSS, CHROM, POS, Intz = zscore) -> c_bulks

IntPeaks %>% merge(c_bulks) -> IxB_R2

print("The Bulk peaks R2 is:", quote = FALSE)
summary(lm(BxI_R2$zscore ~ BxI_R2$Intz))$r.squared

print("The absolute value of Bulk peak R2 is:", quote = FALSE)
summary(lm(abs(BxI_R2$zscore) ~ abs(BxI_R2$Intz)))$r.squared

print("The Interaction peak R2 is:", quote = FALSE)
summary(lm(IxB_R2$zscore ~ IxB_R2$Intz))$r.squared

print("The absolute value of interaction peaks R2 is:", quote = FALSE)
summary(lm(abs(IxB_R2$zscore) ~ abs(IxB_R2$Intz)))$r.squared

print("The 95% quantile of the uncorrelated absolute values bootstrapped is:", quote = FALSE)
quantile(alloutput$Rsquared, 0.95, na.rm = TRUE)

BxI_R2 %>% ggplot(aes(x = zscore, y = Intz)) + geom_point(size = 2, alpha = 0.8) + 
  ylab("Corresponding z-score") + xlab("Peak z-score") +
  geom_smooth(method = "lm", color = "black") + ggtitle("Bulk peaks x Interactions") + theme_bw() -> cp1
IxB_R2 %>% ggplot(aes(x = zscore, y = Intz)) + geom_point(size = 2, alpha = 0.8) + 
  ylab("Corresponding z-score") + xlab("Peak z-score") +
  geom_smooth(method = "lm", color = "red") + ggtitle("Interaction peaks x Bulks")  + theme_bw() -> cp2
  
BxI_R2 %>% ggplot(aes(x = abs(zscore), y = abs(Intz))) + geom_point(size = 2, alpha = 0.8) + 
  ylab("Corresponding |z-score|") + xlab("Peak |z-score|") +
  geom_smooth(method = "lm", color = "black") + ggtitle("|Bulk peaks| x |Interactions|") + theme_bw()  -> cp3
IxB_R2 %>% ggplot(aes(x = abs(zscore), y = abs(Intz))) + geom_point(size = 2, alpha = 0.8) + 
  ylab("Corresponding |z-score|") + xlab("Peak |z-score|") +
  geom_smooth(method = "lm", color = "red") + ggtitle("|Interaction peaks| x |Bulks|")  + theme_bw() -> cp4

plot_grid(cp1, cp2)
plot_grid(cp3, cp4)
  
```

Correlate the peaks from CuSO4

```{r}
AllTrait_glms %>% select(-quant, -q15) %>% pivot_wider(names_from = label, values_from = zscore) -> AllTrait_wide

AllTrait_wide %>% mutate(ID = row_number()) -> BootstrappingDF

BulkPeaks %>%
  rbind(IntPeaks) -> Peaks

Peaks %>% filter(Selection == "Copper", label == "Bulk") %>% select(-quant, -q15) %>%
  pivot_wider(names_from = label, values_from = zscore) %>%
  select(-Bulk) %>%
  merge(BootstrappingDF) -> IntTest

summary(lm(abs(IntTest$Interaction) ~ abs(IntTest$Bulk)))
summary(lm(abs(IntTest$Bulk) ~ abs(IntTest$Interaction)))

IntTest %>% ggplot(aes(x = abs(Bulk), y = abs(Interaction))) + 
  geom_point(aes(color = CSS, fill = CSS)) +
  geom_smooth(method = "lm", aes(color = CSS, fill = CSS), alpha = 0.2) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0) +
  ggtitle("CuSO4 Bulk Peak Correlations") +
  theme_bw()

IntTest %>% ggplot(aes(x = abs(Bulk), y = abs(Interaction))) + 
  geom_point(aes(color = CHROM), size = 4, alpha = 0.3) +
  #geom_smooth(method = "lm", aes(color = CSS, fill = CSS), alpha = 0.2) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0) +
  ggtitle("CuSO4 Bulk x Interaction Peak Correlations") +
  theme_bw()
```

```{r}

Peaks %>% filter(label == "Bulk") %>% select(-quant, -q15) %>%
  pivot_wider(names_from = label, values_from = zscore) %>%
  select(-Bulk) %>%
  merge(BootstrappingDF) -> IntTest_all

summary(lm(abs(IntTest_all$Interaction) ~ abs(IntTest_all$Bulk)))
summary(lm(abs(IntTest_all$Bulk) ~ abs(IntTest_all$Interaction)))

IntTest_all %>% ggplot(aes(x = abs(Bulk), y = abs(Interaction))) + 
  geom_point(aes(color = CSS, fill = CSS)) +
  geom_smooth(method = "lm", aes(color = CSS, fill = CSS), alpha = 0.2) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0) +
  ggtitle("All Bulk Peak Correlations with Interaction Effects") +
  theme_bw()

IntTest_all %>% ggplot(aes(x = abs(Bulk), y = abs(Interaction))) + 
  geom_point(aes(color = Selection)) +
  geom_smooth(method = "lm", aes(color = Selection, fill = Selection), alpha = 0.2) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0) +
  ggtitle("All Bulk Peak Correlations with Interaction Effects") +
  theme_bw()

IntTest_all %>% filter(abs(Interaction) > 2)

```

## Better correlations

Look between pearson and spearman, try ranks for the entire dataset but values for the peaks.

```{r}
cor(x = abs(IntTest_all$Interaction), y = abs(IntTest_all$Bulk), method = "pearson")
cor(x = abs(IntTest_all$Interaction), y = abs(IntTest_all$Bulk), method = "spearman")

summary(lm(abs(IntTest$Interaction) ~ abs(IntTest$Bulk)))
summary(lm(abs(IntTest$Bulk) ~ abs(IntTest$Interaction)))

0.55^2
0.45^2
```
### How much of the YPD is nitrogen vs KAc?

Y - 10% nitrogen | 2% of solution
P - 12% nitrogen | 1% of solution
D - should be 0? Because C6H12O6?

KAc: (K+) and acetate (CH3COO−)

```{r}
N_YPD_perL <- sum(0.1*20, 0.12*10)

Dilution_1to50 <- N_YPD_perL/50

print(paste("Normal media has", N_YPD_perL, "g nitrogen/L"), quote = FALSE)
print(paste("1:50 YPD in 1% KAc media has", Dilution_1to50, "g nitrogen/L"), quote = FALSE)
print(paste("Sporulation (2% KAc) media has 0", "g Nitrogen/L"), quote = FALSE)

```

### How much carbon is in each dilution?

Y - 49% carbon | 2% of solution
P - 50% carbon | 1% of solution
D - 40% if you ask chatgpt to do the math on C6H12O6?

KAc: (K+) and acetate (CH3COO−), 24.5%

```{r}
C_YPD_perL <- sum(0.49*20, 0.5*10, 0.4*20)
C_KAc_perL <- 0.245*1000

C_Dilution_1to50 <- sum(C_YPD_perL/50, C_KAc_perL/100)

C_KAc_2percent <- C_KAc_perL/50

print(paste("Normal media has", C_YPD_perL, "g carbon/L"), quote = FALSE)
print(paste("1:50 YPD in 1% KAc media has", C_Dilution_1to50, "g carbon/L"), quote = FALSE)
print(paste("Sporulation (2% KAc) media has", C_KAc_2percent, "g carbon/L"), quote = FALSE)
```
The Kruglyak sporulation media ends up having more Nitrogen (0.064 g/L) and less carbon (3g/L rather than 5 g/L), which allows for sporulation of the Oak CSS 15 cells (Containing Oak Chr 15). 
