---
title: "GLM_ComparingBulks"
author: "Cassandra Buzby"
date: "7/19/2022"
output:
  html_document:
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

#Load packages
library(ggplot2)
library(tidyr)
#library(tidyverse)
library(reshape2)
library(cowplot)
library(dplyr)
library(foreach)
library(doParallel)


#ggplot2::theme_set(theme_light())
ggplot2::theme_set(theme_cowplot())


CBchromPalette <- c("#F26430", "#0A369D", "#7EA3CC","#FF9F1C", "#C14953","#92DCE5", "#8FC93A","#4C4C47", 
                   "#F26430", "#0A369D", "#7EA3CC","#FF9F1C", "#C14953","#92DCE5", "#8FC93A","#4C4C47",
                  "#F26430", "#0A369D", "#7EA3CC")

CBchromPalette_ext <- c("#F26430", "#0B0B45", "#7EA3CC","#FF9F1C", "#C14953","#92DCE5", "#8FC93A","#4C4C47", 
                   "#1E64AA", "#32936F", "#FEC601","#8DAA9D", "#7B0828","#0F0E0E", "#522B47")
                  

library("QTLseqr")

ChromKey <- data.frame(chromosomes = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII", 
                                       "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"), 
                       CHROM = c("NC_001133.9", "NC_001134.8", "NC_001135.5", "NC_001136.10", 
                                 "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6", 
                                 "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5", 
                                 "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1"))

setwd("C:/Users/cassa/OneDrive/Documents/GitHub/Sequencing/Analysis")
load("RdataFiles/SAUA_4-13-22.Rdata")
load("RdataFiles/SCUC_4-13-22.Rdata")


#################################################################################################
#################################################################################################
BSA_GLM <-  function(lrP, chr = "II", windowsize = 100){
  
  lrP <- subset(lrP, CHROM == chr)
  
  AllResults <- list()
  for(c in unique(lrP$CHROM)){
    lrP <- subset(lrP, CHROM == c)
    #Run the glm on that chromosome
    Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
      res <- glm(reads ~ bulk*parent, weights = value, family = binomial, data = lrP[lrP$POS == i,])
      c(c, i, res$coefficients)
    }
  
    #Format the results for the next function
    Results <- as.data.frame(Results)
    colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
    Results[,2] <- as.numeric(Results[,2])
    Results[,3] <- as.numeric(Results[,3])
    Results[,4] <- as.numeric(Results[,4])
    Results[,5] <- as.numeric(Results[,5])
    Results[,6] <- as.numeric(Results[,6])
    
    Results %>% arrange(POS) %>% select(-Intercept) -> Results
  }
  
 
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
            #save the median value from original index 1 to original end index
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  return(WResult)
  }

################################################################################
perChromWindow_binom_redone <- function(lrP, chr = "II", windowsize = 100, coverage = 15634092/2, seedt = Sys.time()){
  lrP <- lrP[lrP$CHROM == chr,]
  
  set.seed(seedt)
  
  for(i in 1:length(lrP$CHROM)){
    lrP$subs[i] <- rbinom(1, coverage, prob = lrP$perc[i]) + 1
  }
  
  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk*parent, weights = subs, family = binomial, data = lrP[lrP$POS == i,])
    c(chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  Results[,5] <- as.numeric(Results[,5])
  Results[,6] <- as.numeric(Results[,6])
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
            #save the median value from original index 1 to original end index
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  return(WResult)
}

#################################################################################################
#################################################################################################


pois_binom_sample <- function(lrP, chr = "II", windowsize = 100, coverage_div_factor = 2, seedt = 0){
  lrP <- lrP[lrP$CHROM == chr,]
  
  set.seed(seedt + Sys.time())
  
  #calculate reads by Poisson
   reads <- rpois(n = length(unique(lrP$id)), lambda = mean(lrP$value)/coverage_div_factor)
   readsdf <- data.frame(id = unique(lrP$id), numreads = reads)
   lrP %>% left_join(readsdf, by = "id") -> lrP
  
  #calculate binom for number of reads at position
  for(i in 1:length(lrP$CHROM)){
    lrP$subs[i] <- rbinom(1, lrP$numreads[i], prob = lrP$perc[i]) + 1
  }
  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk*parent, weights = subs, family = binomial, data = lrP[lrP$POS == i,])
    c(chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  Results[,5] <- as.numeric(Results[,5])
  Results[,6] <- as.numeric(Results[,6])
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
            #save the median value from original index 1 to original end index
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  return(WResult)
}

#################################################################################################
#################################################################################################

MakeStackedPlots <- function(pb = pb_VIII_df, chrom = "VII", bar = 100000){
  
  maxChrVII <- data.frame(Index = unique(pb$Index),
                       max_bulk_zprime = NA,
                       max_parent_zprime = NA,
                       max_int_zprime = NA)

for(i in 1:length(unique(pb$Index))){
  isubset <- subset(pb, Index == as.character(i))
  maxChrVII$max_bulk_zprime[i] <- isubset$POS[abs(isubset$bulk_Zprime) == max(abs(isubset$bulk_Zprime))]
  maxChrVII$max_parent_zprime[i] <- isubset$POS[abs(isubset$parent_Zprime) == max(abs(isubset$parent_Zprime))]
  maxChrVII$max_int_zprime[i] <- isubset$POS[abs(isubset$Interaction_Zprime) == max(abs(isubset$Interaction_Zprime))]
  rm(isubset)
}

#sd(maxChrVII$max_bulk_zprime)

ggplot(maxChrVII, aes(x = max_bulk_zprime)) + geom_density(size = 1) + 
  ggtitle(paste("Maximum Z' value for Chr ",chrom, " Bulk Effect"))-> p1
ggplot(maxChrVII, aes(x = max_bulk_zprime, y = "Bulk    .")) + geom_boxplot(size = 1, color = "violet") + geom_jitter(alpha = 0.4, size = 3)  + ggtitle(paste("SD = ", round(sd(maxChrVII$max_bulk_zprime), 2))) -> p2
a1 <- plot_grid(p1, p2, nrow = 2)

ggplot(maxChrVII, aes(x = max_bulk_zprime)) + geom_density(size = 1) + 
  ggtitle(paste("Maximum Z' value for Chr ",chrom, " Bulk Effect")) -> p1
  p1 + annotate("segment", x = min(maxChrVII$max_bulk_zprime), 
           xend = min(maxChrVII$max_bulk_zprime) + bar, 
           y = layer_scales(p1)$y$range$range[1] + (layer_scales(p1)$y$range$range[2] - layer_scales(p1)$y$range$range[1])/10, 
           yend = layer_scales(p1)$y$range$range[1] + (layer_scales(p1)$y$range$range[2] - layer_scales(p1)$y$range$range[1])/10,  
           colour = "red", size = 2, alpha = 0.5) -> p1
ggplot(maxChrVII, aes(x = max_bulk_zprime, y = "Bulk    .")) + geom_boxplot(size = 1, color = "violet") + geom_jitter(alpha = 0.4, size = 3)+xlim(layer_scales(p1)$x$range$range) + ggtitle(paste("SD = ", round(sd(maxChrVII$max_bulk_zprime), 2))) -> p2
a2 <- plot_grid(p1, p2, nrow = 2)

ggplot(maxChrVII, aes(x = max_parent_zprime)) + geom_density(size = 1) + 
  ggtitle(paste("Maximum Z' value for Chr ",chrom, " Parent Effect"))-> p3
  p3 + annotate("segment", x = min(maxChrVII$max_parent_zprime), 
           xend = min(maxChrVII$max_parent_zprime) + bar, 
           y = layer_scales(p3)$y$range$range[1] + (layer_scales(p3)$y$range$range[2] - layer_scales(p3)$y$range$range[1])/10, 
           yend = layer_scales(p3)$y$range$range[1] + (layer_scales(p3)$y$range$range[2] - layer_scales(p3)$y$range$range[1])/10,  
           colour = "red", size = 2, alpha = 0.5) -> p3
ggplot(maxChrVII, aes(x = max_parent_zprime, y = "Parent .")) + geom_boxplot(size = 1, color = "darkorange") + geom_jitter(alpha = 0.4, size = 3) + ggtitle(paste("SD = ", round(sd(maxChrVII$max_parent_zprime), 2)))  -> p4
a3 <- plot_grid(p3, p4, nrow = 2)

ggplot(maxChrVII, aes(x = max_int_zprime)) + geom_density(size = 1) + ggtitle(paste("Maximum Z' value for Chr ",chrom, " Interaction Effect"))-> p5
  p5 + annotate("segment", x = min(maxChrVII$max_int_zprime), 
           xend = min(maxChrVII$max_int_zprime) + bar, 
           y = layer_scales(p5)$y$range$range[1] + (layer_scales(p5)$y$range$range[2] - layer_scales(p5)$y$range$range[1])/10, 
           yend = layer_scales(p5)$y$range$range[1] + (layer_scales(p5)$y$range$range[2] - layer_scales(p5)$y$range$range[1])/10,  
           colour = "red", size = 2, alpha = 0.5) -> p5
  
ggplot(maxChrVII, aes(x = max_int_zprime, y = "Max Int Z'")) + geom_boxplot(size = 1, color = "lightblue") + geom_jitter(alpha = 0.4, size = 3) +ylab("") + ggtitle(paste("SD = ", round(sd(maxChrVII$max_int_zprime), 2)))  -> p6
a4 <- plot_grid(p5, p6, nrow = 2)

return(list(a1, a2, a3, a4))

}

#################################################################################################
#################################################################################################

MakeZePlots <- function(pb_II_df = pb_VIII_df){
  maxChrVI <- data.frame(Index = unique(pb_II_df$Index),
                       max_bulk_zprime = NA,
                       max_parent_zprime = NA,
                       max_int_zprime = NA)

for(i in 1:length(unique(pb_II_df$Index))){
  isubset <- subset(pb_II_df, Index == as.character(i))
  maxChrVI$max_bulk_zprime[i] <- isubset$POS[abs(isubset$bulk_Zprime) == max(abs(isubset$bulk_Zprime))]
  maxChrVI$max_parent_zprime[i] <- isubset$POS[abs(isubset$parent_Zprime) == max(abs(isubset$parent_Zprime))]
  maxChrVI$max_int_zprime[i] <- isubset$POS[abs(isubset$Interaction_Zprime) == max(abs(isubset$Interaction_Zprime))]
  rm(isubset)
}


pb_II_df %>% ggplot(., aes(x = POS, y = bulk_Zprime, color = Index)) + 
  geom_line(alpha = 0.2) + theme(legend.position = "none") -> pbulkz


pb_II_df %>% ggplot(., aes(x = POS, y = parent_Zprime, color = Index)) + 
  geom_line(alpha = 0.2) + theme(legend.position = "none") -> pparentz

pb_II_df %>% ggplot(., aes(x = POS, y = Interaction_Zprime, color = Index)) + 
  geom_line(alpha = 0.2) + theme(legend.position = "none") -> pintz

ggplot(maxChrVI, aes(x = max_bulk_zprime, y = 1)) + geom_boxplot() + geom_jitter(alpha = 0.5) + theme(legend.position = "none") + ylab("") + xlab("Position") + xlim(min(pb_II_df$POS), max(pb_II_df$POS)) -> pbulkmax

ggplot(maxChrVI, aes(x = max_parent_zprime, y = 1)) + geom_boxplot() + geom_jitter(alpha = 0.5) + theme(legend.position = "none") + ylab("") + xlab("Position") + xlim(min(pb_II_df$POS), max(pb_II_df$POS)) -> pparentmax

ggplot(maxChrVI, aes(x = max_int_zprime, y = 1)) + geom_boxplot() + geom_jitter(alpha = 0.5) + theme(legend.position = "none") + ylab("") + xlab("Position") + xlim(min(pb_II_df$POS), max(pb_II_df$POS)) -> pintmax

a <- plot_grid(pbulkz, pbulkmax, nrow = 2)
b <- plot_grid(pparentz, pparentmax, nrow = 2)
c <- plot_grid(pintz, pintmax, nrow = 2)

 return(list(plotA = a, plotB = b, plotC = c))
}

#################################################################################################
#################################################################################################

getmaxvalues <- function(pb = pb_VIII_df200, idstring = NA){
  #change this for each dataset
  
  #make the df to save
  maxChrVII <- data.frame(Index = unique(pb$Index),
                         max_bulk_zprime = NA,
                         max_parent_zprime = NA,
                         max_int_zprime = NA,
                         max_bulk_zprime_pos = NA,
                         max_parent_zprime_pos = NA,
                         max_int_zprime_pos = NA)
  
  for(i in 1:length(unique(pb$Index))){
    isubset <- subset(pb, Index == as.character(i))
    maxChrVII$max_bulk_zprime_pos[i] <- isubset$POS[abs(isubset$bulk_Zprime) == max(abs(isubset$bulk_Zprime))]
    maxChrVII$max_parent_zprime_pos[i] <- isubset$POS[abs(isubset$parent_Zprime) == max(abs(isubset$parent_Zprime))]
    maxChrVII$max_int_zprime_pos[i] <- isubset$POS[abs(isubset$Interaction_Zprime) == max(abs(isubset$Interaction_Zprime))]
    maxChrVII$max_bulk_zprime[i] <- max(abs(isubset$bulk_Zprime))
    maxChrVII$max_parent_zprime[i] <- max(abs(isubset$parent_Zprime))
    maxChrVII$max_int_zprime[i] <- max(abs(isubset$Interaction_Zprime))
    rm(isubset)
  }
  
  plot_int <- maxChrVII %>% ggplot(aes(x = max_int_zprime_pos, y = max_int_zprime)) + geom_point(size = 2, alpha = 0.4) + ggtitle("Max Interaction Z primes by Position")
  plot_parent <- maxChrVII %>% ggplot(aes(x = max_parent_zprime_pos, y = max_parent_zprime)) + geom_point(size = 2, alpha = 0.4) + ggtitle("Max Parent Z primes by Position")
  plot_bulk <- maxChrVII %>% ggplot(aes(x = max_bulk_zprime_pos, y = max_bulk_zprime)) + geom_point(size = 2, alpha = 0.4) + ggtitle("Max Bulk Z primes by Position")
  
  maxChrVII$Chr <- idstring
  maxdf <- maxChrVII
  
  maxstats <- data.frame(parentz_mean = mean(maxdf$max_parent_zprime),
                         parentz_sd = sd(maxdf$max_parent_zprime),
                         parentpos_mean = mean(maxdf$max_parent_zprime_pos),
                         parentpos_sd = sd(maxdf$max_parent_zprime_pos),
                         intz_mean = mean(maxdf$max_int_zprime),
                         intz_sd = sd(maxdf$max_int_zprime),
                         intpos_mean = mean(maxdf$max_int_zprime_pos),
                         intpos_sd = sd(maxdf$max_int_zprime_pos),
                         bulkz_mean = mean(maxdf$max_bulk_zprime),
                         bulkz_sd = sd(maxdf$max_bulk_zprime),
                         bulkpos_mean = mean(maxdf$max_bulk_zprime_pos),
                         bulkpos_sd = sd(maxdf$max_bulk_zprime_pos),
                         Chr = idstring
                         )
  
  return(list(maxChrVII, maxstats, plot_bulk,plot_parent, plot_int))
}

#################################################################################################
#################################################################################################


GLM_Bulk_Only <- function(startLRP, windowsize = 100, Chr = "II"){
  if(Chr == "All"){
    appendWResult <- data.frame(CHROM = NA, Index = NA, POS = NA, bulk_Z = NA, bulk_Zprime = NA)
    for(Chrall in unique(startLRP$CHROM)){
      lrP <- subset(startLRP, CHROM == Chrall)
      #Run the glm on that chromosome
      Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
        res <- glm(reads ~ bulk, weights = value, family = binomial, data = lrP[lrP$POS == i,])
        c(Chrall, i, res$coefficients)
      }
      
      #Format the results for the next function
      Results <- as.data.frame(Results)
      colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh")
      Results[,2] <- as.numeric(Results[,2])
      Results[,3] <- as.numeric(Results[,3])
      Results[,4] <- as.numeric(Results[,4])
      
      
      Results %>% arrange(POS) %>% select(-Intercept) -> Results
    
      
      #Run the windows on that chromosome
      WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
                    res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                    #print CHROM, index, POS, and median
                    c(Chrall, i, Results$POS[i], Results$bulkHigh[i],res_bulk)}
      
      WResult <- as.data.frame(WResult)
      colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "bulk_Zprime")
      WResult[,2] <- as.numeric(WResult[,2])
      WResult[,3] <- as.numeric(WResult[,3])
      WResult[,4] <- as.numeric(WResult[,4])
      WResult[,5] <- as.numeric(WResult[,5])
      
      appendWResult <- rbind(appendWResult,WResult)
    }
    return(appendWResult)
  }else{
  lrP <- subset(lrP, CHROM == Chr)
  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk, weights = value, family = binomial, data = lrP[lrP$POS == i,])
    c(Chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(Chr, i, Results$POS[i], Results$bulkHigh[i],res_bulk)}
  
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "bulk_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  return(WResult)
  }
  
}

load("RdataFiles/logregParental.Rdata")
```

## Post 7/19/22 Meeting

Notes:
* changing the window size would help with the jaggedness of peaks, and have the max values align more with peak locations
* clustering on the location of the max
* it's only a problem when they're nearly equal
* k-means clustering should be done on that one vector
* distance function - make sure it's not trying to do correlation as distance; euclidian works, should be fine in any dimension
* silhouette width gives the right number of clusters apparently - try that
* the goal is to see if there's two clusters, then what's the sd in each cluster


### Bulk Correlations

* correlation between the two bulks
* there's going to be some slope to the z scores through each
* at low values it might be noisier, since that should just be noise
* look at that for where to trust the values

### Run this for all chromosomes now

```{r}
# load("RdataFiles/logregParental.Rdata")
# 
# logregParental %>% filter(parent == "Wine") -> WineParents
# logregParental %>% filter(parent == "Oak") -> OakParents

# WineP_Results <- GLM_Bulk_Only(WineParents, Chr = "All")
# OakP_Results <- GLM_Bulk_Only(OakParents, Chr = "All")
# 
# WineP_Results$Parent <- "Wine"
# OakP_Results$Parent <- "Oak"
# 
# rbind(WineP_Results, OakP_Results) %>% pivot_wider(names_from = Parent, values_from = c(bulk_Z, bulk_Zprime)) -> PResults_Wider
# rbind(WineP_Results, OakP_Results) -> PResults
# save(PResults, file = "PResults.Rdata")
# save(PResults_Wider, file = "PResults_Wider.Rdata")

load("RdataFiles/PResults.Rdata")
load("RdataFiles/PResults_Wider.Rdata")


PResults %>% ggplot(aes(x = POS, y = bulk_Zprime, color = Parent)) + geom_point(aes(x = POS, y = bulk_Z, color = Parent), alpha = 0.01) + geom_line() + ggtitle("Bulk Effects") + facet_grid(~CHROM, scales = "free_x") + ylim(-2,5)

PResults %>% ggplot(aes(x = POS, y = bulk_Zprime, color = Parent)) + geom_line() + ggtitle("Bulk Effects")

PResults %>% ggplot(aes(x = POS, y = bulk_Z, color = Parent)) + geom_line() + ggtitle("Raw Bulk Effects")

PResults_Wider %>% ggplot(aes(x = bulk_Zprime_Wine, y = bulk_Zprime_Oak)) + geom_point(alpha = 0.05, size = 1) + ggtitle("Zprime Correlation") + ylim(-1,1) + xlim(-1,1)

PResults_Wider %>% ggplot(aes(x = bulk_Z_Wine, y = bulk_Z_Oak)) + geom_point(alpha = 0.1, size = 2) + ggtitle("Z Correlation") + ylim(-5,5) + xlim(-5,5)
```



## Find Parent and Interaction Effects from Randomized Parent

```{r}
load("RdataFiles/logregParental.Rdata")
parentscramble <- logregParental %>% select(-Type, -Oak, -Wine) %>% pivot_wider(names_from = c(parent), values_from = value)

# swap <- sample(1:length(parentscramble$Oak), size = (length(parentscramble$Oak)/2), replace = FALSE)
# 
# parentscramble$newOak <- parentscramble$Oak
# parentscramble$newWine <- parentscramble$Wine
# parentscramble$newOak[swap] <- parentscramble$Wine[swap]
# parentscramble$newWine[swap] <- parentscramble$Oak[swap]
# 
# #Test this
# length(which(parentscramble$Oak == parentscramble$newOak))
# length(which(parentscramble$Oak == parentscramble$newWine))
bulkscramble <- logregParental %>% select(-Type, -Oak, -Wine) %>% pivot_wider(names_from = c(bulk), values_from = value)
swap <- sample(1:length(bulkscramble$Oak), size = (length(bulkscramble$Oak)/2), replace = FALSE)

bulkscramble$newLOW <- bulkscramble$LOW
bulkscramble$newHIGH <- bulkscramble$HIGH
bulkscramble$newLOW[swap] <- bulkscramble$HIGH[swap]
bulkscramble$newHIGH[swap] <- bulkscramble$LOW[swap]

#Test this
length(which(bulkscramble$Oak == bulkscramble$newOak))
length(which(bulkscramble$Oak == bulkscramble$newWine))

```

```{r}
GLM__RandParent <- function(lrPinit, windowsize = 100, Chr = "III", seedstart = Sys.time()){
  
  
  parentscramble <- subset(lrPinit, CHROM == Chr) 
  
  #Add in parent swap
  set.seed(seedstart)
  swap <- sample(1:length(parentscramble$Oak), size = (length(parentscramble$Oak)/2), replace = FALSE)

  parentscramble$newOak <- parentscramble$Oak
  parentscramble$newWine <- parentscramble$Wine
  parentscramble$newOak[swap] <- parentscramble$Wine[swap]
  parentscramble$newWine[swap] <- parentscramble$Oak[swap]
  
  lrP <- parentscramble %>% pivot_longer(c(newOak, newWine), names_to = "parent")

  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk*parent, weights = value, family = binomial, data = lrP[lrP$POS == i,])
    c(Chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  Results[,5] <- as.numeric(Results[,5])
  Results[,6] <- as.numeric(Results[,6])
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(Chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  WResult$seed <- seedstart
  
  return(WResult)
}

```


```{r, eval = FALSE}
GLM__RandParent(parentscramble, Chr = "III")

randparentlist <- list()
for(i in ChromKey$chromosomes[2:16]){
  randparentlist[[i]] <- GLM__RandParent(parentscramble, Chr = i)
}

save(randparentlist, file = "randparentlist.Rdata")

```

```{r}
load("RdataFiles/randparentlist.Rdata")
randpdf <- bind_rows(randparentlist, .id = "CHROM")

randpdf %>% ggplot(aes(x = POS, y = bulk_Zprime)) + geom_line() + geom_line(aes(x = POS, y = parent_Zprime), color = "gray") +
   geom_line(aes(x = POS, y =Interaction_Zprime), color = "purple") +
  facet_grid(~CHROM, scales = "free", space = "free")
```

### Chromosome X

Looks like there is no effect, so wanted to run this with random parent effects. 

```{r, eval = FALSE}
randparent_X <- list()
for(i in 1:100){
   randparent_X[[i]] <- GLM__RandParent(parentscramble, Chr = "X", seedstart = (100+i))
}

randpdf_X <- bind_rows(randparent_X, .id = "seed")

save(randpdf_X, file = "randpdf_X.Rdata")

load("RdataFiles/randpdf_X.Rdata")

ggplot(randpdf_X, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Bulk Effects with Random Parent, Chr X")

ggplot(randpdf_X, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Parental Effects, Chr X")

ggplot(randpdf_X, aes(x = POS, y = Interaction_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Interaction Effects, Chr X")

```

```{r}
load("RdataFiles/randpdf_X.Rdata")
load("RdataFiles/logregParental.Rdata")

VXResults <- BSA_GLM(lrP = logregParental, chr = "X")

VXResults %>% mutate(Zprime_Original = bulk_Zprime) %>% select(POS, Zprime_Original) %>% left_join(select(randpdf_X, c(POS, bulk_Zprime, seed))) %>% ggplot(aes(x = Zprime_Original, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.01)

```

### Chromosome VIII

This looked weird when running it with the bulk effect on its own, but running with random parental effects might help?

```{r, eval = FALSE}
randparent_VIII <- list()
for(i in 1:100){
   randparent_VIII[[i]] <- GLM__RandParent(parentscramble, Chr = "VIII", seedstart = (100+i))
}

randpdf_VIII <- bind_rows(randparent_VIII, .id = "seed")


save(randpdf_VIII, file = "randpdf_VIII.Rdata")
load("RdataFiles/randpdf_VIII.Rdata")
```

Running Chr VIII again for real

```{r}
load("RdataFiles/logregParental.Rdata")

VIIIResults <- BSA_GLM(lrP = logregParental, chr = "VIII")


```

```{r}
load("RdataFiles/randpdf_VIII.Rdata")

load("RdataFiles/WindowComparison.Rdata")

unique(WindowComp$Window)

# ggplot() + geom_point(data = subset(WindowComp, CHROM == "VIII" & Stat == "ZPrime"& Window == "WeightedMean.100"), aes(x = POS, y = Bulk))

ggplot(randpdf_VIII, aes(x = POS, y = bulk_Zprime)) + geom_line(aes(group = seed), alpha = 0.1) + 
  geom_line(data = VIIIResults, aes(x = POS, y = bulk_Zprime), color = "red") +
  ggtitle("Bulk Effects with Random Parent, Chr VIII")

ggplot(randpdf_VIII, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Parental Effects, Chr VIII")

ggplot(randpdf_VIII, aes(x = POS, y = Interaction_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Interaction Effects, Chr VIII")

VIIIResults %>% mutate(Zprime_Original = bulk_Zprime) %>% select(POS, Zprime_Original) %>% left_join(select(randpdf_VIII, c(POS, bulk_Zprime, seed))) %>% ggplot(aes(x = Zprime_Original, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.01)

```

```{r}
GLM_RandBulk <- function(lrPinit, windowsize = 100, Chr = "III", seedstart = Sys.time()){
  
  #lrPinit <- logregParental
  #Chr <- "VII"
  
  bulkscramble <- subset(lrPinit, CHROM == Chr)  %>% select(-Type, -Oak, -Wine) %>% pivot_wider(names_from = c(bulk), values_from = value)
  
  #Add in parent swap
  set.seed(seedstart)
  swap <- sample(1:length(bulkscramble$POS), size = (length(bulkscramble$POS)/2), replace = FALSE)
  
  bulkscramble$newLOW <- bulkscramble$LOW
  bulkscramble$newHIGH <- bulkscramble$HIGH
  bulkscramble$newLOW[swap] <- bulkscramble$HIGH[swap]
  bulkscramble$newHIGH[swap] <- bulkscramble$LOW[swap]

  
  lrP <- bulkscramble %>% pivot_longer(c(newLOW, newHIGH), names_to = "bulk")

  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk*parent, weights = value, family = binomial, data = lrP[lrP$POS == i,])
    c(Chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  Results[,5] <- as.numeric(Results[,5])
  Results[,6] <- as.numeric(Results[,6])
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(Chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  WResult$seed <- seedstart
  
  return(WResult)
}
```

```{r, eval = FALSE}

#RUN FUNCTINO ABOVE THIS TO START

load("RdataFiles/logregParental.Rdata")

randbulk_VII <- list()
for(i in 1:100){
   randbulk_VII[[i]] <- GLM_RandBulk(logregParental, Chr = "VII", seedstart = (100+i))
}

randbdf_VII <- bind_rows(randbulk_VII, .id = "Index")

#randbdf_VII <- do.call("rbind", randbulk_VII)

save(randbdf_VII, file = "randbdf_VII.Rdata")

```

```{r}
load("RdataFiles/randbdf_VII.Rdata")

#length(unique(randbdf_VII$seed))

ggplot(randbdf_VII, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Bulk Effects with Random bulk, Chr VII")

ggplot(randbdf_VII, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Parental Effects, Chr VII")

ggplot(randbdf_VII, aes(x = POS, y = Interaction_Zprime, group = as.factor(seed))) + geom_line(alpha = 0.1) + ggtitle("Random Interaction Effects, Chr VII") + theme(legend.position = "none")

```

```{r}
max(abs(randbdf_VII$bulk_Zprime))
max(abs(randbdf_VII$parent_Zprime))
max(abs(randbdf_VII$Interaction_Zprime))

```

### Running this on Chr VIII

```{r, eval = FALSE}

#RUN FUNCTINO ABOVE THIS TO START

load("RdataFiles/logregParental.Rdata")

randbulk_VIII <- list()
for(i in 1:100){
   randbulk_VIII[[i]] <- GLM_RandBulk(logregParental, Chr = "VIII", seedstart = (100+i))
}

randbdf_VIII <- bind_rows(randbulk_VIII, .id = "Index")

#randbdf_VIII <- do.call("rbind", randbulk_VIII)

save(randbdf_VIII, file = "randbdf_VIII.Rdata")

```

```{r}
load("RdataFiles/randbdf_VIII.Rdata")

#length(unique(randbdf_VIII$seed))

ggplot(randbdf_VIII, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Bulk Effects with Random bulk, Chr VIII")

ggplot(randbdf_VIII, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Random Parental Effects, Chr VIII")

ggplot(randbdf_VIII, aes(x = POS, y = Interaction_Zprime, group = as.factor(seed))) + geom_line(alpha = 0.1) + ggtitle("Random Interaction Effects, Chr VIII") + theme(legend.position = "none")

```

### Stats on Chr VIII

```{r}
quantile(randbdf_VIII$bulk_Zprime, c(0.01, 0.99))
quantile(randbdf_VIII$parent_Zprime, c(0.01, 0.99))
quantile(randbdf_VIII$Interaction_Zprime, c(0.01, 0.99))

max(abs(randbdf_VIII$bulk_Zprime))
max(abs(randbdf_VIII$parent_Zprime))
max(abs(randbdf_VIII$Interaction_Zprime))

```

## Running function for entire genome to average

```{r, eval = FALSE}
load("RdataFiles/logregParental.Rdata")

randbulk_II <- list()
for(i in 1:100){
   randbulk_II[[i]] <- GLM_RandBulk(logregParental, Chr = "II", seedstart = (100+i))
}

randbdf_II <- bind_rows(randbulk_II, .id = "Index")
save(randbdf_II, file = "randbdf_II.Rdata")

###################################
randbulk_III <- list()
for(i in 1:100){
   randbulk_III[[i]] <- GLM_RandBulk(logregParental, Chr = "III", seedstart = (100+i))
}

randbdf_III <- bind_rows(randbulk_III, .id = "Index")
save(randbdf_III, file = "randbdf_III.Rdata")

###################################
randbulk_IV <- list()
for(i in 1:100){
   randbulk_IV[[i]] <- GLM_RandBulk(logregParental, Chr = "IV", seedstart = (100+i))
}

randbdf_IV <- bind_rows(randbulk_IV, .id = "Index")
save(randbdf_IV, file = "randbdf_IV.Rdata")

###################################
randbulk_V <- list()
for(i in 1:100){
   randbulk_V[[i]] <- GLM_RandBulk(logregParental, Chr = "V", seedstart = (100+i))
}

randbdf_V <- bind_rows(randbulk_V, .id = "Index")
save(randbdf_V, file = "randbdf_V.Rdata")

###################################
randbulk_VI <- list()
for(i in 1:100){
   randbulk_VI[[i]] <- GLM_RandBulk(logregParental, Chr = "VI", seedstart = (100+i))
}

randbdf_VI <- bind_rows(randbulk_VI, .id = "Index")
save(randbdf_VI, file = "randbdf_VI.Rdata")

###################################
randbulk_IX <- list()
for(i in 1:100){
   randbulk_IX[[i]] <- GLM_RandBulk(logregParental, Chr = "IX", seedstart = (100+i))
}

randbdf_IX <- bind_rows(randbulk_IX, .id = "Index")
save(randbdf_IX, file = "randbdf_IX.Rdata")

###################################
randbulk_X <- list()
for(i in 1:100){
   randbulk_X[[i]] <- GLM_RandBulk(logregParental, Chr = "X", seedstart = (100+i))
}

randbdf_X <- bind_rows(randbulk_X, .id = "Index")
save(randbdf_X, file = "randbdf_X.Rdata")

###################################
randbulk_XI <- list()
for(i in 1:100){
   randbulk_XI[[i]] <- GLM_RandBulk(logregParental, Chr = "XI", seedstart = (100+i))
}

randbdf_XI <- bind_rows(randbulk_XI, .id = "Index")
save(randbdf_XI, file = "randbdf_XI.Rdata")

###################################
randbulk_XII <- list()
for(i in 1:100){
   randbulk_XII[[i]] <- GLM_RandBulk(logregParental, Chr = "XII", seedstart = (100+i))
}

randbdf_XII <- bind_rows(randbulk_XII, .id = "Index")
save(randbdf_XII, file = "randbdf_XII.Rdata")

###################################
randbulk_XIII <- list()
for(i in 1:100){
   randbulk_XIII[[i]] <- GLM_RandBulk(logregParental, Chr = "XIII", seedstart = (100+i))
}

randbdf_XIII <- bind_rows(randbulk_XIII, .id = "Index")
save(randbdf_XIII, file = "randbdf_XIII.Rdata")

###################################
randbulk_XIV <- list()
for(i in 1:100){
   randbulk_XIV[[i]] <- GLM_RandBulk(logregParental, Chr = "XIV", seedstart = (100+i))
}

randbdf_XIV <- bind_rows(randbulk_XIV, .id = "Index")
save(randbdf_XIV, file = "randbdf_XIV.Rdata")

###################################
randbulk_XV <- list()
for(i in 1:100){
   randbulk_XV[[i]] <- GLM_RandBulk(logregParental, Chr = "XV", seedstart = (100+i))
}

randbdf_XV <- bind_rows(randbulk_XV, .id = "Index")
save(randbdf_XV, file = "randbdf_XV.Rdata")

###################################
randbulk_XVI <- list()
for(i in 1:100){
   randbulk_XVI[[i]] <- GLM_RandBulk(logregParental, Chr = "XVI", seedstart = (100+i))
}

randbdf_XVI <- bind_rows(randbulk_XVI, .id = "Index")
save(randbdf_XVI, file = "randbdf_XVI.Rdata")

AllChromRandBulk <- rbind(randbdf_II,randbdf_III,randbdf_IV,randbdf_V,randbdf_VI,randbdf_VII,randbdf_VIII,randbdf_IX,
      randbdf_X,randbdf_XI,randbdf_XII,randbdf_XIII,randbdf_XIV,randbdf_XV, randbdf_XVI)

save(AllChromRandBulk, file = "AllChromRandBulk_100rep.Rdata")
```

```{r, eval=FALSE}
load("RdataFiles/AllChromRandBulk_100rep.Rdata")

ggplot(AllChromRandBulk, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Bulk Effects with Random bulk") + facet_grid(~CHROM, scales = "free", space = "free_x")

ggplot(AllChromRandBulk, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Parent Effects with Random bulk") + facet_grid(~CHROM, scales = "free", space = "free_x")

ggplot(AllChromRandBulk, aes(x = POS, y = Interaction_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Interaction Effects with Random bulk") + facet_grid(~CHROM, scales = "free", space = "free_x")


```

Stats on this

```{r}

load("RdataFiles/AllChromRandBulk_100rep.Rdata")

quantile(AllChromRandBulk$bulk_Zprime, c(0.025, 0.975))
quantile(AllChromRandBulk$parent_Zprime, c(0.025, 0.975))
quantile(AllChromRandBulk$Interaction_Zprime, c(0.025, 0.975))
```
What if I were to look at the max of each trial and then find the 95% cutoffs of those?

```{r}
load("RdataFiles/AllChromRandBulk_100rep.Rdata")

AllChromRandBulk %>% group_by(seed) %>% summarise(max_bulk = max(abs(bulk_Zprime)),
                                                  max_parent = max(abs(parent_Zprime)),
                                                  max_int = max(abs(Interaction_Zprime))) -> Max_Zprimes

save(Max_Zprimes, file = "Max_Zprimes.Rdata")

quantile(Max_Zprimes$max_bulk, 0.95)
quantile(Max_Zprimes$max_parent, 0.95)
quantile(Max_Zprimes$max_int, 0.95)

```

Remove Chr VIII from this

```{r}

load("RdataFiles/AllChromRandBulk_100rep.Rdata")
AllChromRandBulk %>% filter(CHROM != "VIII") %>% group_by(seed) %>% summarise(max_bulk = max(abs(bulk_Zprime)),
                                                  max_parent = max(abs(parent_Zprime)),
                                                  max_int = max(abs(Interaction_Zprime))) -> Max_Zprimes_minus8

#save(Max_Zprimes_minus8, file = "Max_Zprimes_minus8.Rdata")

quantile(Max_Zprimes_minus8$max_bulk, 0.95)
quantile(Max_Zprimes_minus8$max_parent, 0.95)
quantile(Max_Zprimes_minus8$max_int, 0.95)

Max_Zprimes %>% pivot_longer(-seed, names_to = "scoretype", values_to = "Zprime")-> MaxZ_pivot
Max_Zprimes_minus8 %>% pivot_longer(-seed, names_to = "scoretype", values_to = "Zprime") -> MaxZ_pivot_minus8

MaxZ_pivot %>% ggplot(aes(x = Zprime, fill = scoretype)) + geom_density(alpha = 0.3, size = 1, color = "gray") + ggtitle("Distribution of abs(max(zprime))") + xlim(0,0.8)+ ylim(0,25) + geom_vline(xintercept = quantile(MaxZ_pivot$Zprime, 0.95), linetype = "dashed", size = 1, color = "gray") + geom_vline(xintercept = quantile(MaxZ_pivot_minus8$Zprime, 0.95), linetype = "dashed", size = 1, color = "black")

MaxZ_pivot_minus8 %>% ggplot(aes(x = Zprime, fill = scoretype)) + geom_density(alpha = 0.3, size = 1, color = "black") + ggtitle("Distribution of abs(max(zprime)) without Chr VIII")+ xlim(0,0.8) + ylim(0,25) + geom_vline(xintercept = quantile(MaxZ_pivot_minus8$Zprime, 0.95), linetype = "dashed", size = 1, color = "black")+ geom_vline(xintercept = quantile(MaxZ_pivot$Zprime, 0.95), linetype = "dashed", size = 1, color = "gray")

```


Looking at this cutoff on the plot

```{r}
load("RdataFiles/bsa_glm_results.Rdata")

bsa_glm_results.plot %>% filter(CHROM != "I") %>% ggplot(aes(x = POS, y = bulk_Zprime)) + 
  geom_point(color = "#345F6F", size = 0.2, alpha = 0.8) + 
  geom_point(aes(x = POS, y = parent_Zprime), color = "#FFB05C", alpha= 0.8, size = 0.2) +
  geom_point(aes(x = POS, y = Interaction_Zprime), color = "#D7335C", alpha= 0.8, size = 0.2) +
  scale_x_continuous(breaks = seq(from = 0, to = max(bsa_glm_results.plot$POS), by = 1e5), name = "Genomic Position") +
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + theme_minimal() +
  ggtitle("Comparison of Smoothed Z scores") + theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + #ylim(-2, 5) +
  xlab("Genomic Position") + ylab("Oak  <--    Z Score  -->  Wine") + 
  geom_hline(yintercept = c(-quantile(MaxZ_pivot$Zprime, 0.95), quantile(MaxZ_pivot$Zprime, 0.95)), color = "gray", linetype = "dashed") +
  geom_hline(yintercept = c(-quantile(MaxZ_pivot_minus8$Zprime, 0.95), quantile(MaxZ_pivot_minus8$Zprime, 0.95)), color = "black", linetype = "dashed")

```

Plot the original lines on each

```{r}
load("RdataFiles/AllChromRandBulk_100rep.Rdata")
load("RdataFiles/bsa_glm_results.Rdata")


ggplot(AllChromRandBulk, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + 
  ggtitle("Bulk Effects with Random bulk") + 
  geom_line(data = bsa_glm_results.plot, aes(x = POS, y = bulk_Zprime, group = NULL), color = "#345F6F") + 
  geom_hline(yintercept = c(-quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$bulk_Zprime)), 0.95),
                            quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$bulk_Zprime)), 0.95)), 
             color = "red", linetype = "dashed") +
  facet_grid(~CHROM, scales = "free", space = "free_x") + 
  theme_minimal() + 
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())


ggplot(AllChromRandBulk, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + ggtitle("Parent Effects with Random bulk") + geom_line(data = bsa_glm_results.plot, aes(x = POS, y = parent_Zprime, group = NULL), color = "#FFB05C") + 
  geom_hline(yintercept = c(-quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$parent_Zprime)), 0.95),
                            quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$parent_Zprime)), 0.95)), 
             color = "red", linetype = "dashed") +
  facet_grid(~CHROM, scales = "free", space = "free_x")+ theme_minimal() + theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggplot(AllChromRandBulk, aes(x = POS, y = Interaction_Zprime, group = seed)) + geom_line(alpha = 0.1) + geom_line(data = bsa_glm_results.plot, aes(x = POS, y = Interaction_Zprime, group = NULL), color = "#D7335C") + ggtitle("Interaction Effects with Random bulk") + 
  geom_hline(yintercept = c(-quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$Interaction_Zprime)), 0.95),
                            quantile(max(abs(subset(AllChromRandBulk, CHROM != "VIII")$Interaction_Zprime)), 0.95)), 
             color = "red", linetype = "dashed") +
  facet_grid(~CHROM, scales = "free", space = "free_x")+ theme_minimal() + theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

```

What if we scrambled both parent and bulks? Then what is the max value by chance across the genome?

```{r}
GLM_RandBulkandParent <- function(lrPinit, windowsize = 100, Chr = "III", seedstart = Sys.time()){
  
  # lrPinit <- logregParental
  # Chr <- "VII"
  
  bulkscramble <- subset(lrPinit, CHROM == Chr) %>% select(-Type, -Oak, -Wine) %>% pivot_wider(names_from = c(bulk), values_from = value)
  
  #Add in parent swap
  set.seed(seedstart)
  bswap <- sample(1:length(bulkscramble$POS), size = (length(bulkscramble$POS)/2), replace = FALSE)
  
  bulkscramble$newLOW <- bulkscramble$LOW
  bulkscramble$newHIGH <- bulkscramble$HIGH
  bulkscramble$newLOW[bswap] <- bulkscramble$HIGH[bswap]
  bulkscramble$newHIGH[bswap] <- bulkscramble$LOW[bswap]

  
  parentscramble <- bulkscramble %>% pivot_longer(c(newLOW, newHIGH), names_to = "bulk") %>% select(-HIGH, -LOW) %>%  
    pivot_wider(names_from = c(parent), values_from = value)

  #Add in parent swap
  set.seed(seedstart)
  pswap <- sample(1:length(parentscramble$POS), size = (length(parentscramble$POS)/2), replace = FALSE)

  parentscramble$newOak <- parentscramble$Oak
  parentscramble$newWine <- parentscramble$Wine
  parentscramble$newOak[pswap] <- parentscramble$Wine[pswap]
  parentscramble$newWine[pswap] <- parentscramble$Oak[pswap]
  
  lrP <- parentscramble %>% pivot_longer(c(newOak, newWine), names_to = "parent") %>% select(-Oak, -Wine)

  
  #Run the glm on that chromosome
  Results <- foreach (i=unique(lrP$POS), .combine=rbind) %dopar% {
    res <- glm(reads ~ bulk*parent, weights = value, family = binomial, data = lrP[lrP$POS == i,])
    c(Chr, i, res$coefficients)
  }
  
  #Format the results for the next function
  Results <- as.data.frame(Results)
  colnames(Results) <- c("CHROM", "POS", "Intercept", "bulkHigh", "parentWine", "Interaction")
  Results[,2] <- as.numeric(Results[,2])
  Results[,3] <- as.numeric(Results[,3])
  Results[,4] <- as.numeric(Results[,4])
  Results[,5] <- as.numeric(Results[,5])
  Results[,6] <- as.numeric(Results[,6])
  
  Results %>% arrange(POS) %>% select(-Intercept) -> Results

  
  #Run the windows on that chromosome
  WResult <- foreach(i=windowsize+1:(length(Results$POS) - (2*windowsize)), .combine=rbind) %dopar% {
                res_int <- mean(Results$Interaction[(i-windowsize):(i+windowsize)])
                res_bulk <- mean(Results$bulkHigh[(i-windowsize):(i+windowsize)])
                res_parent <- mean(Results$parentWine[(i-windowsize):(i+windowsize)])
                #print CHROM, index, POS, and median
                c(Chr, i, Results$POS[i], Results$bulkHigh[i], Results$parentWine[i],Results$Interaction[i],
                  res_bulk, res_parent, res_int)}
  
  WResult <- as.data.frame(WResult)
  colnames(WResult) <- c("CHROM", "Index", "POS", "bulk_Z", "parent_Z", "Interaction_Z",
                         "bulk_Zprime", "parent_Zprime", "Interaction_Zprime")
  WResult[,2] <- as.numeric(WResult[,2])
  WResult[,3] <- as.numeric(WResult[,3])
  WResult[,4] <- as.numeric(WResult[,4])
  WResult[,5] <- as.numeric(WResult[,5])
  WResult[,6] <- as.numeric(WResult[,6])
  WResult[,7] <- as.numeric(WResult[,7])
  WResult[,8] <- as.numeric(WResult[,8])
  WResult[,9] <- as.numeric(WResult[,9])
  
  WResult$seed <- seedstart
  
  return(WResult)
}
```

```{r}
load("RdataFiles/logregParental.Rdata")

#rand_bp_VIII <- GLM_RandBulkandParent(logregParental, Chr = "VIII")

rand_bp_VIII <- list()
for(i in 1:100){
   rand_bp_VIII[[i]] <- GLM_RandBulkandParent(logregParental, Chr = "VIII", seedstart = (100+i))
}

rand_bp_df_VIII <- bind_rows(rand_bp_VIII, .id = "Index")
save(rand_bp_df_VIII, file = "rand_bp_df_VIII.Rdata")

```

```{r}
load("RdataFiles/rand_bp_df_VIII.Rdata")
load("RdataFiles/AllChromRandBulk_100rep.Rdata")
load("RdataFiles/bsa_glm_results.Rdata")

# length(unique(rand_bp_df_VIII$CHROM))
# max(rand_bp_df_VIII$POS)
# max(AllChromRandBulk$POS)

ggplot(rand_bp_df_VIII, aes(x = POS, y = bulk_Zprime, group = seed)) + geom_line(alpha = 0.1) + 
  ggtitle("Bulk Effects with Random bulk and parent") + 
  geom_line(data = subset(bsa_glm_results.plot, CHROM == "VIII"), aes(x = POS, y = bulk_Zprime, group = NULL), color = "#345F6F") + 
  geom_hline(yintercept = c(-quantile(max(abs(rand_bp_df_VIII$bulk_Zprime)), 0.95),
                            quantile(max(abs(rand_bp_df_VIII$bulk_Zprime)), 0.95)),
             color = "red", linetype = "dashed") +
  #facet_grid(~CHROM, scales = "free", space = "free_x") + 
  theme_minimal() + 
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggplot(rand_bp_df_VIII, aes(x = POS, y = parent_Zprime, group = seed)) + geom_line(alpha = 0.1) + 
  ggtitle("Parent Effects with Random bulk and parent") + 
  geom_line(data = subset(bsa_glm_results.plot, CHROM == "VIII"), aes(x = POS, y = parent_Zprime, group = NULL), color = "#FFB05C") + 
  geom_hline(yintercept = c(-quantile(max(abs(rand_bp_df_VIII$parent_Zprime)), 0.95),
                            quantile(max(abs(rand_bp_df_VIII$parent_Zprime)), 0.95)),
             color = "red", linetype = "dashed") +
  #facet_grid(~CHROM, scales = "free", space = "free_x") + 
  theme_minimal() + 
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

ggplot(rand_bp_df_VIII, aes(x = POS, y = Interaction_Zprime, group = seed)) + geom_line(alpha = 0.1) + 
  ggtitle("Interaction Effects with Random bulk and parent") + 
  geom_line(data = subset(bsa_glm_results.plot, CHROM == "VIII"), aes(x = POS, y = Interaction_Zprime, group = NULL), color = "#D7335C") + 
  geom_hline(yintercept = c(-quantile(max(abs(rand_bp_df_VIII$Interaction_Zprime)), 0.95),
                            quantile(max(abs(rand_bp_df_VIII$Interaction_Zprime)), 0.95)),
             color = "red", linetype = "dashed") +
  #facet_grid(~CHROM, scales = "free", space = "free_x") + 
  theme_minimal() + 
  theme(legend.position = "none", axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

```{r}
head(logregParental)
```

