---
title: "QTLseq Method of Bulk Segregant Analysis"
author: "Cassandra Buzby"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
---

Keep in mind, use coolors.co for color palettes :)

Notes from Grace: use repeatmasker (isb), or trim off telomeres
* institute for systems biology, seattle
* probably also stops the transposons
* there could also be variants



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Load packages
library(ggplot2)
library(tidyr)
library(tidyverse)
library(reshape2)
library(cowplot)
ggplot2::theme_set(theme_light())

CBchromPalette <- c("#F26430", "#0A369D", "#7EA3CC","#FF9F1C", "#C14953","#92DCE5", "#4C4C47", "#8FC93A",
                   "#F26430", "#0A369D", "#7EA3CC","#FF9F1C", "#C14953","#92DCE5", "#4C4C47", "#8FC93A",
                  "#F26430", "#0A369D", "#7EA3CC")


library("QTLseqr")

ChromKey <- data.frame(chromosomes = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII", 
                                       "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"), 
                       CHROM = c("NC_001133.9", "NC_001134.8", "NC_001135.5", "NC_001136.10", 
                                 "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6", 
                                 "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5", 
                                 "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1"))

```

```{r, include=FALSE}
#Function to Plot
plotQTLStatsCB <- function (SNPset, subset = NULL, var = "nSNPs", scaleChroms = TRUE, 
    line = TRUE, plotThreshold = FALSE, plotIntervals = FALSE, 
    q = 0.05, ...) 
{
    if (!all(subset %in% unique(SNPset$CHROM))) {
        whichnot <- paste(subset[base::which(!subset %in% unique(SNPset$CHROM))], 
            collapse = ", ")
        stop(paste0("The following are not true chromosome names: ", 
            whichnot))
    }
    if (!var %in% c("nSNPs", "deltaSNP", "Gprime", 
        "negLog10Pval")) 
        stop("Please choose one of the following variables to plot: \"nSNPs\", \"deltaSNP\", \"Gprime\", \"negLog10Pval\"")
    if ((plotThreshold == TRUE & var == "deltaSNP") | (plotThreshold == 
        TRUE & var == "nSNPs")) {
        message("FDR threshold is not plotted in deltaSNP or nSNPs plots")
        plotThreshold <- FALSE
    }
    GprimeT <- 0
    logFdrT <- 0
    if (plotThreshold == TRUE) {
        fdrT <- getFDRThreshold_CB(SNPset$pvalue, alpha = q)
        if (is.na(fdrT)) {
            warning("The q threshold is too low. No threshold line will be drawn")
            plotThreshold <- FALSE
        }
        else {
            logFdrT <- -log10(fdrT)
            GprimeT <- SNPset[which(SNPset$pvalue == fdrT), "Gprime"]
        }
    }
    SNPset <- if (is.null(subset)) {
        SNPset
    }
    else {
        SNPset[SNPset$CHROM %in% subset, ]
    }
    p <- ggplot2::ggplot(data = SNPset) + ggplot2::scale_x_continuous(breaks = seq(from = 0, 
        to = max(SNPset$POS), by = 10^(floor(log10(max(SNPset$POS))))), 
        #labels = format_genomic(), 
        name = "Genomic Position (Mb)") + 
        ggplot2::theme(plot.margin = ggplot2::margin(b = 10, 
            l = 20, r = 20, unit = "pt"))
    if (var == "Gprime") {
        threshold <- GprimeT
        p <- p + ggplot2::ylab("G' value")
    }
    if (var == "negLog10Pval") {
        threshold <- logFdrT
        p <- p + ggplot2::ylab(expression("-" * log[10] * 
            "(p-value)"))
    }
    if (var == "nSNPs") {
        p <- p + ggplot2::ylab("Number of SNPs in window")
    }
    if (var == "deltaSNP") {
        var <- "tricubeDeltaSNP"
        p <- p + ggplot2::ylab(expression(Delta * "(SNP-index)")) + 
            ggplot2::ylim(-0.55, 0.55) + ggplot2::geom_hline(yintercept = 0, 
            color = "black", alpha = 0.4)
        if (plotIntervals == TRUE) {
            ints_df <- dplyr::select(SNPset, CHROM, POS, dplyr::matches("CI_")) %>% 
                tidyr::gather(key = "Interval", value = "value", 
                  -CHROM, -POS)
            p <- p + ggplot2::geom_line(data = ints_df, ggplot2::aes(x = POS, 
                y = value, color = Interval)) + ggplot2::geom_line(data = ints_df, 
                ggplot2::aes(x = POS, y = -value, color = Interval))
        }
    }
    if (line) {
        p <- p + ggplot2::geom_line(ggplot2::aes_string(x = "POS", 
            y = var), ...)
    }
    if (!line) {
        p <- p + ggplot2::geom_point(ggplot2::aes_string(x = "POS", 
            y = var), ...)
    }
    if (plotThreshold == TRUE) 
        p <- p + ggplot2::geom_hline(ggplot2::aes_string(yintercept = "threshold"), 
            color = "red", size = 1, alpha = 0.4)
    if (scaleChroms == TRUE) {
        p <- p + ggplot2::facet_grid(~CHROM, scales = "free_x", 
            space = "free_x")
    }
    else {
        p <- p + ggplot2::facet_grid(~CHROM, scales = "free_x")
    }
    p
}

```

```{r, eval=FALSE, include = FALSE}
#Following directions for installation

install.packages("devtools")

##Updating Rtools from https://github.com/metrumresearchgroup/mrgsolve/issues/160 
# path <- Sys.getenv("PATH")
# path <- c("C:/rtools40/usr/bin", path) #changed from original verion to my path
# path <- paste(path,collapse=";")
# Sys.setenv(PATH=path)
# 
# Sys.which("make") #test that "make" is found in the right folder

#################
devtools::install_github("bmansfeld/QTLseqr")
```


### Functions for running analysis and plots on all samples

```{r}
#################################################
#Change this to analyze all differently
#################################################

mindepth = 50
maxdepth = 1500
minsampledepth = 50
mingq = 0.98

PipelineFunc <- function(HighBulk, LowBulk, rawData = "mergedCuSO4.REF.SortedCat.vcf.output.table",
                         mindepth = mindepth,
                         maxdepth = maxdepth,
                         minsampledepth = minsampledepth,
                         mingq = mingq,
                         windowSize = 2e4,
                         Chroms = c("NC_001134.8", "NC_001135.5", "NC_001136.10", 
                                 "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6", 
                                 "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5", 
                                 "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1")
                         ){
  
  mytitle <- paste(HighBulk, LowBulk, sep = " vs ")
  HNGLCDRXY <- read.table(rawData, header = TRUE)

  df <- importFromGATK(
        file = rawData,
        highBulk = HighBulk,
        lowBulk = LowBulk,
        chromList = Chroms
        )

df %>% merge(.,ChromKey) %>% 
  group_by(CHROM) %>% mutate(Start = min(POS) + 350, End = max(POS) - 350) %>% 
  as.data.frame() %>% na.omit() -> df

colnames(df)[1] <- "NC_Chrom"
colnames(df)[which(colnames(df) == "chromosomes")] <- "CHROM"

df$CHROM <- factor(df$CHROM, levels = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII", "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"))
#################################

#Filter SNPs based on some criteria
df_filt <-
    filterSNPs(
        SNPset = df,
        refAlleleFreq = 0.10, #0.20
        minTotalDepth = mindepth, #100
        maxTotalDepth = maxdepth, #400
        minSampleDepth = minsampledepth, #40
        minGQ = mingq #99
    )

  #df %>% merge(.,ChromKey)
  #df_filt <- df
  
  #Run G' analysi
  df_filt <- runGprimeAnalysis(
      SNPset = df_filt,
      windowSize = windowSize, #1e6
      outlierFilter = "deltaSNP")
  
  #Run QTLseq analysis
  df_filt <- runQTLseqAnalysis(
      SNPset = df_filt,
      windowSize = windowSize,
      popStruc = "F2",
      bulkSize = 1000, #c(25, 25)
      replications = 10000,
      intervals = c(95, 99)
  )

  df_filt$idu <- row.names(df_filt)
  q <- 0.01
  fdrT <- getFDRThreshold(df_filt$pvalue, alpha = q)
  GprimeT <- df_filt[which(df_filt$pvalue == fdrT), "Gprime"]
  
  # df_filt$chromosomes <- factor(df_filt$chromosomes, levels = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII", "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"))

    
  return(as.data.frame(df_filt))
}

#######################################################################
# Change this to plot differently #
#######################################################################

plotallfunc <- function(df_filt, HighBulk, LowBulk){
  
  mytitle <- paste(HighBulk, LowBulk, sep = " vs ")
    
  q <- 0.01
  fdrT <- getFDRThreshold(df_filt$pvalue, alpha = q)
  GprimeT <- df_filt[which(df_filt$pvalue == fdrT), "Gprime"]
  
  # plot.gprime.idu <- ggplot(df_filt, aes(x = as.numeric(idu), y = Gprime, color = chromosomes)) + 
  #   geom_point(size = 3, alpha = 0.8) + geom_hline(yintercept = GprimeT, linetype = "dashed") +
  #   ggtitle(mytitle) + scale_colour_manual(values=CBchromPalette)
  # 
  # plot.nlogp <- ggplot(df_filt, aes(x = as.numeric(idu), y = negLog10Pval, color = chromosomes)) + 
  #   geom_point(size = 3, alpha = 0.8) + geom_hline(yintercept = -log(0.05), linetype = "dashed") +
  #   ggtitle(mytitle) + scale_colour_manual(values=CBchromPalette)

#Fancy plots from the Ziv script adjustments

  plot.gprime <- plotQTLStatsCB(SNPset = df_filt, var = "Gprime", plotThreshold = F, q = 0.01)
  plot.deltasnp <- plotQTLStatsCB(SNPset = df_filt, var = "deltaSNP", plotIntervals = TRUE)

  plot.gprime.CB <- ggplot(data = df_filt, aes(x = POS, y = Gprime, color = CHROM)) + geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(df_filt$POS), 
                                  by = 10^(floor(log10(max(df_filt$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette) + 
    #geom_vline(xintercept = 212535, linetype = "dashed", size = 1) + #CUP1 gene
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle(mytitle)
  
  #print(plot.gprime.idu)
  #print(plot.nlogp)
  
  pointsofsig <- ggplot(data = df_filt, aes(x = POS, y = Gprime, color = abs(deltaSNP) < 0.1)) + geom_point(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(df_filt$POS), 
                                  by = 10^(floor(log10(max(df_filt$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette) + 
    #geom_vline(xintercept = 212535, linetype = "dashed", size = 1) + #CUP1 gene
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle(mytitle)
  
  print(plot.gprime.CB)
  print(pointsofsig)
 # print(plot.gprime)
  print(plot.deltasnp + theme(legend.position = "bottom")) 
}

```

```{r, eval = FALSE, include = FALSE}

ggplot(data = subset(df_filt, (POS < End | POS > Start) & CHROM == "VIII"), aes(x = POS, y = Gprime, color = CHROM)) + geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(df_filt$POS), 
                                  by = 10^(floor(log10(max(df_filt$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette) + 
    #geom_vline(xintercept = 212535, linetype = "dashed", size = 1) + #CUP1 gene
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle(mytitle)

```

## Run All Data Through Functions

```{r, include = FALSE}
rawData = "C:\\Users\\cassa\\OneDrive\\Documents\\R_SiegalLab\\SequencingPractice\\Data\\mergedCuSO4.REF.SortedCat.vcf.output.table"

SAUA <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "UnselectedA", rawData = rawData)
SCUC <- PipelineFunc(HighBulk = "SelectedC", LowBulk = "UnselectedC", rawData = rawData)
Selected <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "SelectedC", rawData = rawData)
Unselected <- PipelineFunc(HighBulk = "UnselectedA", LowBulk = "UnselectedC", rawData = rawData)

```

```{r, eval = FALSE}
rawData = "C:\\Users\\cassa\\OneDrive\\Documents\\R_SiegalLab\\SequencingPractice\\Data\\mergedCuSO4.REF.SortedCat.vcf.output.table"

SAUA <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "UnselectedA", rawData = rawData)
SCUC <- PipelineFunc(HighBulk = "SelectedC", LowBulk = "UnselectedC", rawData = rawData)
Selected <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "SelectedC", rawData = rawData)
Unselected <- PipelineFunc(HighBulk = "UnselectedA", LowBulk = "UnselectedC", rawData = rawData)

```

### Summaries of Files

```{r, include = FALSE}
#rawData = "C:\\Users\\cassa\\OneDrive\\Documents\\R_SiegalLab\\SequencingPractice\\Data\\mergedCuSO4.REF.SortedCat.vcf.output.table"

#rawData = "mergedCuSO4.REF.SortedCat.vcf.output.table"
Chroms <- ChromKey$CHROM

OakI_Selected <- importFromGATK(
        file = rawData,
        highBulk = "SelectedC",
        lowBulk = "UnselectedC",
        chromList = Chroms
        ) %>% mutate(Dataset = "OakI_Selected")

OakI_Unselected <- importFromGATK(
        file = rawData,
        highBulk = "UnselectedC",
        lowBulk = "SelectedC",
        chromList = Chroms
        ) %>% mutate(Dataset = "OakI_Unselected")

WineI_Selected <- importFromGATK(
        file = rawData,
        highBulk = "SelectedA",
        lowBulk = "UnselectedC",
        chromList = Chroms
        ) %>% mutate(Dataset = "WineI_Selected")

WineI_Unselected <- importFromGATK(
        file = rawData,
        highBulk = "UnselectedA",
        lowBulk = "UnselectedC",
        chromList = Chroms
        ) %>% mutate(Dataset = "WineI_Unselected")

OakI_Selected %>% select(CHROM, POS, REF, ALT, 
                AD_REF.HIGH, AD_ALT.HIGH, DP.HIGH, GQ.HIGH, PL.HIGH, SNPindex.HIGH,
                REF_FRQ, deltaSNP, Dataset) -> OakI_Selected

OakI_Unselected %>% select(CHROM, POS, REF, ALT, 
                AD_REF.HIGH, AD_ALT.HIGH, DP.HIGH, GQ.HIGH, PL.HIGH, SNPindex.HIGH,
                REF_FRQ, deltaSNP, Dataset) -> OakI_Unselected

WineI_Selected %>% select(CHROM, POS, REF, ALT, 
                AD_REF.HIGH, AD_ALT.HIGH, DP.HIGH, GQ.HIGH, PL.HIGH, SNPindex.HIGH,
                REF_FRQ, deltaSNP, Dataset) -> WineI_Selected

WineI_Unselected %>% select(CHROM, POS, REF, ALT, 
                AD_REF.HIGH, AD_ALT.HIGH, DP.HIGH, GQ.HIGH, PL.HIGH, SNPindex.HIGH,
                REF_FRQ, deltaSNP, Dataset) -> WineI_Unselected

rbind(OakI_Selected, OakI_Unselected, WineI_Selected, WineI_Unselected) %>% merge(., ChromKey) -> HNG

################# Plots ###############
# mindepth = 10
# maxdepth = 1500
# minsampledepth = 40
# mingq = 0.98
```


```{r, echo = FALSE, eval = FALSE}
head(HNG)

ggplot(HNG, aes(x = REF_FRQ, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("Reference Allele Frequency") 

ggplot(HNG, aes(x = AD_REF.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("Reference AD (unfiltered allele depth)") + 
  geom_vline(xintercept = c(mindepth,maxdepth), linetype = "dashed")

ggplot(HNG, aes(x = AD_ALT.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("Alt AD (unfiltered allele depth)") + 
  geom_vline(xintercept = c(mindepth,maxdepth), linetype = "dashed")

ggplot(HNG, aes(x = DP.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("DP (filtered depth, at the sample level)") + geom_vline(xintercept = minsampledepth, linetype = "dashed")

ggplot(HNG[HNG$GQ.HIGH > 97,], aes(x = GQ.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("Genotype Quality (Phred-scaled confidence that the genotype assignment  is correct)")

ggplot(HNG[HNG$GQ.HIGH < 99,], aes(x = GQ.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("Genotype Quality (Phred-scaled confidence that the genotype assignment  is correct)")

table(HNG$GQ.HIGH)

ggplot(HNG, aes(x = SNPindex.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + ggtitle("SNP Index") 

```

### Extracting Stats for Telomeres

```{r, echo = FALSE}
HNG %>% group_by(CHROM) %>% mutate(Start = min(POS) + 350, End = max(POS) - 350) -> HNGt

# ggplot(HNGt, aes(x = REF_FRQ, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
#   ggtitle("Reference Allele Frequency") 

ggplot(HNGt, aes(x = REF_FRQ, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("Reference Allele Frequency") + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End))+ theme(legend.position = "bottom")

ggplot(HNGt, aes(x = AD_REF.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("Reference AD (unfiltered allele depth)") + 
  #geom_vline(xintercept = c(mindepth,maxdepth), linetype = "dashed") + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End))+ theme(legend.position = "bottom")

ggplot(HNGt, aes(x = AD_ALT.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("Alt AD (unfiltered allele depth)") + 
  #geom_vline(xintercept = c(mindepth,maxdepth), linetype = "dashed")  + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End))+ theme(legend.position = "bottom")

ggplot(HNGt, aes(x = DP.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("DP (filtered depth, at the sample level)") + #geom_vline(xintercept = minsampledepth, linetype = "dashed")  + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End))+ theme(legend.position = "bottom")

ggplot(HNGt, aes(x = GQ.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("Genotype Quality (Phred-scaled confidence that the genotype assignment  is correct)")  + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End)) + theme(legend.position = "bottom")

ggplot(HNGt, aes(x = SNPindex.HIGH, fill = Dataset)) + geom_density(alpha = 0.5, size = 1) + 
  ggtitle("SNP Index") + 
  facet_grid(cols = vars(HNGt$POS < HNGt$Start | HNGt$POS > HNGt$End)) + theme(legend.position = "bottom")

```

### Traditional BSA (Selected vs Unselected)
```{r}
plotallfunc(SAUA, HighBulk = "SelectedA", LowBulk = "UnselectedA")
plotallfunc(SCUC, HighBulk = "SelectedC", LowBulk = "UnselectedC")

```

### Unselected Bulks

These two bulks should only differ at Chr I since that is the fixed chromosome; all other loci should segregate evenly and be at approximately 50/50 frequency.
```{r}
plotallfunc(Unselected, HighBulk = "UnselectedC", LowBulk = "UnselectedA")

```

### Selected Bulks: Epistasis with Chromosome I
```{r}

plotallfunc(Selected, HighBulk = "SelectedA", LowBulk = "SelectedC")

```


```{r, eval = FALSE, include = FALSE}
HighBulk <- "SelectedC"
LowBulk <- "UnselectedC"
rawData = "C:\\Users\\cassa\\OneDrive\\Documents\\R_SiegalLab\\SequencingPractice\\mergedCuSO4.REF.SortedCat.vcf.output.table"
  
  mytitle <- paste(HighBulk, LowBulk, sep = " vs ")
  HNGLCDRXY <- read.table(rawData, header = TRUE)
  #Chroms = "NC_001142.9" #"NC_001140.6"
  Chroms = tail(unique(HNGLCDRXY$CHROM), -1)
  
    
  df <- importFromGATK(
        file = rawData,
        highBulk = HighBulk,
        lowBulk = LowBulk,
        chromList = Chroms
        )

df %>% merge(.,ChromKey) %>% na.omit() -> df


#Filter SNPs based on some criteria
df_filt <-
    filterSNPs(
        SNPset = df,
        refAlleleFreq = 0.10, #0.20
        minTotalDepth = 10, #100
        maxTotalDepth = 600, #400
        minSampleDepth = 4, #40
        minGQ = 99 #99
    )

  #df %>% merge(.,ChromKey)
  #df_filt <- df
  
  #Run G' analysi
  df_filt <- runGprimeAnalysis(
      SNPset = df_filt,
      windowSize = 2e4, #1e6
      outlierFilter = "deltaSNP")
  
  #Run QTLseq analysis
  df_filt <- runQTLseqAnalysis(
      SNPset = df_filt,
      windowSize = 2e4, #1e6
      popStruc = "F2",
      bulkSize = c(1000, 1000),
      replications = 10000,
      intervals = c(95, 99)
  )

  df_filt$idu <- row.names(df_filt)
  q <- 0.01
  fdrT <- getFDRThreshold(df_filt$pvalue, alpha = q)
  GprimeT <- df_filt[which(df_filt$pvalue == fdrT), "Gprime"]
  
  ##### NEW ###########
  
  sig_SCUC <- getSigRegions(df_filt)
  
```

### Testing Epistasis Data Chr. III

```{r, include = FALSE}
Selected_3 <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "SelectedC", 
                           rawData = rawData, 
                           Chroms = "NC_001135.5", windowSize = 1e4)

#plotallfunc(Selected_3, HighBulk = "SelectedA", LowBulk = "SelectedC")
QTL_3_Sel <- subset(Selected_3, Gprime > 5)
dim(QTL_3_Sel)
QTL_3_Sel

Selected_7 <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "SelectedC", 
                           rawData = rawData, 
                           Chroms = "NC_001139.9", windowSize = 2e4)

Oak_8 <- PipelineFunc(HighBulk = "SelectedA", LowBulk = "UnselectedA", 
                           rawData = rawData, 
                           Chroms = "NC_001140.6", windowSize = 1e4)


```


```{r, echo = FALSE}
plot.deltasnp <- plotQTLStatsCB(SNPset = Selected_3, var = "deltaSNP", plotIntervals = TRUE)


ggplot(data = Selected_3, aes(x = POS, y = Gprime)) + geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(Selected_3$POS), 
                                  by = 10^(floor(log10(max(Selected_3$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette[3]) + 
    geom_vline(xintercept = c(114385,114501), col = "gray", linetype = "dotted", size = 1) + #CEN3
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle("Selected, Chr III")
  

```

### Testing Epistasis Data Chr. VII

```{r, echo = FALSE}

#plotallfunc(Selected_3, HighBulk = "SelectedA", LowBulk = "SelectedC")

plot.deltasnp <- plotQTLStatsCB(SNPset = Selected_7, var = "deltaSNP", plotIntervals = TRUE)


ggplot(data = Selected_7, aes(x = POS, y = Gprime)) + geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(Selected_7$POS), 
                                  by = 10^(floor(log10(max(Selected_7$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette[7]) + 
    geom_vline(xintercept = c(496920,497038), col = "gray", linetype = "dotted", size = 1) + #CEN7
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle("Selected, Chr VII")
  
# Selected_7 <- subset(Selected_7, Gprime > 5)
# dim(Selected_7)
# #Selected_7
```

### Identifying CUP1 gene on Chr VIII

```{r, echo = FALSE}

#plotallfunc(Oak_8, HighBulk = "SelectedA", LowBulk = "SelectedC")
plot.deltasnp <- plotQTLStatsCB(SNPset = Oak_8, var = "deltaSNP", plotIntervals = TRUE)


ggplot(data = Oak_8, aes(x = POS, y = Gprime, color = CHROM)) + geom_line(size = 1) + 
  scale_x_continuous(breaks = seq(from = 0, to = max(Oak_8$POS), 
                                  by = 10^(floor(log10(max(Oak_8$POS))))), 
                    # labels = format_genomic(), 
                    name = "Genomic Position (Mb)") +
  theme(plot.margin = margin(b = 10, l = 20, r = 20, unit = "pt")) + 
  guides(colour = "none") +
    scale_colour_manual(values=CBchromPalette[8]) + 
    geom_vline(xintercept = 212535, linetype = "dashed", size = 1) + #CUP1 gene
    geom_vline(xintercept = c(105586), col = "gray", linetype = "dotted", size = 1) + #CEN8
  facet_grid(~CHROM, scales = "free_x", space = "free_x") + ggtitle("Oak Fixed, Chr VIII")
  
```


