---
title: "Sanity Check Simulation"
author: "Cassandra Buzby"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    code_folding: hide
  html_notebook:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(tidyr)
require(dplyr)
require(ggplot2)
require(reshape2)
ggplot2::theme_set(theme_light() + theme(text = element_text(size = 10)))

```

```{r, eval = FALSE}
glm_cb2_short <- function(..., W, formula, numgroups = FALSE, outputlength = 4, return = c("Z")) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  #MAYBEWORKS
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  #Return specific ones like z-score only
  if(return %in% "Z"){
    output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients)*0.5)+1):((length(summary(glm_fit)$coefficients)*0.75))]
  }
  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
}

glm_cb2_effectsize <- function(..., W, formula, numgroups = FALSE, outputlength = 4, return = c("Z")) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  #MAYBEWORKS
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  #Return specific ones like z-score only
  if(return %in% "Z"){
    output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients)*0)+1):((length(summary(glm_fit)$coefficients)*0.25))]
  }
  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
}

```

## Simulations

### Null Model

If you have a no effect, what does that look like?

```{r, eval = FALSE}
#let's just say everything is the same

Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

rbind(Unselected_O,
      Unselected_W,
      Selected_O,
      Selected_W) %>%
  
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> NullModel

NullModel %>% pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(B/b)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Bulk)) + geom_point()

NullModel %>% #filter(POS == 1) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             #Rep = Rep,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Null_GLM

# Null_GLM %>% ggplot(aes(x = POS, y = Summary, color = Factor)) + geom_point()
# 
# Null_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Bulk, y = Intercept)) + geom_point()
# Null_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Parent, y = Interaction)) + geom_point()



```

### Bulk Effects Only

Both parents have the same distribution in the selected bulks

```{r, eval = FALSE}
#let's just say everything is the same

Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 60, sd = 10),
                          b = rnorm(100, mean = 20, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 60, sd = 10),
                          b = rnorm(100, mean = 20, sd = 10))

rbind(Unselected_O,
      Unselected_W,
      Selected_O,
      Selected_W) %>%
  
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> BulkModel

BulkModel %>% pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(B/b)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Bulk)) + geom_point()

BulkModel %>% filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Bulk_GLM

# Bulk_GLM %>% ggplot(aes(x = POS, y = Summary, color = Factor)) + geom_point()
# 
# Bulk_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Bulk, y = Intercept)) + geom_point()
# Bulk_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Parent, y = Interaction)) + geom_point()



```

### Parental Epistasis

Okay so now what if this is actually epistatic, ie there is a 2x difference in the wine parent but a 4x difference in oak?

```{r, eval = FALSE}
#let's just say everything is the same

Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 70, sd = 10),
                          b = rnorm(100, mean = 10, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 60, sd = 10),
                          b = rnorm(100, mean = 20, sd = 10))

rbind(Unselected_O,
      Unselected_W,
      Selected_O,
      Selected_W) %>%
  
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> ParentalModel

ParentalModel %>% pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(B/b)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Bulk)) + geom_point()

ParentalModel %>% filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Parental_GLM

# Parental_GLM %>% ggplot(aes(x = POS, y = Summary, color = Factor)) + geom_point()
# 
# Parental_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Bulk, y = Intercept)) + geom_point()
# Parental_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Parent, y = Interaction)) + geom_point()



```



What if only one parent has the effect?

```{r, eval = FALSE}
#let's just say everything is the same

Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 60, sd = 10),
                          b = rnorm(100, mean = 20, sd = 10))

rbind(Unselected_O,
      Unselected_W,
      Selected_O,
      Selected_W) %>%
  
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> SingleParentModel

SingleParentModel %>% pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(B/b)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Bulk)) + geom_point()

SingleParentModel %>% filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> SingleParent_GLM

SingleParent_GLM %>% ggplot(aes(x = POS, y = Summary, color = Factor)) + geom_point()

# SingleParent_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Bulk, y = Intercept)) + geom_point()
# SingleParent_GLM %>% pivot_wider(names_from = Factor, values_from = Summary) %>% ggplot(aes(x = Parent, y = Interaction)) + geom_point()
# 


```

And now what if there's sign epistasis?

Okay so now what if this is actually epistatic, ie there is a 2x difference in the wine parent but a 4x difference in oak?

```{r, eval = FALSE}
#let's just say everything is the same

Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 40, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 20, sd = 10),
                          b = rnorm(100, mean = 60, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 60, sd = 10),
                          b = rnorm(100, mean = 20, sd = 10))

rbind(Unselected_O,
      Unselected_W,
      Selected_O,
      Selected_W) %>%
  
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> EpistaticModel

EpistaticModel %>% pivot_wider(names_from = Allele, values_from = Reads) %>%
  mutate(logOdds = log(B/b)) %>%
  ggplot(aes(x = POS, y = logOdds, color = Bulk)) + geom_point()

EpistaticModel %>% filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Epistatic_GLM

#Reversing the order
EpistaticModel %>% mutate(Bulk = gsub("C", "S", Bulk),
                          Parent = gsub("W", "A", Parent)) %>%
  filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Epistatic_GLM_revall

#Reversing the order
EpistaticModel %>% mutate(Bulk = gsub("D", "aD", Bulk)) %>%
  filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Epistatic_GLM_rev

Epistatic_GLM %>% ggplot(aes(x = Factor, y = (Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1))  + ggtitle("Sign Epistasis, C vs D")

Epistatic_GLM_revall  %>% ggplot(aes(x = Factor, y = (Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1)) + ggtitle("Sign Epistasis, aD vs C, A vs O")

Epistatic_GLM_rev %>% ggplot(aes(x = Factor, y = (Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1)) + ggtitle("Sign Epistasis, aD vs C")

```

What if we reverse Oak and Wine?

```{r, eval = FALSE}
#Reversing the order
EpistaticModel %>% mutate(Parent = gsub("W", "A", Parent)) %>%
  filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Epistatic_GLM_PA

Epistatic_GLM %>% ggplot(aes(x = Factor, y = abs(Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1))  + ggtitle("Sign Epistasis, O/W")

Epistatic_GLM_PA %>% ggplot(aes(x = Factor, y = abs(Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1))  + ggtitle("Sign Epistasis, A/O")
```

Finally, what if we just look at bulk?

```{r, eval = FALSE}
EpistaticModel %>% mutate(Bulk = gsub("D", "aD", Bulk)) %>%
  filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             # Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk",
                             outputlength = 2),
            Factor = (c("Intercept", "Bulk"))) -> Epistatic_BulkOnly

Epistatic_BulkOnly %>% ggplot(aes(x = Factor, y = (Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1))  + ggtitle("Sign Epistasis, Bulk Only")
```
And what is the effect size?

```{r, eval = FALSE}
EpistaticModel %>% mutate(Bulk = gsub("D", "aD", Bulk)) %>%
  filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_effectsize(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk*Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) -> Epistatic_EffectSize

Epistatic_EffectSize %>% ggplot(aes(x = Factor, y = (Summary), color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, position = position_jitterdodge(jitter.width = 0.1))  + ggtitle("Sign Epistasis, Effect Size")
```

Let's compare all of the models

```{r, eval = FALSE}
Epistatic_GLM %>% ggplot(aes(x = "Sign Epistasis", y = Summary, color = Factor)) + geom_boxplot()
Parental_GLM %>% ggplot(aes(x = "Parent Effect", y = Summary, color = Factor)) + geom_boxplot()
SingleParent_GLM %>% ggplot(aes(x = "Single Parent", y = Summary, color = Factor)) + geom_boxplot()
Null_GLM %>% ggplot(aes(x = "Null", y = Summary, color = Factor)) + geom_boxplot()

#What is the effect when you arrange by Intercept?
Epistatic_GLM %>%  pivot_wider(values_from = Summary, names_from = Factor) %>%
  ungroup() %>% 
  arrange(Intercept) %>% mutate(Row = row_number()) %>%
  pivot_longer(c(Intercept, Bulk, Parent, Interaction), names_to = "Factor", values_to = "Summary") %>%
  ggplot(aes(x = Row, y = Summary, color = Factor)) + geom_point()

#What is the effect when you arrange by Intercept?
Epistatic_GLM %>%  pivot_wider(values_from = Summary, names_from = Factor) %>%
  ungroup() %>% 
  arrange(Bulk) %>% mutate(Row = row_number()) %>%
  pivot_longer(c(Intercept, Bulk, Parent, Interaction), names_to = "Factor", values_to = "Summary") %>%
  ggplot(aes(x = Row, y = Summary, color = Factor)) + geom_point()

#What is the effect when you arrange by Intercept?
Epistatic_GLM %>%  pivot_wider(values_from = Summary, names_from = Factor) %>%
  ungroup() %>% 
  arrange(Parent) %>% mutate(Row = row_number()) %>%
  pivot_longer(c(Intercept, Bulk, Parent, Interaction), names_to = "Factor", values_to = "Summary") %>%
  ggplot(aes(x = Row, y = Summary, color = Factor)) + geom_point()

#What is the effect when you arrange by Intercept?
Epistatic_GLM %>%  pivot_wider(values_from = Summary, names_from = Factor) %>%
  ungroup() %>% 
  arrange(Interaction) %>% mutate(Row = row_number()) %>%
  pivot_longer(c(Intercept, Bulk, Parent, Interaction), names_to = "Factor", values_to = "Summary") %>%
  ggplot(aes(x = Row, y = Summary, color = Factor)) + geom_point()

```
Combine these

```{r, eval = FALSE, fig.width=12, fig.height=4}
rbind(data.frame(Null_GLM, ds = "A_Null"),
      data.frame(Parental_GLM, ds = "B_Bulk"),
      data.frame(SingleParent_GLM, ds = "C_Single Parent"),
      data.frame(Epistatic_GLM, ds = "D_Sign Epistasis")) -> Simulations

Simulations %>% ggplot(aes(x = ds, y = Summary, color = Factor)) + geom_hline(yintercept = 0) +
  geom_boxplot(size = 1, alpha = 0.4) + geom_point(size = 2, alpha = 0.2, width = 0.2, position = position_jitterdodge(jitter.width = 0.1)) 

```

```{r, eval = FALSE}

Simulations %>% pivot_wider(values_from = Summary, names_from = Factor) %>%
  ggplot(aes(x = Parent, y = Interaction, color = ds, fill = ds)) + geom_point() + geom_smooth(method = "lm") + 
  scale_color_manual(values = c("black", "gray", "purple", "firebrick")) +
  scale_fill_manual(values = c("black", "gray", "purple", "firebrick"))

Simulations %>% pivot_wider(values_from = Summary, names_from = Factor) %>%
  ggplot(aes(x = Bulk, y = Intercept, color = ds, fill = ds)) + geom_point() + geom_smooth(method = "lm") +
  scale_color_manual(values = c("black", "gray", "purple", "firebrick")) +
  scale_fill_manual(values = c("black", "gray", "purple", "firebrick"))

Simulations %>% pivot_wider(values_from = Summary, names_from = Factor) %>%
  ggplot(aes(x = Bulk, y = Interaction, color = ds, fill = ds)) + geom_point() + geom_smooth(method = "lm") +
  scale_color_manual(values = c("black", "gray", "purple", "firebrick")) +
  scale_fill_manual(values = c("black", "gray", "purple", "firebrick"))

Simulations %>% pivot_wider(values_from = Summary, names_from = Factor) %>%
  ggplot(aes(x = Parent, y = Intercept, color = ds, fill = ds)) + geom_point() + geom_smooth(method = "lm") +
  scale_color_manual(values = c("black", "gray", "purple", "firebrick")) +
  scale_fill_manual(values = c("black", "gray", "purple", "firebrick"))

```

## Investigation

How do we actually get more of a parentxinteraction effect? 

```{r, eval = FALSE}
Unselected_O <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "O",
                          B = rnorm(100, mean = 200, sd = 10),
                          b = rnorm(100, mean = 200, sd = 10))

Unselected_W <- data.frame(POS = 1:100,
                          Bulk = "D",
                          Parent = "W",
                          B = rnorm(100, mean = 800, sd = 10),
                          b = rnorm(100, mean = 400, sd = 10))

Selected_O <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "O",
                          B = rnorm(100, mean = 400, sd = 10),
                          b = rnorm(100, mean = 40, sd = 10))

Selected_W <- data.frame(POS = 1:100,
                          Bulk = "C",
                          Parent = "W",
                          B = rnorm(100, mean = 800, sd = 10),
                          b = rnorm(100, mean = 400, sd = 10))

rbind(Unselected_O, Unselected_W, Selected_O, Selected_W) %>%
  pivot_longer(c(B, b), names_to = "Allele", values_to = "Reads") %>%
  mutate(Reads = ceiling(Reads)) -> TestModel

TestModel %>% filter(Reads > 0) %>%
  group_by(POS) %>%
  mutate_if(is.character, as.factor) %>%
  summarize(Summary = glm_cb2_short(Allele = Allele,
                             Bulk = Bulk,
                             Parent = Parent,
                             W = Reads,
                             formula = "Allele ~ Bulk * Parent",
                             outputlength = 4),
            Factor = (c("Intercept", "Bulk", "Parent", "Interaction"))) %>%
  ggplot(aes(x = Factor, y = (Summary), color = Factor)) +
  geom_hline(yintercept = 0) +
  geom_boxplot(size = 1) + geom_jitter(size = 2, alpha = 0.4, width = 0.2) 

```


## Modeling epistasis data by different glms

```{r}
signepistasisdata <- data.frame(Bulk = c(0,0,1,1),
                                Parent = c(0,1,0,1),
                                A = c(50, 50, 80, 20),
                                B = c(50, 50, 20, 80))

signepistasisdata %>% ggplot(aes(x = Bulk, y = log2(A/B), color = as.factor(Parent))) + geom_point(size = 4, alpha = 0.3) + geom_line()
signepistasisdata %>% ggplot(aes(x = Parent, y = log2(A/B), color = as.factor(Bulk))) + geom_point(size = 4, alpha = 0.3) + geom_line()

signepistasisdata %>% pivot_longer(c(A,B), names_to = "Allele", values_to = "Reads")  %>% mutate(across(where(is.character),as.factor))-> signepistasispivot

glm_fit <- glm("Allele ~ Bulk*Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- data.frame(glm_fit$coefficients, model = "Bulk*Parent")
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk + Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk+Parent"))
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk"))
glm_fit$aic

maxcoefficients$names <- rownames(maxcoefficients)
maxcoefficients %>% mutate(names = gsub("1", "", names)) %>% mutate(names = gsub("2", "", names)) %>%
  ggplot(aes(x = names, y = glm_fit.coefficients, color = model)) + geom_point(size = 4, alpha = 0.3) +  geom_hline(yintercept = 0) +
 ggtitle("Sign Epistasis")

```

```{r}
signepistasisdata <- data.frame(Bulk = c(0,0,1,1),
                                Parent = c(0,1,0,1),
                                A = c(20, 20, 80, 20),
                                B = c(80, 80, 20, 80))

signepistasisdata %>% ggplot(aes(x = Bulk, y = log2(A/B), color = as.factor(Parent))) + geom_point(size = 4, alpha = 0.3) + geom_line()
signepistasisdata %>% ggplot(aes(x = Parent, y = log2(A/B), color = as.factor(Bulk))) + geom_point(size = 4, alpha = 0.3) + geom_line()

signepistasisdata %>% pivot_longer(c(A,B), names_to = "Allele", values_to = "Reads")  %>% mutate(across(where(is.character),as.factor))-> signepistasispivot

glm_fit <- glm("Allele ~ Bulk*Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- data.frame(glm_fit$coefficients, model = "Bulk*Parent")
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk + Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk+Parent"))
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk"))
glm_fit$aic

maxcoefficients$names <- rownames(maxcoefficients)
maxcoefficients %>% mutate(names = gsub("1", "", names)) %>% mutate(names = gsub("2", "", names)) %>%
  ggplot(aes(x = names, y = glm_fit.coefficients, color = model)) + geom_point(size = 4, alpha = 0.3) +  geom_hline(yintercept = 0) +
 ggtitle("Magnitude Epistasis")
```

```{r}
signepistasisdata <- data.frame(Bulk = c(0,0,1,1),
                                Parent = c(0,1,0,1),
                                A = c(40, 40, 20, 20),
                                B = c(40, 40, 80, 80))

signepistasisdata %>% ggplot(aes(x = Bulk, y = log2(A/B), color = as.factor(Parent))) + geom_point(size = 4, alpha = 0.3) + geom_line()
signepistasisdata %>% ggplot(aes(x = Parent, y = log2(A/B), color = as.factor(Bulk))) + geom_point(size = 4, alpha = 0.3) + geom_line()

signepistasisdata %>% pivot_longer(c(A,B), names_to = "Allele", values_to = "Reads")  %>% mutate(across(where(is.character),as.factor))-> signepistasispivot

glm_fit <- glm("Allele ~ Bulk*Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- data.frame(glm_fit$coefficients, model = "Bulk*Parent")
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk + Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk+Parent"))
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk"))
glm_fit$aic

maxcoefficients$names <- rownames(maxcoefficients)
maxcoefficients %>% mutate(names = gsub("1", "", names)) %>% mutate(names = gsub("2", "", names)) %>%
  ggplot(aes(x = names, y = glm_fit.coefficients, color = model)) + geom_point(size = 4, alpha = 0.3) +  geom_hline(yintercept = 0) +
 ggtitle("Bulk Only")
```

```{r}
signepistasisdata <- data.frame(Bulk = c(0,0,1,1),
                                Parent = c(0,1,0,1),
                                A = c(60, 60, 20, 20),
                                B = c(40, 40, 80, 80))

signepistasisdata %>% ggplot(aes(x = Bulk, y = log2(A/B), color = as.factor(Parent))) + geom_point(size = 4, alpha = 0.3) + geom_line()
signepistasisdata %>% ggplot(aes(x = Parent, y = log2(A/B), color = as.factor(Bulk))) + geom_point(size = 4, alpha = 0.3) + geom_line()

signepistasisdata %>% pivot_longer(c(A,B), names_to = "Allele", values_to = "Reads")  %>% mutate(across(where(is.character),as.factor))-> signepistasispivot

glm_fit <- glm("Allele ~ Bulk*Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- data.frame(glm_fit$coefficients, model = "Bulk*Parent")
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk + Parent", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk+Parent"))
glm_fit$aic

glm_fit <- glm("Allele ~ Bulk", data = as.data.frame(signepistasispivot), weights = Reads, family = binomial)
maxcoefficients <- rbind(maxcoefficients, data.frame(glm_fit$coefficients, model = "Bulk"))
glm_fit$aic

maxcoefficients$names <- rownames(maxcoefficients)
maxcoefficients %>% mutate(names = gsub("1", "", names)) %>% mutate(names = gsub("2", "", names)) %>%
  ggplot(aes(x = names, y = glm_fit.coefficients, color = model)) + geom_point(size = 4, alpha = 0.3) + 
  geom_hline(yintercept = 0) +
  ggtitle("Bulk Only") 
```
