---
title: "MergedVCFs_CuSO4_Gaussian_June24"
author: "Cassandra Buzby"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load packages
require(ggplot2)
require(tidyr)
require(dplyr)
require(reshape2)
require(cowplot)
require(data.table)

require(doParallel)
require(RColorBrewer)
require(scales)
require(circlize) 
require(stringr)
require(ggrepel)

require(cybrBSA)
require(lme4)

ggplot2::theme_set(theme_minimal() + theme(text = element_text(size = 10)) +
                     theme(#axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()))

ChromosomeScale <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(Summary = NA, Label = NA) %>% select(-delete)

ChromosomeScale$Start <- 30000
ChromosomeScale$End <- ChromosomeScale$POS - 30000

ChromosomeScale2 <- data.frame(CHROM = factor(as.character(as.roman(1:16)),
                                             levels = as.character(as.roman(1:16))),
                              start = rep(1, 16),
                              end = c(.23,.81,.32, 1.53, .58, .27, 1.09, .56, .44, .75, .67, 1.08, .92, .78, 1.09, .95)*1000000) %>% 
  pivot_longer(c(start, end), names_to = "delete", values_to = "POS") %>%
  mutate(summary = 0, label = "Bulk") %>% select(-delete)

# Loci to look at specifically

myloci <- data.frame(CHROM = c("V","V","IX", "III", "IV", "I", "III"),
                     POS = c(375215, 116167,389572, 198671, 46271, 203403, 260311),
                     name = c("FLO8", "URA3", "FLO11", "MAT", "HO", "FLO1", "TUP1"),
                     cat = c("Floc", "X", "Floc", "X", "X", "Floc", "Floc"))



## Functions for GLM all and Permutation all

glm_cb2_all <- function(..., W, formula, numgroups = FALSE, outputlength = 8) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  output <- summary(glm_fit)$coefficients[c(((length(summary(glm_fit)$coefficients)*0)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.25)),
                                            ((length(summary(glm_fit)$coefficients)*0.5)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.75)))]

  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
} 


################################################################################
# No replicates, fix Parent
cybrPermute_cb2_all <- function(dataset, 
                                R = 0, perp = 1, outlength = 4, 
                                glmform = "Allele ~ Bulk * Parent", 
                                inputlabels = c("Intercept", "Bulk", "Parent", "Interaction")){
  start.time <- Sys.time()
    
  print("Make sure that dilute bulk is labeled aD")
  print(paste("Your labels are:", inputlabels))

    if(R > 0){ #INCLUDE REPLICATES
        dataset %>% 
        distinct() %>% ungroup() %>%
        group_by(CHROM, POS, Allele, Bulk, Rep, Parent) %>% 
        summarize(culprits = length((SmoothCount))) %>% 
        merge(dataset) %>% 
        filter(culprits == 1) %>% 
        ungroup() %>%
        distinct() %>% #THIS IS IMPORTANT
        pivot_wider(names_from = Allele, values_from = SmoothCount) -> newnewtest    
    }else{ #DO NOT INCLUDE REPLICATES
        dataset %>% 
        distinct() %>% ungroup() %>%
        group_by(CHROM, POS, Allele, Bulk, Parent) %>% 
        summarize(culprits = length((SmoothCount))) %>% 
        merge(dataset) %>% 
        filter(culprits == perp) %>% 
        ungroup() %>%
        distinct() %>% #THIS IS IMPORTANT
        pivot_wider(names_from = Allele, values_from = SmoothCount) -> newnewtest
    }
  
    #PERMUTE TWICE
  if(R > 0){
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Rep, 
             Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Rep = Rep, 
                Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "A") -> shuffled_DiluteA2
    
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, 
             Rep, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Rep = Rep,
                Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "B") -> shuffled_DiluteB2
    
  }else{
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "A") -> shuffled_DiluteA2
    
    newnewtest %>% filter(Bulk == "aD",
                          CHROM %in% c("I", "III", "V", "VIII", "M") == FALSE) %>% 
      select(CHROM, POS, Parent, Oak, Wine) %>% 
      group_by(Parent) %>% mutate(Loc = paste(CHROM, POS)) %>%
      summarize(Parent = Parent, Oak = Oak, Wine = Wine, Loc = sample(Loc)) %>%
      mutate(Bulk = "B") -> shuffled_DiluteB2
    
  }
    
    rbind(shuffled_DiluteA2, shuffled_DiluteB2) %>% pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "SmoothCount") -> shuffletoglm2
    
    #RUN THE GLM
    if(R > 0) {
      shuffletoglm2 %>% na.omit() %>%
      group_by(Loc) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(Allele = Allele,
                                 Bulk = Bulk,
                                 Parent = Parent,
                                 Rep = Rep,
                                 W = SmoothCount,
                                 formula = glmform,
                                outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> glmresult
    }else{
      shuffletoglm2 %>% na.omit() %>%
      #Original Script
      group_by(Loc) %>%
      mutate_if(is.character, as.factor) %>%
        summarize(Summary = glm_cb2_all(Allele = Allele,
                                 Bulk = Bulk,
                                 Parent = Parent,
                                 W = SmoothCount,
                                 formula = glmform,
                                outputlength = length(inputlabels)*2),
                Factor = rep(inputlabels, 2),
                d = c(rep("Effect", length(inputlabels)),
                      rep("Z", length(inputlabels)))) -> glmresult
    }
    
    
    end.time = Sys.time()
    print(end.time - start.time)
    return(glmresult)
}

cybrInputGATKTable2 <- function(rawData, yeast = TRUE){

  require(dplyr)
  require(doParallel)
  require(foreach)

  HNGLCDRXY <- read.table(rawData, header = TRUE)

  #Identify the unique values besides AD/DP/GQ/PL
  gsub(".AD", "",
       gsub(".GQ", "",
            gsub(".DP","",
                 gsub(".PL","",
                      colnames(select(HNGLCDRXY, -CHROM, -POS, -REF, -ALT)))))) %>% unique() -> Samples
  #i <- Samples[1]

  resultscdf <- foreach(i=Samples,.combine=rbind) %dopar% {
    mydf <- HNGLCDRXY %>% select(CHROM, POS, REF, ALT) %>% mutate(Dataset = i)
    AD <- select(HNGLCDRXY,matches(c(i), ignore.case = FALSE)) %>% select(., contains("AD"))
    GQ <- select(HNGLCDRXY,matches(c(i), ignore.case = FALSE)) %>% select(., contains("GQ"))
    DP <- select(HNGLCDRXY,matches(c(i), ignore.case = FALSE)) %>% select(., contains("DP"))
    PL <- select(HNGLCDRXY,matches(c(i), ignore.case = FALSE)) %>% select(., contains("PL"))
    cbind(mydf, AD , GQ , DP, PL) -> mydftotal
    colnames(mydftotal) <- c(colnames(mydf), "AD", "GQ", "DP", "PL")

    mydftotal %>% separate(AD, c('AD.REF','AD.ALT'), extra='drop') %>%
      separate(PL, c('PL.REF','PL.ALT'), extra='drop') %>%
      #Added 10/18/23:
      select(CHROM, POS,REF,ALT,Dataset,AD.REF,AD.ALT,GQ,DP,PL.REF,PL.ALT) -> mycdf

    mycdf %>% filter(grepl(",", ALT)) %>% 
      separate(ALT, c("A1", "A2"), extra = 'merge') %>%
      separate(AD.ALT, c("AD1", "AD2"), extra = 'merge') %>%
      separate(PL.ALT, c("P1", "P2"), extra = 'merge') %>%
      
      pivot_longer(c(A1, A2), names_to = "NumAlt", values_to = "ALT") %>%
      pivot_longer(c(AD1, AD2), names_to = "NumADAlt", values_to = "AD.ALT") %>%
      pivot_longer(c(P1, P2), names_to = "NumPL", values_to = "PL.ALT") %>%
      mutate(NumAlt = gsub("A", "", NumAlt),
             NumADAlt = gsub("AD", "", NumADAlt),
             NumPL = gsub("P", "", NumPL)) %>%
      filter(NumAlt == NumPL,
             NumPL == NumADAlt) %>%
      select(CHROM, POS,REF,ALT,Dataset,AD.REF,AD.ALT,GQ,DP,PL.REF,PL.ALT) -> doublecdf
    
    doublecdf %>% filter(grepl(",", ALT)) %>%
      separate(ALT, c("A1", "A2"), extra = 'merge') %>%
      separate(AD.ALT, c("AD1", "AD2"), extra = 'merge') %>%
      separate(PL.ALT, c("P1", "P2"), extra = 'merge') %>%
      
      pivot_longer(c(A1, A2), names_to = "NumAlt", values_to = "ALT") %>%
      pivot_longer(c(AD1, AD2), names_to = "NumADAlt", values_to = "AD.ALT") %>%
      pivot_longer(c(P1, P2), names_to = "NumPL", values_to = "PL.ALT") %>%
      mutate(NumAlt = gsub("A", "", NumAlt),
             NumADAlt = gsub("AD", "", NumADAlt),
             NumPL = gsub("P", "", NumPL)) %>%
      filter(NumAlt == NumPL,
             NumPL == NumADAlt) %>%
      select(CHROM, POS,REF,ALT,Dataset,AD.REF,AD.ALT,GQ,DP,PL.REF,PL.ALT) -> triplecdf
    
    rbind(mycdf, doublecdf, triplecdf) -> newcdf
    
    newcdf
  }

  if(yeast == TRUE){
    ChromKey <- data.frame(chromosomes = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII",
                                         "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"),
                         CHROM = c("NC_001133.9", "NC_001134.8", "NC_001135.5", "NC_001136.10",
                                   "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6",
                                   "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5",
                                   "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1"))

    resultscdf %>% left_join(.,ChromKey) %>% select(-CHROM) %>% mutate(CHROM = chromosomes) %>% select(-chromosomes) -> results
  }else{
    results <- resultscdf
  }
  return(results)

}

```

# Pre-processing

## Load in table and match to oak or wine parents

```{r}
setwd("C:/Users/Cassandra/Documents/GitHub/Sequencing/Analysis/")

parentSNPids <- cybrConvertParentalAlleles(ParentFiles = c("Wine_VCF.txt", "Oak_VCF.txt"), Truncate = TRUE)
parentSNPids %>% group_by(CHROM, POS) %>% summarize(Type = Type, Unique = length(unique(Type))) -> pSNPs

```

## Exclude duplicates 

```{r, message = FALSE, warning=FALSE}
myfile <- "C:/Users/Cassandra/Documents/Data_NYU/Sequencing/HWTCNDMXY.SortedCat.vcf.output.table"

#GET RID OF EXCLUDED ONES
read.table(myfile, header = TRUE) -> testrawdata
testrawdata %>% select(CHROM, POS, ALT) %>% separate(ALT, into = c("First", "Second"), sep = ",") %>% na.omit() -> exclude

ChromKey <- data.frame(chromosomes = c("I", "II", "III", "IV", "V", "VI", "VII", "VIII",
                                         "IX", "X", "XI", "XII", "XIII", "XIV", "XV", "XVI", "M"),
                         CHROM = c("NC_001133.9", "NC_001134.8", "NC_001135.5", "NC_001136.10",
                                   "NC_001137.3", "NC_001138.5", "NC_001139.9", "NC_001140.6",
                                   "NC_001141.2", "NC_001142.9", "NC_001143.9", "NC_001144.5",
                                   "NC_001145.3", "NC_001146.8", "NC_001147.6", "NC_001148.4", "NC_001224.1"))

exclude %>% left_join(.,ChromKey) %>% select(-CHROM) %>% mutate(CHROM = chromosomes) %>% select(-chromosomes) -> exclude

exclude %>% mutate(locus = paste(CHROM, POS)) -> exclKEY

cybrInputGATKTable2(myfile) %>% mutate(Coverage = as.numeric(AD.REF) + as.numeric(AD.ALT)) %>%
  select(POS, CHROM, Dataset, GQ, AD.REF, AD.ALT, Coverage) -> rawdata


saveRDS(rawdata, file = "CSSVIII_A24_rawdataG.rds")

################################################################################
rawdata %>% #head(3000) %>%
  merge(parentSNPids) %>% mutate(REFW = as.numeric(Type == "Wine"), REFO = as.numeric(Type == "Oak")) %>%
  group_by(Dataset, CHROM, POS) %>%
  mutate(Wine = max(REFW * as.numeric(AD.REF), REFO * as.numeric(AD.ALT)),
         Oak = max(REFW * as.numeric(AD.ALT), REFO * as.numeric(AD.REF))) %>%
  select(Dataset, POS, CHROM, Coverage, Wine, Oak) %>%
  pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "Reads") -> rawdata_called

rawdata_called %>% mutate(locus = paste(CHROM, POS)) %>% filter(locus %in% exclKEY$locus == FALSE) %>% select(-locus) -> rawdata_called_ex


################################################################################

saveRDS(rawdata_called_ex, file = "CSSVIII_A24_rawdata_called_ex.rds")
```


### Separate out what could be smoothed here

```{r}

cybr_weightedgauss <- function(myx){
  myy <- dnorm(1:length(myx), mean = length(myx)/2, sd = 10)
  return(weighted.mean(x = myx, y = myy, na.rm = TRUE))
} 

plot(dnorm(1:200, mean = 200/2, sd = 10), main = "SD 10")
plot(dnorm(1:200, mean = 200/2, sd = 20), main = "SD 20")
plot(dnorm(1:200, mean = 200/2, sd = 100), main = "SD 100") #choosing this one for including all of the points
plot(dnorm(1:200, mean = 200/2, sd = 1000), main = "SD 1000")

# rd_ex %>% ungroup() %>% arrange(POS) %>% 
#   reframe(POS = POS, 
#           SmoothCount = frollapply(Reads, n = 600, FUN = cybr_weightedgauss, align = "center")) %>%
#   ggplot(aes(x = POS, y = SmoothCount)) + geom_point()

# Test_VII <- rawdata_called_ex %>% filter(Dataset == "HTG3TDMXY_n01_O8_451_E_2.fastq", CHROM == "VII") %>% pivot_wider(names_from = Allele, values_from = Reads) %>% unnest() %>% mutate(logOdds = log(Wine/Oak))
# 
# rawdata_called_ex %>% ungroup() %>% filter(Dataset == "HTG3TDMXY_n01_O8_451_E_2.fastq", CHROM == "VII") %>%
#   group_by(Dataset, CHROM, Allele) %>%
#   arrange(POS) %>%
#   reframe(POS = POS, SmoothCount = frollapply(Reads, n = 200, FUN = cybr_weightedgauss, align = "center")) %>% mutate(smooth = 200) -> rg_200
# 
# rawdata_called_ex %>% ungroup() %>% filter(Dataset == "HTG3TDMXY_n01_O8_451_E_2.fastq", CHROM == "VII") %>%
#   group_by(Dataset, CHROM, Allele) %>%
#   arrange(POS) %>%
#   reframe(POS = POS, SmoothCount = frollapply(Reads, n = 300, FUN = cybr_weightedgauss, align = "center")) %>% mutate(smooth = 300) -> rg_400
# 
# rawdata_called_ex %>% ungroup() %>% filter(Dataset == "HTG3TDMXY_n01_O8_451_E_2.fastq", CHROM == "VII") %>%
#   group_by(Dataset, CHROM, Allele) %>%
#   arrange(POS) %>%
#   reframe(POS = POS, SmoothCount = frollapply(Reads, n = 400, FUN = cybr_weightedgauss, align = "center")) %>% mutate(smooth = 400) -> rg_600
# 
# #saveRDS(rawdata_gauss, file = "rawdata_newG.rds")
# 
# rbind(rg_200,rg_400,rg_600) %>% pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>% mutate(logOdds = log(Wine/Oak)) -> G_logodds
# 
# 
# G_logodds %>% ggplot() + 
#   geom_point(data = Test_VII, aes(x = POS, y = logOdds), alpha = 0.3, color = "lightblue") +
#     geom_line(aes(x = POS, y = logOdds, color = as.factor(smooth))) 

rawdata_called_ex <- readRDS("CSSVIII_A24_rawdata_called_ex.rds")

unique(rawdata_called_ex$Dataset)

rawdata_called_ex %>% ungroup() %>% 
  group_by(Dataset, CHROM, Allele) %>%
  arrange(POS) %>%
  reframe(POS = POS, SmoothCount = frollapply(Reads, n = 200, FUN = cybr_weightedgauss, align = "center")) %>% mutate(smooth = 200) -> rawdata_smoothed_G200

rawdata_smoothed_G200 %>% mutate(SmoothCount = ceiling(SmoothCount)) %>% na.omit() -> rawdata_smoothed_G200

saveRDS(rawdata_smoothed_G200, file = "CSSVIII_A24_rawdata_smoothed_G200.rds")


```

## Separate into bulks, make ready for glms

```{r}

# rawdata_called_ex <- readRDS("CSSVIII_A24_rawdata_smoothed_G200.rds")
rawdata_smoothed_G200 <- readRDS("CSSVIII_A24_rawdata_smoothed_G200.rds")

# rawdata_called_ex %>% filter(grepl("AIG", Dataset) == FALSE) %>%
#   mutate(Dataset = gsub("HWMMFDMXY_n01_", "", Dataset)) %>%
#   mutate(Dataset = gsub(".fastq", "", Dataset)) %>% 
#   separate(Dataset, into = c("Bulk","Parent","Rep","Day"), sep = "_") -> rd_named

rawdata_smoothed_G200 %>% filter(grepl("AIG", Dataset) == FALSE) %>%
  mutate(Dataset = gsub("HWTCNDMXY_n01_", "", Dataset)) %>%
  mutate(Dataset = gsub(".fastq", "", Dataset)) %>% 
  separate(Dataset, into = c("Bulk","Parent","Rep","Day"), sep = "_") -> smoothdata_named

unique(rawdata_smoothed_G200$Dataset) #Found out I was missing all of these whoops

unique(smoothdata_named$Bulk)
unique(smoothdata_named$Parent)
unique(smoothdata_named$Rep)

table(smoothdata_named$Bulk,smoothdata_named$Day)

table(smoothdata_named$Bulk)
```


## Change into factors

```{r}

smoothdata_named %>% filter(Bulk %in% c("D", "C")) %>% mutate(Bulk = gsub("D", "A", Bulk))  %>% na.omit() %>%
  mutate_if(is.character, as.factor) %>% mutate(Sel = "C") -> rd_factor_cyclohex

smoothdata_named %>% filter(Bulk %in% c("D", "E")) %>% mutate(Bulk = gsub("D", "A", Bulk))  %>% na.omit() %>%
  mutate_if(is.character, as.factor) %>% mutate(Sel = "E") -> rd_factor_ethanol

smoothdata_named %>% filter(Bulk %in% c("D", "H")) %>% mutate(Bulk = gsub("D", "A", Bulk))  %>% na.omit() %>%
  mutate_if(is.character, as.factor) %>% mutate(Sel = "H") -> rd_factor_H2O2


contrasts(rd_factor_cyclohex$Parent) <- matrix(c(0.5, -0.5))
contrasts(rd_factor_ethanol$Parent) <- matrix(c(0.5, -0.5))
contrasts(rd_factor_H2O2$Parent) <- matrix(c(0.5, -0.5))

contrasts(rd_factor_cyclohex$Bulk) <- matrix(c(1, 0))
contrasts(rd_factor_ethanol$Bulk) <- matrix(c(1, 0))
contrasts(rd_factor_H2O2$Bulk) <- matrix(c(1, 0))

saveRDS(rd_factor_cyclohex, "CSSVIII_A24_rd_factor_cyclohex.rds")
saveRDS(rd_factor_ethanol, "CSSVIII_A24_rd_factor_ethanol.rds")
saveRDS(rd_factor_H2O2, "CSSVIII_A24_rd_factor_H2O2.rds")

```

################################################################################

# Running GLMs

```{r}
rd_factor_cyclohex <- readRDS("CSSVIII_A24_rd_factor_cyclohex.rds") 
rd_factor_ethanol <- readRDS("CSSVIII_A24_rd_factor_ethanol.rds")
rd_factor_H2O2 <- readRDS("CSSVIII_A24_rd_factor_H2O2.rds")

rd_factor <- rbind(rd_factor_cyclohex,rd_factor_ethanol,rd_factor_H2O2)
```

## Make function to run glmer

```{r}
glmer_cb2_short <- function (..., W, formula, numgroups = FALSE, outputlength = 4, 
    return = c("Z")) 
{
    data <- list(...)
    
    require(lme4)
    if (is.null(W) || is.null(formula)) {
        stop("Weights (W) and formula must be provided")
    }
    glm_formula <- as.formula(formula)
    if (!all(names(data) %in% all.vars(glm_formula))) {
        stop("One or more variables in the formula are not provided as arguments")
    }
    for (i in all.vars(glm_formula)) {
        if (length(unique(as.data.frame(data)[, i])) < 2) {
            output <- rep(NA, outputlength)
            return(output)
        }
    }
    glm_fit <- glmer(glm_formula, data = as.data.frame(data), weights = W, 
        family = binomial)
    if (return %in% "Z") {
        output <- summary(glm_fit)$coefficients[((length(summary(glm_fit)$coefficients) * 
            0.5) + 1):((length(summary(glm_fit)$coefficients) * 
            0.75))]
    }
    if (length(output) == outputlength) {
        return(output)
    }
    else {
        return(rep(NA, outputlength))
    }
}
```

### Glmer for when we have more time would add to this

```{r}
rd_factor %>% filter(CHROM != "M", CHROM != "I") %>% distinct() %>% 
  group_by(CHROM, POS, Sel) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Parent,
                                                            #Rep = Rep,
                                                            Day = Day,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 5,
                                                            formula = "Allele ~ Bulk*Background + Day "),
                                                                  label = c("cept","Bulk", "Background", "Interaction", "Day"))  -> Aug24_CSS8_glm

saveRDS(Aug24_CSS8_glm, file = "Aug24_CSS8_glm.rds")

rd_factor_cyclohex %>% filter(CHROM != "M", CHROM != "I") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Parent,
                                                            #Rep = Rep,
                                                            #Day = Day,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Cyclo_Aug24_CSS8_glm

```

```{r}
Aug24_CSS8_glm %>% filter(CHROM != "VIII", label %in% c("Bulk", "Interaction")) %>%
  ggplot(aes(x = POS, y = abs(zscore), color = label, linetype = Sel)) + geom_line() +
  facet_grid(Sel~CHROM, scales = "free", space = "free_x")
```

### GLM for a quick look

```{r}

rd_factor_cyclohex %>% filter(CHROM != "M", CHROM != "VIII") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Parent,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS8_glm_cyclohex

saveRDS(Aug24_CSS8_glm_cyclohex, file = "Aug24_CSS8_glm_cyclohex.rds")

rd_factor_ethanol %>% filter(CHROM != "M", CHROM != "VIII") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Parent,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS8_glm_ethanol

saveRDS(Aug24_CSS8_glm_ethanol, file = "Aug24_CSS8_glm_ethanol.rds")

rd_factor_H2O2 %>% filter(CHROM != "M", CHROM != "VIII") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Parent,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS8_glm_H2O2

saveRDS(Aug24_CSS8_glm_H2O2, file = "Aug24_CSS8_glm_H2O2.rds")

```

```{r, fig.width=12, fig.height=4}
Aug24_CSS8_glm_H2O2 %>% filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free") +
  ggtitle("H2O2")

Aug24_CSS8_glm_ethanol %>% filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")+
  ggtitle("EtOH")

Aug24_CSS8_glm_cyclohex %>% filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = zscore, color = label)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")+
  ggtitle("Cyc")

Aug24_CSS8_glm_H2O2 %>% mutate(Selection = "H2O2") -> temp1
Aug24_CSS8_glm_ethanol %>% mutate(Selection = "EtOH") -> temp2
Aug24_CSS8_glm_cyclohex %>% mutate(Selection = "Cycloheximide") %>%
  rbind(temp1) %>%
  rbind(temp2) -> CSSVIII_Aug2024_glm

rm(temp1)
rm(temp2)

CSSVIII_Aug2024_glm %>% filter(label == "Bulk") %>% ggplot(aes(x = POS, y = zscore, color = Selection)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free")

```

# Load previous glms

```{r}

#With 2 replicates included
Fluc_CSS1_glm <- readRDS("C:/Users/Cassandra/Documents/R_FileTransfer/StandardGLM/HGVMVDRX2_CSS1_glm_alld.rds")

#With no replicates
Fluc_CSS1_glm <- readRDS("C:/Users/Cassandra/Documents/R_FileTransfer/StandardGLM/HGVMVDRX2norep_CSS1_glm_all.rds") %>% 
  mutate(zscore = Summary, label = Factor, Selection = "Fluconazole") %>%
  select(-Summary, -Factor) %>%
  na.omit() 

CuSO4_CSS1_glmer_1byRep <- readRDS("CuSO4_CSS1_glmer_1byRepG.rds")
Aug24_CSS1_glm_H2O2 <- readRDS("Aug24_CSS1_glm_H2O2.rds")
Aug24_CSS1_glm_cyclohex <- readRDS("Aug24_CSS1_glm_cyclohex.rds")
Aug24_CSS1_glm_ethanol <- readRDS("Aug24_CSS1_glm_ethanol.rds")

Aug24_CSS1_glm_H2O2 %>% mutate(Selection = "H2O2") -> temp1
Aug24_CSS1_glm_ethanol %>% mutate(Selection = "EtOH") -> temp2
Aug24_CSS1_glm_cyclohex %>% mutate(Selection = "Cycloheximide") %>%
  rbind(temp1) %>%
  rbind(temp2) %>%
  mutate(CSS = 1) -> CSS1_Aug2024_glm

Aug24_CSS8_glm_H2O2 %>% mutate(Selection = "H2O2") -> temp1
Aug24_CSS8_glm_ethanol %>% mutate(Selection = "EtOH") -> temp2
Aug24_CSS8_glm_cyclohex %>% mutate(Selection = "Cycloheximide") %>%
  rbind(temp1) %>%
  rbind(temp2)%>%
  mutate(CSS = 8) -> CSSVIII_Aug2024_glm

rm(temp1)
rm(temp2)

```

# Load in post glm/glmer

```{r}
CSS1_Aug2024_glm %>%
  rbind(CSSVIII_Aug2024_glm) %>%
  filter(label == "Bulk") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = factor(CSS))) + geom_line() + facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("Bulk Effects") +
  theme(legend.position = "bottom")

CSS1_Aug2024_glm %>%
  rbind(CSSVIII_Aug2024_glm) %>%
  filter(label == "Interaction") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = factor(CSS))) + geom_line() + facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("Interaction Effects") +
  theme(legend.position = "bottom")
  
```

```{r, fig.width=12, fig.height=4}

CuSO4_CSS1_glmer_1byRep %>% 
  mutate(Selection = "CuSO4") %>%
  rbind(CSSVIII_Aug2024_glm) %>%
  rbind(CSS1_Aug2024_glm) %>%
  rbind(Fluc_CSS1_glm) %>%
  filter(label == "Bulk") %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = Selection)) + geom_line() + facet_grid(~CHROM, scales = "free", space = "free") + ggtitle("CSS I Bulk Effects") +
  theme(legend.position = "bottom")

```



```{r}
CuSO4_CSS1_glmer_1byRep %>% 
  mutate(Selection = "CuSO4") %>%
  rbind(CSS1_Aug2024_glm) %>%
    rbind(Fluc_CSS1_glm) %>%
  filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line(size = 0.5, alpha = 0.8) + 
  geom_hline(yintercept = 1.1)+
  facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("CSS I Interaction Effects")+ #ylim(0,2) +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("black", "firebrick3"))

CuSO4_CSS8_glmer_1byRep %>% 
  mutate(Selection = "CuSO4") %>%
  rbind(CSSVIII_Aug2024_glm) %>%
  filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line(size = 0.5, alpha = 0.8) + 
  geom_hline(yintercept = 1.1)+
  facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("CSS VIII Interaction Effects")+ #ylim(0,2) +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("black", "firebrick3"))
```




## Permutations for significance

Actually running a permutation on this

```{r}
#unique(rd_factor_cyclohex$Bulk)
rd_factor_cyclohex %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Selected") -> rd_shuffled_selectedc

rd_factor_cyclohex %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Dilute") %>%
  rbind(rd_shuffled_selectedc) -> Perm1c

Perm1c %>% ungroup() %>%
  pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "SmoothCount") %>% unnest() %>%
  mutate(POS = as.numeric(POS)) %>%
  mutate_if(is.character, as.factor) -> Perm1contrasts_c

contrasts(Perm1contrasts_c$Background) <- matrix(c(-0.5, 0.5))
contrasts(Perm1contrasts_c$Bulk)


Perm1contrasts_c %>% filter(CHROM != "M", CHROM != "I") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Background,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS1_glm_cyclohex_PERM

Aug24_CSS1_glm_cyclohex_PERM %>% mutate(Selection = "Cyclohex") -> Aug24_CSS1_glm_cyclohex_PERM

saveRDS(Aug24_CSS1_glm_cyclohex_PERM, file = "Aug24_CSS1_glm_cyclohex_PERM.rds")

```

```{r}
rd_factor_ethanol %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Selected") -> rd_shuffled_selected_e

rd_factor_ethanol %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Dilute") %>%
  rbind(rd_shuffled_selected_e) -> Perm1_e

Perm1_e %>% ungroup() %>%
  pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "SmoothCount") %>% unnest() %>%
  mutate(POS = as.numeric(POS)) %>%
  mutate_if(is.character, as.factor) -> Perm1contrasts_e

contrasts(Perm1contrasts_e$Background) <- matrix(c(-0.5, 0.5))
contrasts(Perm1contrasts_e$Bulk)


Perm1contrasts_e %>% filter(CHROM != "M", CHROM != "I") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Background,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS1_glm_ethanol_PERM

Aug24_CSS1_glm_ethanol_PERM %>% mutate(Selection = "Ethanol") -> Aug24_CSS1_glm_ethanol_PERM

saveRDS(Aug24_CSS1_glm_ethanol_PERM, file = "Aug24_CSS1_glm_ethanol_PERM.rds")

```

```{r}


rd_factor_H2O2 %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Selected") -> rd_shuffled_selected_h

rd_factor_H2O2 %>% filter(Bulk == "A",
                     CHROM %in% c("I", "VIII", "M", "III", "V") == FALSE) %>% 
  pivot_wider(names_from = Allele, values_from = SmoothCount) %>% unnest() %>%
  mutate(label = paste(CHROM, POS, sep = "_")) %>%
  #group_by(Pool, Dataset) %>%
  summarize(NewPOS = sample(label),
            Oak = Oak,
            Wine = Wine,
            Background = Parent) %>%
  separate(NewPOS, into = c("CHROM", "POS"), sep = "_") %>%
  mutate(Bulk = "Dilute") %>%
  rbind(rd_shuffled_selected_h) -> Perm1_h

Perm1_h %>% ungroup() %>%
  pivot_longer(c(Oak, Wine), names_to = "Allele", values_to = "SmoothCount") %>% unnest() %>%
  mutate(POS = as.numeric(POS)) %>%
  mutate_if(is.character, as.factor) -> Perm1contrasts_h

contrasts(Perm1contrasts_h$Background) <- matrix(c(-0.5, 0.5))
contrasts(Perm1contrasts_h$Bulk)


Perm1contrasts_h %>% filter(CHROM != "M", CHROM != "I") %>% distinct() %>% 
  group_by(CHROM, POS) %>% summarize(zscore = glm_cb2_short(Bulk = Bulk,  
                                                            Background = Background,
                                                            Allele = Allele,
                                                            W = SmoothCount, outputlength = 4,
                                                            formula = "Allele ~ Bulk*Background"),
                                                                  label = c("cept","Bulk", "Background", "Interaction"))  -> Aug24_CSS1_glm_H2O2_PERM

Aug24_CSS1_glm_H2O2_PERM %>% mutate(Selection = "H2O2") %>% ungroup() %>% select(-Day) -> Aug24_CSS1_glm_H2O2_PERM

saveRDS(Aug24_CSS1_glm_H2O2_PERM, file = "Aug24_CSS1_glm_H2O2_PERM.rds")
```

```{r}
rbind(Aug24_CSS1_glm_ethanol_PERM, Aug24_CSS1_glm_cyclohex_PERM, Aug24_CSS1_glm_H2O2_PERM) %>% 
  na.omit() %>%
  ungroup() %>%
  filter(abs(zscore) < 10) %>%
  group_by(Selection, label) %>%
  summarize(q5 = quantile(abs(zscore), 0.95)) -> q5_CSSVIII_Aug24

# Aug24_CSS1_glm_H2O2_PERM %>% na.omit() %>% group_by(label) %>% summarize(q5 = quantile(abs(zscore), 0.95)) %>% mutate(Selection = "H2O2") -> q5_h
# Aug24_CSS1_glm_ethanol_PERM %>% na.omit() %>% group_by(label) %>% summarize(q5 = quantile(abs(zscore), 0.95)) %>% mutate(Selection = "EtOH") -> q5_e
# Aug24_CSS1_glm_cyclohex_PERM %>% na.omit() %>% group_by(label) %>% summarize(q5 = quantile(abs(zscore), 0.95)) %>% mutate(Selection = "Cycloheximide") -> q5_c
# 
# rbind(q5_h,q5_e,q5_c) -> q5_CSSVIII_Aug24

saveRDS(q5_CSSVIII_Aug24, file = "q5_CSSVIII_Aug24.rds")

rbind(Aug24_CSS1_glm_H2O2_PERM, Aug24_CSS1_glm_ethanol_PERM, Aug24_CSS1_glm_cyclohex_PERM) %>% 
  ggplot(aes(x = abs(zscore), color = Selection, linetype = label)) + geom_density() +
  theme_bw() + xlim(0, 10)

```

```{r, fig.width=12, fig.height=5}
unique(CSSVIII_Aug2024_glm$Selection)

CSSVIII_Aug2024_glm %>% merge(q5_CSSVIII_Aug24) %>%
  filter(label %in% c("Bulk", "Interaction")) %>% 
  ggplot(aes(x = POS, y = abs(zscore), color = label)) + geom_line(size = 0.5, alpha = 0.8) + 
  geom_hline(aes(yintercept = q5, color = label, linetype = label), alpha = 0.8)+
  facet_grid(Selection~CHROM, scales = "free", space = "free") + ggtitle("CSS I Interaction Effects")+ #ylim(0,2) +
  theme(legend.position = "bottom") +
  scale_color_manual(values = c("black", "maroon")) +
  scale_linetype_manual(values = c(2,4))
  
```

# Sanity Check

If you have 3 things that could all interact, you have to check every pairwise combination, so A/a, B/b, and C/c:

1. Ab
2. aB
3. AB
4. ab
5. bC
6. Bc
7. BC
8. bc
9. Ac
10. aC
11. AC
12. ac

But that's not how it works, since we actually want to know how those two genes change anything based on just those two. So it would be:

1. AxB
2. BxC
3. AxC

Okay instead, you have 26 letter, so each one can pair with another for an effect. You have:

A x B..Z (25 chances)
B x A..Z (25 -1 chances)
C x A..Z (25 - A and B)
D x A..Z (25 - A and B and C)

Or if we make it simpler, out of 5, it's this:

A x B..E (4 chances)
B x A..E (4 -1 chances)
C x A..E (4 - A and B)
D x A..E (4 - A and B and C)
E x A..D (4 - A and B and C and D)

So that's 4 + 3 + 2 + 1 = 10
```{r}
#not this
factorial(4)

#Sum? But it would have to be n-1...
4*(4+1)/2

((5-1)*(5-1+1))/2

5*(5-1)/2

```

