---
title: "Simulations of Sign vs Mag Epistasis"
author: "Cass"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load packages
require(ggplot2)
require(tidyr)
require(dplyr)
require(reshape2)
require(cowplot)
require(data.table)

require(doParallel)
require(RColorBrewer)
require(scales)
require(circlize) 
require(stringr)
require(ggrepel)

require(cybrBSA)
require(lme4)

ggplot2::theme_set(theme_minimal() + theme(text = element_text(size = 10)) +
                     theme(#axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()))

glm_cb2_all <- function(..., W, formula, numgroups = FALSE, outputlength = 8) {
  data <- list(...)
  
  #Ensure that there is a formula and W parameter
  if (is.null(W) || is.null(formula)) {
    stop("Weights (W) and formula must be provided")
  }
  #Set formula
  glm_formula <- as.formula(formula)
  #Ensure that formula works for the data provided
  if (!all(names(data) %in% all.vars(glm_formula))) {
    stop("One or more variables in the formula are not provided as arguments")
  }
  
  #########################
  for(i in all.vars(glm_formula)){
    if(length(unique(as.data.frame(data)[,i])) < 2){
      output <- rep(NA, outputlength)
      #print("Not enough levels within groups")
      
      return(output)
    }
  }
  
  glm_fit <- glm(glm_formula, data = as.data.frame(data), weights = W, family = binomial)
  
  output <- summary(glm_fit)$coefficients[c(((length(summary(glm_fit)$coefficients)*0)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.25)),
                                            ((length(summary(glm_fit)$coefficients)*0.5)+1):
                                            ((length(summary(glm_fit)$coefficients)*0.75)))]

  
  if(length(output) == outputlength){
    return(output)
  }else{
    return(rep(NA, outputlength))
  }
  
} 

```

## Load Data

```{r}
 CuSO4_CSS1_glmer_1byRep <- readRDS("CuSO4_CSS1_glmer_1byRepG.rds")
CuSO4_CSS8_glmer_1byRep <- readRDS("CuSO4_CSS8_glmer_1byRepG.rds")
q5_all <- readRDS("q5_CuSO4_CSS.rds")


CuSO4_CSS1_glmer_1byRep %>% filter(CHROM != "I") %>% mutate(CSS = "I") -> temp1
CuSO4_CSS8_glmer_1byRep %>% mutate(CSS = "VIII") %>%
  rbind(temp1) -> AllCuSO4_glmer_1byRep
```

## What would perfect sign epistasis look like?

Sign epistasis reflects when the effect (y axis) of an allele (different lines) differs in the context of another allele (parent, x axis). If the slope is going the same direction, this is magnitude epistasis, and if the slopes are equal, there is no epistasis. The phenotype here is cell number, and so effects are the number of cells different between parents.

```{r}
#Example of allele A having the effect of 1 regardless of parent
data.frame(A0 = c(0,0),
           A1 = c(1,1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1)+ theme(legend.position = "left")  -> p1

#Example of allele A having the effect of 1 or -1 only in P1; SIGN EPISTASIS
data.frame(A0 = c(0,1),
           A1 = c(0,-1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1)+ theme(legend.position = "none") -> p2

#Example of allele A having the effect of 1 only in non-matching parent; SIGN EPISTASIS
data.frame(A0 = c(1,0),
           A1 = c(0,1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1) + theme(legend.position = "none")-> p3

cowplot::plot_grid(p1, p2, p3, nrow = 1)
```

We can also show that this pattern continues no matter what the actual cell count is

```{r}
data.frame(A0 = c(1,0),
           A1 = c(0,1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  mutate(Count = Count * 10) %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1) + theme(legend.position = "none") -> p4

data.frame(A0 = c(1,0),
           A1 = c(0,1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  mutate(Count = Count +20) %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1) + theme(legend.position = "none") -> p5

plot_grid( p4, p5)

```
We also have unselected bulks; these serve as the null for expectations of actual effects, so that each effect is zeroed out to be relative to that unselected bulk:

```{r}
data.frame(A0 = c(1,0),
           A1 = c(0,1),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  mutate(Count = Count * 10 + 1) %>%
  mutate(UnselectedCount = abs(rnorm(4))) %>%
  mutate(Diff = Count - UnselectedCount) -> TestWithUns

TestWithUns %>%
  ggplot(aes(x = Parent, y = Diff, color = Allele)) + geom_line(size = 2) + theme(legend.position = "none") +
  geom_line(aes(x = Parent, y = Count, color = Allele), linetype = "dashed", size = 1) +
  geom_line(aes(x = Parent, y = UnselectedCount, color = Allele), linetype = "dotted", size = 1)

```

Using this, we should also be able to calculate log ratios of each. We first assume that the unselected bulk has no effect, then take the unselected bulk into consideration to calculate.

```{r}
TestWithUns %>% select(Parent, Allele, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
  mutate(logAllele = log(A1/A0)) %>%
  ggplot(aes(x = Parent, y = logAllele)) + geom_line(size = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", size = 1, color = "gray") -> p6

TestWithUns %>% pivot_longer(c(Count, UnselectedCount), names_to = "Selection", values_to = "Count") %>%
  select(Parent, Allele, Selection, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
  mutate(logAllele = log(A1/A0)) %>%
  ggplot(aes(x = Parent, y = logAllele, linetype = Selection)) + geom_line(size = 1)  -> p7

plot_grid(p6, p7, rel_widths = c(1,1.5))
  
```

Let's demonstrate what magnitude epistasis would look like in the same way

```{r}
data.frame(A0 = c(0,-1),
           A1 = c(5,6),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  mutate(Count = Count + 10) %>%
  #mutate(UnselectedCount = abs(rnorm(4, mean = 10, sd =5))) %>%
  mutate(UnselectedCount = c(10,10,10,10)) %>%
  mutate(Diff = Count/UnselectedCount) -> TestWithUns

TestWithUns %>%
  ggplot(aes(x = Parent, y = Diff, color = Allele)) + geom_line(size = 2) + theme(legend.position = "none") -> p61

TestWithUns %>%
  ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1) + theme(legend.position = "none") +
  #geom_line(aes(x = Parent, y = Count, color = Allele), linetype = "dashed", size = 1) +
  geom_line(aes(x = Parent, y = UnselectedCount, color = Allele), linetype = "dashed", size = 1) -> p62

TestWithUns %>% select(Parent, Allele, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
  mutate(logAllele = log(A1/A0)) %>%
  ggplot(aes(x = Parent, y = logAllele)) + geom_line(size = 1) +
  geom_hline(aes(yintercept = 0), linetype = "dashed", size = 1, color = "gray") -> p6

TestWithUns %>% pivot_longer(c(Count, UnselectedCount), names_to = "Selection", values_to = "Count") %>%
  select(Parent, Allele, Selection, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
  mutate(logAllele = log(A1/A0)) %>%
  ggplot(aes(x = Parent, y = logAllele, linetype = Selection)) + geom_line(size = 1) +
  theme(legend.position = "bottom") -> p7

plot_grid(p62, p61, p6, p7, labels = c("Null"))

for(i in 1:10){
  data.frame(A0 = c(0,-1),
           A1 = c(5,6),
           Parent = c(0,1)) %>%
  pivot_longer(c(A0, A1), names_to = "Allele", values_to = "Count") %>%
  mutate(Count = Count + 10) %>%
  mutate(UnselectedCount = abs(rnorm(4, mean = 10, sd = 5))) %>%
  mutate(Diff = Count/UnselectedCount) -> TestWithUns #Divide or Subtract

    TestWithUns %>%
      ggplot(aes(x = Parent, y = Diff, color = Allele)) + geom_line(size = 2) + theme(legend.position = "none") -> p61

    TestWithUns %>%
      ggplot(aes(x = Parent, y = Count, color = Allele)) + geom_line(size = 1) + theme(legend.position = "none") +
      #geom_line(aes(x = Parent, y = Count, color = Allele), linetype = "dashed", size = 1) +
      geom_line(aes(x = Parent, y = UnselectedCount, color = Allele), linetype = "dashed", size = 1) -> p62

    TestWithUns %>% select(Parent, Allele, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
      mutate(logAllele = log(A1/A0)) %>%
      ggplot(aes(x = Parent, y = logAllele)) + geom_line(size = 1) +
      geom_hline(aes(yintercept = 0), linetype = "dashed", size = 1, color = "gray") -> p6

    TestWithUns %>% pivot_longer(c(Count, UnselectedCount), names_to = "Selection", values_to = "Count") %>%
      select(Parent, Allele, Selection, Count) %>% pivot_wider(names_from = Allele, values_from = Count) %>%
      mutate(logAllele = log(A1/A0)) %>%
      ggplot(aes(x = Parent, y = logAllele, linetype = Selection)) + geom_line(size = 1) +
      theme(legend.position = "none") -> p7



    print(plot_grid(p62, p61, p6, p7))
}
```
## GLM for counts

Now that we have counts and know what to do with them, and assuming that Selected/Unselected for each is truly the determinant of sign epistasis, what happens if we simulate counts and categorize as sign or magnitude epistasis?

```{r}
totalsims <- 1000
avgmean <- 300
data.frame(S00 = round(rnorm(mean = avgmean, n = totalsims, sd = 100)), 
           S01 = round(rnorm(mean = avgmean, n = totalsims, sd = 100)), 
           S10 = round(rnorm(mean = avgmean, n = totalsims, sd = 100)), 
           S11 = round(rnorm(mean = avgmean, n = totalsims, sd = 100)),
           U00 = round(rnorm(mean = avgmean, n = totalsims, sd = 10)), 
           U01 = round(rnorm(mean = avgmean, n = totalsims, sd = 10)), 
           U10 = round(rnorm(mean = avgmean, n = totalsims, sd = 10)), 
           U11 = round(rnorm(mean = avgmean, n = totalsims, sd = 10))) %>%
  mutate(Name = as.character(1:totalsims)) %>%
  pivot_longer(-Name) %>%
  separate(name, into = c("Selection", "Parent", "Allele"), sep = c(1,2)) %>%
  mutate_if(is.character, as.factor) %>%
  mutate(value = abs(value)) -> redone_test

redone_test %>% pivot_wider(names_from = Allele, names_prefix = "A", values_from = value) %>%
  mutate(value = A0/A1) %>%
  transmute(Name = Name, sp = paste(Selection, Parent, sep = ""), value = A0/A1) %>%
  pivot_wider(names_from = sp, values_from = value) %>%
  mutate(Gamma = S0 - U0, Delta = S1 - U1) %>%
  mutate(Sign = (Gamma > 0 & Delta < 0) | (Gamma < 0 & Delta > 0)) -> redone_gd

contrasts(redone_test$Selection) <- matrix(c(1,0))
contrasts(redone_test$Parent) <- matrix(c(-0.5,0.5))

################################################################################
redone_test %>%
  group_by(Name) %>%
  summarize(Zscore = glm_cb2_short(Allele = Allele, Selection = Selection, Parent = Parent,
                            W = value, formula = "Allele ~ Selection*Parent"),
            Lab = c("cept", "Selection", "Parent", "Interaction")) %>%
  merge(redone_gd) %>% distinct() -> redone_glm

#FIND THE RATIO HERE
redone_glm %>% 
  select(Name, Zscore, Lab, Sign) %>%
  pivot_wider(names_from = Lab, values_from = Zscore) %>%
  mutate(ratio = log(abs(Interaction/Selection))) %>%
  ggplot(aes(x = Sign, y = ratio)) + 
  geom_jitter(aes(color = ratio > 0), alpha = 0.1) +
  geom_boxplot(aes(color = Sign)) + 
  ggtitle("Simulation Results of GLM") +
  scale_color_manual(values = c("black", "salmon","gray", "gray"))+
  theme(legend.position = "none") +
  ylab("abs Interaction/Bulk") 

redone_gd %>%
  filter(Name %in% c(1:9)) %>%
  pivot_longer(c(S0, S1, U0, U1), names_to = c("Selection", "Parent"), names_sep = 1) %>%
  ggplot(aes(x = as.numeric(Parent), y = value, linetype = Selection, color = Sign)) + geom_line(size = 1) +
  geom_hline(aes(yintercept = 0), color = "gray")+ geom_line() + 
  facet_grid(Selection ~ Name) +
  scale_color_manual(values = c("black", "purple", "gray")) +
  ggtitle("Sample of Bulk Differences") +
  theme(legend.position = "bottom")

redone_gd %>%
  filter(Sign == TRUE) -> SignList

redone_test %>%
  filter(Name %in% c(1:20)) %>%
  mutate(Name = factor(Name, levels = 1:20)) %>%
  pivot_wider(names_from = Selection, values_from = value) %>%
  mutate(actualeffect = S/U) %>%
  ggplot(aes(x = as.numeric(Parent), y = actualeffect, linetype = Allele, color = Name %in% SignList$Name)) + 
  geom_line(size = 1) +
  scale_color_manual(values = c("black", "salmon")) +
  scale_linetype_manual(values = c(1,1)) +
  facet_wrap("Name") +theme_bw() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = breaks_pretty(n = 1)) +
  xlab("Parent") + ylab("Selected/Unselected Counts")
  
redone_glm %>% filter(Name %in% c(1:20)) %>%
    mutate(Name = factor(Name, levels = 1:20)) %>%
  ggplot(aes(x = Name, y = abs(Zscore), color = Lab, shape = Sign, alpha = Lab == "Interaction")) + geom_point(size = 4) +
  facet_grid("Sign") + scale_alpha_manual(values = c(0.4, 1, 1)) +
  theme_bw() +  theme(legend.position = "none") +
  xlab("Trial")
```
For Kia

```{r}
redone_glm %>% select(Name, Zscore, Lab, Sign) %>%
  pivot_wider(names_from = Lab, values_from = Zscore) %>%
  ggplot(aes(x = Interaction, y = Selection, color = Sign)) + geom_point()
```


Putting these together

```{r, fig.width=8, fig.height=6}
redone_glm %>% 
  select(Name, Zscore, Lab, Sign) %>%
  pivot_wider(names_from = Lab, values_from = Zscore) %>%
  mutate(ratio = log(abs(Interaction/Selection))) %>%
  ggplot(aes(x = Sign, y = ratio)) + 
  geom_jitter(aes(color = ratio > 0), alpha = 0.1) +
  geom_boxplot(aes(color = Sign)) + 
  ggtitle("Simulation Results of GLM") +
  scale_color_manual(values = c("black", "salmon","gray", "gray"))+
  theme(legend.position = "none") +
  ylab("abs Interaction/Bulk") -> pw

redone_test %>%
  filter(Name %in% c(1:20)) %>%
  mutate(Name = factor(Name, levels = 1:20)) %>%
  pivot_wider(names_from = Selection, values_from = value) %>%
  mutate(actualeffect = S/U) %>%
  ggplot(aes(x = as.numeric(Parent), y = actualeffect, linetype = Allele, color = Name %in% SignList$Name)) + 
  geom_line(size = 1) +
  scale_color_manual(values = c("black", "salmon")) +
  scale_linetype_manual(values = c(1,1)) +
  facet_wrap("Name") +theme_bw() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = breaks_pretty(n = 1)) +
  xlab("Parent") + ylab("Selected/Unselected Counts") -> px
  
################################################################################
redone_glm %>% filter(Name %in% c(1:20)) %>%
    mutate(Name = factor(Name, levels = 1:20)) %>%
  mutate(Sign = gsub("TRUE", "Sign", Sign),
         Sign = gsub("FALSE", "Magnitude", Sign)) %>%
  mutate(Coefficient = Lab) %>%
  filter(Coefficient %in% c("Selection", "Interaction")) %>%
  ggplot(aes(x = Name, y = abs(Zscore), color = Coefficient)) + 
  geom_point(size = 4, alpha = 0.8, shape = 2, stroke = 1) +
  scale_color_manual(values = c("purple","black")) +
  scale_shape_manual(values = c(2,1)) +
  facet_grid("Sign") + 
  theme_bw() +  theme(legend.position = "left") +
  theme(strip.background = element_rect(fill = c("black", "salmon" )),
        strip.text = element_text(color = "white")) +
  xlab("Trial") -> py

#plot_grid(pw, px, rel_widths = c(2,4)) -> pz

plot_grid(pz, py, ncol = 1, rel_heights = c(4,2))
```

## Looking at actual peaks for what the counts are

```{r}

rd_factor <- readRDS("rd_factorG.rds")
peaks <- readRDS("peaks_CuAll.rds")
```

```{r}

peaks %>% filter(label == "Interaction") %>% mutate(POS = peakPOS) -> IntPeaks
peaks %>% filter(label == "Bulk") -> BulkPeaks

rd_factor %>% filter(POS %in% IntPeaks$peakPOS) %>%
  mutate(Background = gsub("Oak", 0, Background),
         Background = gsub("Wine", 1, Background)) %>%
  ggplot(aes(x = as.numeric(Background), y = SmoothCount, color = Allele)) + 
  geom_point(shape = 1, size = 2, stroke = 1, alpha = 0.8) + 
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_color_manual(values = c("palegreen3", "firebrick3")) +
    xlab("Parental Background") +
  #scale_fill_manual(values = c("limegreen", "firebrick")) +
  facet_grid(Bulk ~ paste(CHROM, POS)) + ggtitle("Interaction Peaks") ->pint
  #facet_grid(Bulk ~CHROM)

# rd_factor %>% filter(CHROM == "VIII", POS == 204879	) %>%
#   filter(grepl("elected", Dataset)) %>%
#   mutate(Background = gsub("Oak", 0, Background),
#          Background = gsub("Wine", 1, Background)) %>%
#   ggplot(aes(x = as.numeric(Background), y = SmoothCount, color = Allele)) + 
#   geom_point(shape = 1, size = 2, stroke = 1, alpha = 0.8) + 
#   geom_smooth(method = "lm", alpha = 0.2) +
#   scale_color_manual(values = c("limegreen", "firebrick3")) +
#   #scale_fill_manual(values = c("limegreen", "firebrick")) +
#   facet_grid(Bulk ~ CHROM)

rd_factor %>% filter(POS %in% BulkPeaks$peakPOS) %>%
  filter(CHROM %in% c("XV", "XIV", "IX")) %>%
  mutate(Background = gsub("Oak", 0, Background),
         Background = gsub("Wine", 1, Background)) %>%
  ggplot(aes(x = as.numeric(Background), y = SmoothCount, color = Allele)) + 
  geom_point(shape = 1, size = 2, stroke = 1, alpha = 0.8) + 
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_color_manual(values = c("palegreen3", "firebrick3")) +
  facet_grid(Bulk ~ paste(CHROM, POS)) +
  xlab("Parental Background") +
  ggtitle("Select Bulk Peaks") -> pbulk

plot_grid(pbulk, pint, ncol = 1) -> plm

AllCuSO4_glmer_1byRep %>% merge(IntPeaks[,c(1,3,7)]) %>%
  filter(label %in% c("Bulk", "Interaction")) %>%
  mutate(Coefficient = label) %>%
  #filter(abs(zscore) > 1.1) %>%
  ggplot(aes(x = as.character(POS), y = abs(zscore), color = Coefficient)) + 
  geom_point(stroke = 1, size = 2, alpha = 0.8, shape = 2) + 
  facet_grid( ~ CHROM, scales = "free") +
  ylim(0,10) +
  xlab("") + ylab("abs Z-score") +
  scale_color_manual(values = c("black", "purple")) -> pzscores
```

Actual scores of each

```{r, fig.width=7, fig.height=7}
plot_grid(plm, pzscores, ncol = 1, rel_heights = c(4,1))
```

Actually do the same plot but with the highest point from each of these chromosomes

```{r}
AllCuSO4_glmer_1byRep %>% filter(label == "Interaction", CSS == "VIII",
                                 CHROM %in% c("VII", "X", "XI", "XII", "XIV", "XV")) %>%
  group_by(CHROM) %>%
  arrange(desc(abs(zscore))) %>%
  summarize(POS = head(POS, 1)) -> IntPeaks2

rd_factor %>% filter(POS %in% IntPeaks2$POS) %>%
  mutate(Background = gsub("Oak", 0, Background),
         Background = gsub("Wine", 1, Background)) %>%
  ggplot(aes(x = as.numeric(Background), y = SmoothCount, color = Allele)) + 
  geom_point(shape = 1, size = 2, stroke = 1, alpha = 0.8) + 
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_color_manual(values = c("palegreen3", "firebrick3")) +
    xlab("Parental Background") +
  facet_grid(Bulk ~ paste(CHROM, POS)) + ggtitle("Interaction Peaks") -> pa

AllCuSO4_glmer_1byRep %>% merge(IntPeaks2) %>%
  filter(label %in% c("Bulk", "Interaction"), CSS == "VIII") %>%
  mutate(Coefficient = label) %>%
  #filter(abs(zscore) > 1.1) %>%
  ggplot(aes(x = as.character(POS), y = abs(zscore), color = Coefficient)) + 
  geom_point(stroke = 1, size = 2, alpha = 0.8, shape = 2) + 
  facet_grid( ~ CHROM, scales = "free") +
  ylim(0,10) +
  xlab("") + ylab("abs Z-score") +
  scale_color_manual(values = c("black", "purple")) -> pb

plot_grid(pa, pb, ncol = 1, rel_heights = c(2,1))

```

